### 2023-08-24 paper.tex
Initial commit

\documentclass[1p]{elsarticle}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{xcolor}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{hyperref}
\usepackage{cleveref}

\bibliographystyle{elsarticle-num}
\journal{Physica A: Statistical Mechanics and its Applications}

\begin{document}

\author[Smith]{Vasily~Postnicov}
\author[Smith]{Marina~V.~Karsanina}
\author[Smith,MIT]{Aleksey~Khlyupin}
\author[Smith]{Kirill~M.~Gerke\corref{maincorr}}
\cortext[maincorr]{Corresponding author}
\ead{kg@ifz.ru}

\address[Smith]{Schmidt Institute of Physics of the Earth of Russian Academy of
  Sciences, Moscow, 107031, Russia}
\address[MIT]{Moscow Institute of Physics and Technology,
  Dolgoprudny, 141701, Russia}
%\affiliation{\textsuperscript{3}Oil and Gas Research Institute Russian Academy
%  of Sciences (OGRI RAS) 3, Gubkina st., Moscow, 119333, Russian Federation}

\title{Another paper with lots of text and fancy pictures}

\begin{abstract}
  Wow, we can multiply arrays and tell you how cool it is.
\end{abstract}

\begin{keyword}
  Arrays, multiplication, addition
\end{keyword}

\maketitle

\section{Theoretical background}
Let $A_1, A_2, \dots, A_n$ be pairwise disjoint subsets of a set
$A \subset \mathbb{R}^n$. We introduce a family of indicator functions
$I_n(x) : A \rightarrow \{0,1\}$ defined as:
\begin{equation}
  I_n(x) = \left\{
  \begin{array}{ll}
    1 & \quad x \in A \\
    0 & \quad \text{otherwise}
  \end{array}
  \right.
\end{equation}

Now we can define the three-point correlation function $S_3: A^2 \rightarrow [0, 1]$:
\begin{equation}
  S_3^n(x_1, x_2) = \langle I_n(x) I_n(x + x_1) I_n(x + x_2) \rangle
\end{equation}
It can be understood as the probability that all three vertices of a triangle
$(0, x_1, x_2)$ will appear in the subset $A_n$ when it is randomly thrown in
$A$. When $A$ represent isotropic medium, $x_1$ and $x_2$ can be replaced with
three numbers $r_1 = |x_1|$, $r_2 = |x_2|$ and $r_3 = |x_2 - x_1|$ to get a
function $S_3: [0, \infty)^3 \rightarrow [0, 1]$.

Another function closely related to the three-point correlation function is the
cluster function which can be defined as
\begin{equation}
  C_3^n(x_1, x_2) = \sum_{k=1}^K \langle \tilde{I}_k(x) \tilde{I}_k(x + x_1) \tilde{I}_k(x + x_2) \rangle
\end{equation}
where $\tilde{I}_k$ is an indicator function for $k$-th cluster and $K$ is a
total number of clusters. A cluster is a subset of $A_n$ so that any two points
in this subset can be connected with a curve belonging to that subset.

Introduce a function $M_n(x) = |\nabla I_n(x)|$ which is a so-called interface
indicator function. With this function we can define three additional
correlation functions, which are the surface-surface-surface function
($F_{sss}$), surface-surface-void function ($F_{ssv}$) and surface-void-void
function ($F_{svv}$). They are defined as
\begin{align}
  F_{sss}^n(x_1, x_2) &= \langle M_n(x) M_n(x + x_1) M_n(x + x_2) \rangle \\
  F_{ssv}^n(x_1, x_2) &= \langle M_n(x) M_v(x + x_1) I_v(x + x_2) \rangle \\
  F_{svv}^n(x_1, x_2) &= \langle M_n(x) I_v(x + x_1) I_v(x + x_2) \rangle
\end{align}
Here $I_v$ is an indicator function for the subset of the void phase
$A_v$. Unlike $S_3$ and $C_3$ functions, these functions do not have the meaning
of probability and have the units of measurement inversely proportional to
volume, surface and length, respectively (e.g. $\mu m^{-3}$, $\mu m^{-2}$ and
$\mu m^{-1}$). These functions describe the interface of the subset $A_n$ and
its spatial configuration with respect to $A_v$.

\section{Computational algorithms}
Three-point correlation function $S_3$ can be computed either in spatial domain
or in frequency domain via the convolution theorem. The simplest algorithm below
calculates $S_3$ pointwise in spatial domain:
\begin{algorithmic}[1]
  \Procedure{$S_3$}{$A, n, x_1, x_2$}
  \State $A_n \gets I_n (A)$
  \State $A'_n \gets \mathfrak{S}(A_n, x_1)$
  \State $A''_n \gets \mathfrak{S}(A_n, x_2)$
  \State $T \gets A_n \cdot A'_n \cdot A''_n$
  \State \textbf{return} $Sum(T) / Norm(A, x_1, x_2)$
  \EndProcedure
\end{algorithmic}
In this algorithm the indicator function $I_n$ for the phase of interest $n$ is
applied to the input array $A$. Then the shift operator $\mathfrak{S}$ is used
to shift $A_n$ by vectors $x_1$ and $x_2$. Finally, the three arrays are
multiplied pointwise and normalized sum of all elements of the product is
returned.

There are two common boundary conditions when applying $\mathfrak{S}$. The first
condition is to extend $A_n$ periodically (\cref{fig:s3-periodic}) when
accessing out-of-bounds array elements. This is the same as circular-shifting
$A_n$. In this case $Norm(A, x_1, x_2)$ does not depend on $x_1$ and $x_2$ and
is equal to the total number of elements in $A$. The second condition is to
replace out-of-bound elements with zeros (so-called zero padding)
(\cref{fig:s3-zeros}). A formula for $Norm(A, x_1, x_2)$ in this case is in
\ref{sec:number-of-trials}.
\begin{figure*}[tp]
  \centering
  \subfigure[Periodic boundary conditions]{
    \includegraphics[width=0.45\linewidth]{images/periodic.png}
    \label{fig:s3-periodic}}
  \hfill
  \subfigure[Zero padding]{
    \includegraphics[width=0.45\linewidth]{images/zeros.png}
    \label{fig:s3-zeros}}
  \caption[]{Computation of unnormalized $S_3$ function at point $(1, 2)$ for
    one-dimensional sequence of length 8.}
  \label{fig:s3-computation}
\end{figure*}

The second approach is to compute the whole correlation map in Fourier
domain. Suppose we have a function
$f: \mathbb{R} \rightarrow \mathbb{R}$. Triple correlation for this function is
a function
\begin{equation}
  g(t_1, t_2) = \int f(\tau) f(\tau + t_1) f(\tau + t_2) d \tau
\end{equation}
We can use a well-known formula to compute Fourier image of $g$:
\begin{equation}
  \hat{g}(z_1, z_2) = \hat{f}(z_1) \hat{f}(z_2) \overline{\hat{f}(z_1 + z_2)}
\end{equation}
This algorithm has a better computational complexity compared with the previous
algorithms if the whole correlation map is needed ($O(n \log n)$ vs
$O(n^2)$). The whole correlation map, however, requires a lot of memory and is
rarely needed. Imagine, that the input array $A$ is of dimensions
$500 \times 500$. Then, considering that single precision floating point numbers
are used, $4 \cdot 2 \cdot 500^4 / 1000^3 = 500$ GB are needed to store Fourier
image of the map. Moreover, Fourier image of the whole map is needed even if
only one element of the map in spatial domain is required. The aforementioned
limitations render this approach very impractical.

Our implementation fixes $x_1$ and $x_2$ to be parallel to one of the axes $X$,
$Y$ or $Z$ with restriction $x_1 \perp x_2$ (\cref{fig:pattern}). Thus, the
output has dimensions $D_1 \times D_2$ where $D_1$ and $D_2$ are dimensions of
the input array along selected axes.
\begin{figure}[ht]
  \centering
  \includegraphics[width=0.5\linewidth]{images/pattern.png}
  \caption[]{Pattern used for calculation of $S_3$ function in out
    implementation. Vectors $x_1$ and $x_2$ are parallel to one of the axes $X$,
    $Y$ or $Z$ and have lengths $r_1$ and $r_2$ respectively.}
  \label{fig:pattern}
\end{figure}

Algorithms for three-point surface functions are the same as for $S_3$,
containing only small modifications. The main difference is that we need to
replace an indicator function $I_n$ with an edge detection operator $E_n$
(see \ref{sec:filter}). Then the algorithms are straightforward:
\begin{algorithmic}[1]
  \Procedure{$F_{sss}$}{$A, n, x_1, x_2$}
  \State $A_n \gets E_n (A)$
  \State $A'_n \gets \mathfrak{S}(A_n, x_1)$
  \State $A''_n \gets \mathfrak{S}(A_n, x_2)$
  \State $T \gets A_n \cdot A'_n \cdot A''_n$
  \State \textbf{return} $Sum(T) / Norm(A, x_1, x_2)$
  \EndProcedure

  \Procedure{$F_{ssv}$}{$A, n, x_1, x_2$}
  \State $A_n \gets E_n (A)$
  \State $A_{(void)} \gets I_{(void)} (A)$
  \State $A'_n \gets \mathfrak{S}(A_n, x_1)$
  \State $A'_{(void)} \gets \mathfrak{S}(A_{(void)}, x_2)$
  \State $T \gets A_n \cdot A'_n \cdot A'_{(void)}$
  \State \textbf{return} $Sum(T) / Norm(A, x_1, x_2)$
  \EndProcedure

  \Procedure{$F_{svv}$}{$A, n, x_1, x_2$}
  \State $A_n \gets E_n (A)$
  \State $A_{(void)} \gets I_{(void)} (A)$
  \State $A'_{(void)} \gets \mathfrak{S}(A_{(void)}, x_1)$
  \State $A''_{(void)} \gets \mathfrak{S}(A_{(void)}, x_2)$
  \State $T \gets A_n \cdot A'_{(void)} \cdot A''_{(void)}$
  \State \textbf{return} $Sum(T) / Norm(A, x_1, x_2)$
  \EndProcedure
\end{algorithmic}

To compute $C_3$ function we need to use a connected-component labeling
algorithm \cite{4728561,PhysRevB.14.3438} to label clusters. Then, again, a
slightly modified algorithm for $S_3$ is used.
\begin{algorithmic}[1]
  \Procedure{$C_3$}{$A, n, x_1, x_2$}
  \State $A_n \gets I_n (A)$
  \State $C_n \gets \mathfrak{C}(A_n)$
  \State $C'_n \gets \mathfrak{S}(C_n, x_1)$
  \State $C''_n \gets \mathfrak{S}(C_n, x_2)$
  \State $T \gets C_n \odot C'_n \odot C''_n$
  \State \textbf{return} $Sum(T) / Norm(A, x_1, x_2)$
  \EndProcedure
\end{algorithmic}
Here $\mathfrak{C}$ is connected-component labeling operator and $\odot$ is
defined as follows:
\begin{equation}
  x \odot y = \left\{
  \begin{array}{ll}
    1 & \quad x = y \\
    0 & \quad \text{otherwise}
  \end{array}
  \right.
\end{equation}

\section{Verification}
To verify correctness of computation of $S_3$ and $C_3$ functions we use the
following simple relations:
\begin{align}
  & S_3^n (x, 0) = S_3^n (0, x) = S_2^n(x) \\
  & C_3^n (x, 0) = C_3^n (0, x) = C_2^n(x) \\
  & \lim_{\substack{x_1 \to \infty \\ x_2 \to \infty}} S_3^n (x_1, x_2) =
  \lim_{\substack{x_1 \to \infty \\ x_2 \to \infty}} C_3^n (x_1, x_2) = \phi_n^3
\end{align}
Here $\phi_n$ is a fraction of phase $n$ in $A$.

There are only few sets for which analytic expressions for $S_2$ are known. One
of those is a set consisting of overlapping balls with a fixed radius $R$ and
centers generated with Poisson process with parameter $\lambda$. In this case
the expression for $S_2$ is following:
\begin{equation}
  \begin{aligned}
    S_2(r, R) &= \exp(-\frac{4}{3}\pi\lambda R^3 f(r, R)) \\
    f(r, R) &= \left\{
    \begin{array}{ll}
      1 + \frac{3}{4} \frac{r}{R} - \frac{1}{16} (\frac{r}{R})^3 & \quad r < 2R \\
      2 & \quad \text{otherwise}
    \end{array}
    \right.
  \end{aligned}
  \label{eq:s2-balls}
\end{equation}

On \cref{fig:balls} there is an intersection of such a set with $R = 0.02$ and
$\lambda=5000$ and a cube $[0, 1]^3$. Because $R \ll 1$, we can use
\cref{eq:s2-balls} to verify our computations what we do on
\cref{fig:balls-s3-comparison}.
\begin{figure*}[tp]
  \centering
  \subfigure[Realization of overlapping balls]{
    \includegraphics[width=0.45\linewidth]{images/balls.png}
    \label{fig:balls}}
  \hfill
  \subfigure[A plot of $S_3(0, r)$ computed with our algorithm and theoretical
    formula.]{
    \includegraphics[width=0.45\linewidth]{images/balls-s3.png}
    \label{fig:balls-s3-comparison}}
  \caption[]{A comparison of calculated and theoretical values of $S_3$ function
    for overlapping balls.}
  \label{fig:s3-verification}
\end{figure*}

\textcolor{red}{What about $C_3$?}

To test $F_{sss}$ function we use a recently developed approach which computes
that function for sets defined by inequation $f(x) \le T$, $x \in \mathbb{R}^3$
with help of automatic differentiation \cite{postnicov20232}. We choose $f$
\begin{equation}
  f(x, y, z) = \sqrt{x^2 + y^2 + z^2}
\end{equation}
so inequation $f(x, y, z) \le T$ gives us a ball.

The test was performed by evaluating the inequation with the parameter $T = 0.2$
in a cube $[0, 1]^3$ and comparing $F_{sss}$ calculated with our algorithm with
precise values. The result of comparison is on
\cref{fig:sss-verification}. Maximal relative error for this case is about  15\%
when $F_{sss}(r_1, r_2)$ is calculated for $r_1$ and $r_2$ being not too close
to zero.
\begin{figure*}[tp]
  \centering
  \subfigure[Computation with our algorithm]{
    \includegraphics[width=0.45\linewidth]{images/ball-sss.png}
    \label{fig:balls-sss-comp}}
  \hfill
  \subfigure[Relative error of computation]{
    \includegraphics[width=0.45\linewidth]{images/ball-sss-error.png}
    \label{fig:ball-sss-error}}
  \caption[]{Comparison of $F_{sss}$ function for a ball with the radius $0.2$
    with precise values.}
  \label{fig:sss-verification}
\end{figure*}

To test $F_{ssv}$ and $F_{svv}$ we use the following relations for such a set
$A$ where all non-void phase is covered by a ball $\mathfrak{O}(R)$:
\begin{align}
  F^n_{ssv}(x_1, x_2) &= F^n_{ss}(x_1) \qquad x_2 > R \\
  F^n_{svv}(x_1, x_2) &= F^n_{sv}(x_1) \qquad x_2 > R
\end{align}
$F_{ss}$ and $F_{sv}$ functions are well-known for a ball of radius $R$ (solid
phase) placed in the center of cube of volume $V$ (void phase):
\begin{align}
  F_{ss}(r, R) &= \frac{1}{V} \left\{
    \begin{array}{ll}
      2\pi R^2/r & \quad r < 2R \\
      0 & \quad \text{otherwise}
    \end{array}
    \right.\\
  F_{sv}(r, R) &= \frac{1}{V} \left\{
    \begin{array}{ll}
      \pi Rr + 2\pi R^2 & \quad r < 2R \\
      4\pi R^2 & \quad \text{otherwise}
    \end{array}
    \right.
\end{align}
The comparison of our algorithm against theory is on
\cref{fig:surface-verification}. Radius of the ball is chosen $R=0.2$.
\begin{figure*}[tp]
  \centering
  \subfigure[$F_{ssv}$]{
    \includegraphics[width=0.45\linewidth]{images/ball-ssv.png}
    \label{fig:balls-ssv}}
  \hfill
  \subfigure[$F_{svv}$]{
    \includegraphics[width=0.45\linewidth]{images/ball-svv.png}
    \label{fig:ball-svv}}
  \caption[]{Comparison of $F_{ssv}$ and $F_{svv}$ functions for a ball with the
    radius $0.2$ with theoretical values.}
  \label{fig:surface-verification}
\end{figure*}

\section{Results}
In this section we compute correlation functions for some real samples. Table
\ref{tab:summary} contains information about these samples.
\begin{table}[!htp]
  \centering
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    Sample name & Image type & Dimensions (pixels) & Image resolution ($\mu m$) & $C_{0.5}$\\
    \hline
    Ceramic 1   & XCT & $500 \times 500 \times 500$ & 2.25 & 0.9823 \\
    Ceramic 2   & XCT & $500 \times 500 \times 500$ & 2.25 & 0.9890 \\
    Ceramic 3   & XCT & $500 \times 500 \times 500$ & 2.25 & 0.9712 \\
    Sandstone 1 & SEM &  $1280 \times 869$ & 0.10 & 0.9703 \\
    Sandstone 2 & SEM &  $1280 \times 869$ & 0.05 & 0.9897 \\
    Carbonate 1 & SEM &  $1024 \times 691$ & 0.06 & 0.9721 \\
    \hline
  \end{tabular}
  \caption{Summary of samples used for calculation of correlation functions.}
  \label{tab:summary}
\end{table}

\section{Discussion}
In this paper we have provided two approaches to compute three-point correlation
function:
\begin{enumerate}
\item Computation in frequency domain using Fourier transform. This approach has
  computational complexity $O(n \log n)$ and computes the whole correlation
  map. Unfortunately, it requires $O(n^2)$ additional memory and therefore can
  be used only with small inputs. Moreover, the whole Fourier image of the input
  is needed even if we need only a small part of the correlation map.
\item Computation in spatial domain. This approach is implemented by us in
  CorrelationFunctions.jl package. This approach calculates the full map with
  complexity $O(n^2)$ but uses only $O(n)$ additional memory for shifted
  versions of the input. For our purposes the whole map is not needed and
  therefore the amount of calculations can be significantly reduced.
\end{enumerate}
It's tempting to create an algorithm which unites advantages of both approaches
(fast speed of the first and low memory consumption of the second) which
computes some desired slices of correlation map. It is known that Fourier
transform is the only linear transform which allows computation of convolution
in $O(n)$. It is still an open question if there are linear transforms which
allow computation of convolution with complexity between $O(n)$ and $O(n^2)$
\cite{stone2008uniqueness,stone1998convolution}.

\appendix
\section{Computation of number of trials for non-periodic mode}
\label{sec:number-of-trials}
If the displacement vectors $x_1, x_2: x_1 \perp x_2$ are parallel to two
distinct unit vectors $i=(1,0,0)$, $j=(0,1,0)$ or $k=(0,0,1)$ then the number of
trials for the input array having dimensions $D = (D_x, D_y, D_z)$ is the
following:
\begin{equation}
  \begin{aligned}
    & Norm(A, x_1, x_2) = \prod_k D'_k \\
    & D' = D - x_1 - x_2
  \end{aligned}
\end{equation}

\section{Edge detection filter}
\label{sec:filter}
For edge detection we use a kernel with the width 7 with coefficients inversely
proportional to distance to kernel's central element. The central element has
such value, so all elements of the kernel sum to zero:
\begin{equation}
  E_k = S \left\{
  \begin{array}{ll}
    -\sum\limits_{\substack{l \\ l \ne 0}} E_l & \quad k = 0 \\
    1 / \rho(k, 0) & \quad \text{otherwise}
  \end{array}
  \right.
\end{equation}
For 3D case $S=172.96$ and for 2D case $S=30.46$.

\bibliography{paper}
\end{document}

### 2023-08-24 data/plot-s2.py

@@ -1,0 +1,32 @@
+#!/usr/bin/env python
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+def s2_th(x, λ, R):
+    ρ = 4/3*np.pi*λ*R**3
+    return np.exp(-ρ * np.where(x < 2*R, 1 + 3/4*x/R - 1/16*(x/R)**3, 2))
+
+s2 = np.load('test-s2.npy')
+xs = np.linspace(0, 0.5, s2.size)
+
+plt.figure(figsize = (10, 8), dpi = 300)
+plt.rc('font', size = 25)
+plt.plot(xs, s2)
+plt.plot(xs, s2_th(xs, 5000, 0.02))
+plt.xlabel(r'$r$')
+plt.ylabel(r'$S_3(0, r)$')
+plt.ticklabel_format(axis = "y", scilimits = (0, 0), useMathText = True)
+plt.ticklabel_format(axis = "x", scilimits = (0, 0), useMathText = True)
+plt.legend(['Calculation', 'Theory'])
+plt.savefig('../images/balls-s3.png')
+
+plt.figure(figsize = (10, 8), dpi = 300)
+plt.rc('font', size = 30)
+plt.plot(xs, s2)
+plt.plot(xs, s2_th(xs, 5000, 0.02))
+plt.ticklabel_format(axis = "y", scilimits = (0, 0), useMathText = True)
+plt.ticklabel_format(axis = "x", scilimits = (0, 0), useMathText = True)
+plt.xlim([0.03, 0.06])
+plt.ylim([0.71, 0.73])
+plt.savefig('../images/balls-s3-zoom.png')

### 2023-08-24 data/plot-surface.py

@@ -1,0 +1,38 @@
+#!/usr/bin/env python
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+def ss(x, R):
+    return np.where(x < 2*R, 2*np.pi*R**2/x, 0)
+
+def sv(x, R):
+    return np.where(x < 2*R, np.pi*R*x + 2*np.pi*R**2, 4*np.pi*R**2)
+
+ssc = np.load('ball-ss.npy')
+svc = np.load('ball-sv.npy')
+
+xs = np.linspace(0, 0.5, ssc.size)
+plt.figure(figsize = (10, 8), dpi = 300)
+plt.rc('font', size = 25)
+plt.plot(xs, ssc)
+plt.plot(xs, ss(xs, 0.2))
+plt.ylim([0, 20])
+plt.xlabel(r'$r$')
+plt.ylabel(r'$F_{ssv}(r, 0.5)$')
+plt.legend(['Calculation', 'Theory'])
+plt.ticklabel_format(axis = "y", scilimits = (0, 0), useMathText = True)
+plt.ticklabel_format(axis = "x", scilimits = (0, 0), useMathText = True)
+plt.savefig('../images/ball-ssv.png')
+
+xs = np.linspace(0, 0.5, svc.size)
+plt.figure(figsize = (10, 8), dpi = 300)
+plt.rc('font', size = 25)
+plt.plot(xs, svc)
+plt.plot(xs, sv(xs, 0.2))
+plt.xlabel(r'$r$')
+plt.ylabel(r'$F_{svv}(r, 0.5)$')
+plt.legend(['Calculation', 'Theory'])
+plt.ticklabel_format(axis = "y", scilimits = (0, 0), useMathText = True)
+plt.ticklabel_format(axis = "x", scilimits = (0, 0), useMathText = True)
+plt.savefig('../images/ball-svv.png')

### 2023-08-24 data/s3-zoom.sh

@@ -1,0 +1,4 @@
+#!/bin/sh
+
+convert -composite -gravity center -geometry 1500x1200+400+150 \
+        ../images/balls-s3.png ../images/balls-s3-zoom.png ../images/balls-s3-result.png

### 2023-08-24 data/three-point-surface.jl

@@ -1,0 +1,33 @@
+module Shit
+import CorrelationFunctions.Directional as D
+import CorrelationFunctions.Utilities as U
+using NPZ
+export draw_ball, do_all!
+
+function draw_ball(s, r)
+    array = zeros(Bool, s)
+    center = @. (s ÷ 2) |> floor |> Int
+
+    for idx in CartesianIndices(array)
+        dist = sum((Tuple(idx) .- center) .^ 2)
+        if dist <= r^2
+            array[idx]	= true
+        end
+    end
+
+    return array
+end
+
+function do_all!()
+    ball = draw_ball((250, 250, 250), 0.2*250)
+    println(U.lowfreq_energy_ratio(ball))
+    ssv = D.surf2void(ball, false; periodic = true)
+    calc = ssv[D.PlaneXY()][end-15, :] * 250^2
+    npzwrite("ball-ss.npy", calc)
+
+    svv = D.surfvoid2(ball, false; periodic = true)
+    calc = svv[D.PlaneXY()][end-15, :] * 250
+    npzwrite("ball-sv.npy", calc)
+end
+
+end

### 2023-08-24 data/two-point.jl

@@ -1,0 +1,16 @@
+module Shit
+import CorrelationFunctions.Utilities as U
+import CorrelationFunctions.Directional as D
+using Statistics
+using NPZ
+
+function do_it!()
+    data = U.read_cuboid("test.raw", 300, 3)
+    for sym in [:s2, :c2]
+        fn = D.eval(sym)
+        cf = fn(data, false; periodic = true) |> mean
+        npzwrite("test-$(sym).npy", cf)
+    end
+end
+
+end

### 2023-09-25 paper.tex
Replot F_{sss} comparison

@@
 \begin{equation}
-  f(x, y, z) = \sqrt{x^2 + y^2 + z^2}
+  f(x, y, z) = [(2x)^{\frac{3}{2}} + y^{\frac{3}{2}} + z^{\frac{3}{2}}]^{\frac{2}{3}}
 \end{equation}
-so inequation $f(x, y, z) \le T$ gives us a ball.
+so inequation $f(x, y, z) \le T$ gives us an ellipse-like object
+(\cref{fig:sss-ellipse}).
 
-The test was performed by evaluating the inequation with the parameter $T = 0.2$
-in a cube $[0, 1]^3$ and comparing $F_{sss}$ calculated with our algorithm with
-precise values. The result of comparison is on
-\cref{fig:sss-verification}. Maximal relative error for this case is about  15\%
-when $F_{sss}(r_1, r_2)$ is calculated for $r_1$ and $r_2$ being not too close
-to zero.
+The test was performed by evaluating the inequation with the parameter $T = 0.4$
+in a cube $[-1, 1]^3$ and comparing $F_{sss}$ calculated by our algorithm with
+precise values. Pointwise relative error of $F_{sss}$ is on
+\cref{fig:sss-ellipse-error}. Maximal relative error in the area bound by
+inequations $x > 0.1$, $y > 0.1$ and $f(x, y) < 0.78$ is about 10\%.
 \begin{figure*}[tp]
   \centering
-  \subfigure[Computation with our algorithm]{
-    \includegraphics[width=0.45\linewidth]{images/ball-sss.png}
-    \label{fig:balls-sss-comp}}
+  \subfigure[The ellipse-like object used in testing of $F_{sss}$ computation]{
+    \includegraphics[width=0.45\linewidth]{images/ellipse.png}
+    \label{fig:sss-ellipse}}
   \hfill
   \subfigure[Relative error of computation]{
-    \includegraphics[width=0.45\linewidth]{images/ball-sss-error.png}
-    \label{fig:ball-sss-error}}
-  \caption[]{Comparison of $F_{sss}$ function for a ball with the radius $0.2$
-    with precise values.}
+    \includegraphics[width=0.45\linewidth]{images/ellipse-sss-diff.png}
+    \label{fig:sss-ellipse-error}}
+  \vskip\baselineskip
+  \subfigure[$F_{sss}$: precise]{
+    \includegraphics[width=0.45\linewidth]{images/ellipse-sss.png}}
+  \hfill
+  \subfigure[$F_{sss}$: calculated with our approach]{
+    \includegraphics[width=0.45\linewidth]{images/ellipse-sss-julia.png}}
+  \caption[]{A comparison of $F_{sss}$ function calculated using our approach
+    with its precise values.}
   \label{fig:sss-verification}

### 2023-09-27 paper.tex
CFs of real examples

@@
 \usepackage{cleveref}
+\usepackage[export]{adjustbox}
 
@@
 
-\textcolor{red}{What about $C_3$?}
-
 To test $F_{sss}$ function we use a recently developed approach which computes
@@
 \section{Results}
-In this section we compute correlation functions for some real samples. Table
-\ref{tab:summary} contains information about these samples.
+In this section we compute correlation functions along the plane $XY$ for some
+real samples, namely one three-dimensional XCT and one two-dimensional SEM
+sample. Table \ref{tab:summary} contains information about these samples. Images
+of the samples are on \cref{fig:samples}. On the plots of correlation functions
+we provide a family of curves with the first argument of the correlation
+function being fixed.
+
+Correlation functions for the XCT sample are on
+\cref{fig:sample-limestone-cf}. The plot of $S_3$ function allows us to estimate
+porosity of the sample to be $\sim 0.04$ (note, that the curve with $r_1 = 0$ is
+actually $S_2$ function). The two-point correlation function reaches plateau at
+$r_2 \approx 200\div 225\ \mu m$ which means that two events of finding two
+points in the void phase are independent if the points are farther than
+$225\ \mu m$ from each other. We see that the sample is a little bit anisotropic
+($S_3(0, 225) \approx S_3(150, 0)$). From analysis of $C_3$ function it can be
+stated that the sample has clusters of void phase which are $\sim 200\ \mu m$ in
+diameter.
+
+Correlation functions for the SEM sample are on
+\cref{fig:sample-sandstone-cf}. Porosity of the sample is $\sim 0.3$ as follows
+from the plot of $S_3$ function at $r_1 = 0$. The funcion $S_3(0, r_2)$ reaches
+plateau at $r_2 \approx 20\ \mu m$. The sample is highly anisotropic (elongated
+along the ordinate). The samples has clusters which are $\sim 45\ \mu m$ in
+diameter.
 \begin{table}[!htp]
@@
     \hline
-    Ceramic 1   & XCT & $500 \times 500 \times 500$ & 2.25 & 0.9823 \\
-    Ceramic 2   & XCT & $500 \times 500 \times 500$ & 2.25 & 0.9890 \\
-    Ceramic 3   & XCT & $500 \times 500 \times 500$ & 2.25 & 0.9712 \\
-    Sandstone 1 & SEM &  $1280 \times 869$ & 0.10 & 0.9703 \\
-    Sandstone 2 & SEM &  $1280 \times 869$ & 0.05 & 0.9897 \\
-    Carbonate 1 & SEM &  $1024 \times 691$ & 0.06 & 0.9721 \\
+    Limestone & XCT &  $600 \times 600 \times 600$ & 3.02 & 0.9712 \\
+    Sandstone & SEM &  $1280 \times 869$ & 0.10 & 0.9703 \\
     \hline
@@
 \end{table}
+
+\begin{figure*}[tp]
+  \centering
+  \subfigure[Limestone]{
+    \includegraphics[width=0.45\linewidth]{images/carb.png}
+    \label{fig:sample-limestone}}
+  \hfill
+  \subfigure[Sandstone (different clusters of void phase are shown in color)]{
+    \includegraphics[width=0.45\linewidth, frame]{images/sandstone1.png}
+    \label{fig:sample-sandstone}}
+  \caption[]{Images of samples used for calculation of higher-order correlation
+    functions.}
+  \label{fig:samples}
+\end{figure*}
+
+\begin{figure}[tp]
+  \centering
+  \includegraphics[width=0.3\linewidth]{images/carb.npy-surf3.png}
+  \hfill
+  \includegraphics[width=0.3\linewidth]{images/carb.npy-surf2void.png}
+  \hfill
+  \includegraphics[width=0.3\linewidth]{images/carb.npy-surfvoid2.png}
+  \vskip\baselineskip
+  \includegraphics[width=0.3\linewidth]{images/carb.npy-s3.png}
+  \includegraphics[width=0.3\linewidth]{images/carb.npy-c3.png}
+  \caption[]{Correlation functions for carbonate sample
+    (\cref{fig:sample-limestone}).}
+  \label{fig:sample-limestone-cf}
+\end{figure}
+
+\begin{figure}[tp]
+  \centering
+  \includegraphics[width=0.45\linewidth]{images/sandstone1.png-surf2void.png}
+  \hfill
+  \includegraphics[width=0.45\linewidth]{images/sandstone1.png-surfvoid2.png}
+  \vskip\baselineskip
+  \includegraphics[width=0.45\linewidth]{images/sandstone1.png-s3.png}
+  \hfill
+  \includegraphics[width=0.45\linewidth]{images/sandstone1.png-c3.png}
+  \caption[]{Correlation functions for sandstone sample
+    (\cref{fig:sample-sandstone}).}
+  \label{fig:sample-sandstone-cf}
+\end{figure}
 

### 2023-09-27 paper.tex
Ellipse -> ellipsoid

@@
 \end{equation}
-so inequation $f(x, y, z) \le T$ gives us an ellipse-like object
-(\cref{fig:sss-ellipse}).
+so inequation $f(x, y, z) \le T$ gives us an ellipsoid-like object
+(\cref{fig:sss-ellipsoid}).
 
@@
 precise values. Pointwise relative error of $F_{sss}$ is on
-\cref{fig:sss-ellipse-error}. Maximal relative error in the area bound by
+\cref{fig:sss-ellipsoid-error}. Maximal relative error in the area bound by
 inequations $x > 0.1$, $y > 0.1$ and $f(x, y) < 0.78$ is about 10\%.
@@
   \centering
-  \subfigure[The ellipse-like object used in testing of $F_{sss}$ computation]{
-    \includegraphics[width=0.45\linewidth]{images/ellipse.png}
-    \label{fig:sss-ellipse}}
+  \subfigure[The ellipsoid-like object used in testing of $F_{sss}$ computation]{
+    \includegraphics[width=0.45\linewidth]{images/ellipsoid.png}
+    \label{fig:sss-ellipsoid}}
   \hfill
   \subfigure[Relative error of computation]{
-    \includegraphics[width=0.45\linewidth]{images/ellipse-sss-diff.png}
-    \label{fig:sss-ellipse-error}}
+    \includegraphics[width=0.45\linewidth]{images/ellipsoid-sss-diff.png}
+    \label{fig:sss-ellipsoid-error}}
   \vskip\baselineskip
   \subfigure[$F_{sss}$: precise]{
-    \includegraphics[width=0.45\linewidth]{images/ellipse-sss.png}}
+    \includegraphics[width=0.45\linewidth]{images/ellipsoid-sss.png}}
   \hfill
   \subfigure[$F_{sss}$: calculated with our approach]{
-    \includegraphics[width=0.45\linewidth]{images/ellipse-sss-julia.png}}
+    \includegraphics[width=0.45\linewidth]{images/ellipsoid-sss-julia.png}}
   \caption[]{A comparison of $F_{sss}$ function calculated using our approach

### 2023-09-27 paper.tex
C0.5 criterion

@@
 
+Input images must have appropriately high resolution for edge detection filter
+to work correctly. A criterion for ``goodness'' of an image can be expressed
+with $C_{\alpha}$ parameter \cite{samarin2023robust}. Let $\alpha \in [0, 1]$
+and $f(x)$ be (band-limited) input image ($x \in \mathbb{R}^2$ or
+$\mathbb{R}^3$). We define $C_\alpha$ as follows:
+\begin{equation}
+  \begin{aligned}
+    f_0(x) &= f(x) - \langle f(x) \rangle \\
+    C_\alpha &= \frac{\int_{-\alpha\omega}^{\alpha\omega} |\hat{f_0}(z)|^2
+      dz}{\int_{-\omega}^{\omega} |\hat{f_0}(z)|^2 dz}
+  \end{aligned}
+\end{equation}
+where $\hat{f_0}$ is a Fourier transform of $f_0$ and $\omega$ is a folding
+frequency which depends only on resolution of the image. If a criterion
+$C_{0.5} > 0.97$ holds then the image is suitable for application of
+aforementioned algorithms for calculation of surface functions.
+
 To compute $C_3$ function we need to use a connected-component labeling
@@
 real samples, namely one three-dimensional XCT and one two-dimensional SEM
-sample. Table \ref{tab:summary} contains information about these samples. Images
-of the samples are on \cref{fig:samples}. On the plots of correlation functions
-we provide a family of curves with the first argument of the correlation
-function being fixed.
+sample. Table \ref{tab:summary} contains information about these samples. Note
+that the criterion $C_{0.5} > 0.97$ holds for both of the samples. Images of the
+samples are on \cref{fig:samples}. On the plots of correlation functions we
+provide a family of curves with the first argument of the correlation function
+being fixed.
 

### 2023-09-28 paper.tex
Fix some stuff

@@
 \usepackage[export]{adjustbox}
+
+\definecolor{light-gray}{gray}{0.95}
+\newcommand{\code}[1]{\colorbox{light-gray}{\texttt{#1}}}
 
@@
   \begin{array}{ll}
-    1 & \quad x \in A \\
+    1 & \quad x \in A_n \\
     0 & \quad \text{otherwise}
@@
 
-Now we can define the three-point correlation function $S_3: A^2 \rightarrow [0, 1]$:
+Now we can define the three-point correlation function
+$S_3: \mathbb{R}^2 \rightarrow [0, 1]$:
 \begin{equation}
@@
 \end{equation}
-It can be understood as the probability that all three vertices of a triangle
-$(0, x_1, x_2)$ will appear in the subset $A_n$ when it is randomly thrown in
-$A$. When $A$ represent isotropic medium, $x_1$ and $x_2$ can be replaced with
-three numbers $r_1 = |x_1|$, $r_2 = |x_2|$ and $r_3 = |x_2 - x_1|$ to get a
-function $S_3: [0, \infty)^3 \rightarrow [0, 1]$.
+where $\langle \dots \rangle$ means average over all points in $A$. It can be
+understood as the probability that all three vertices of a triangle
+$(0, x_1, x_2)$ will appear in the subset $A_n$ when the triangle is randomly
+thrown in $A$. When $A$ represent isotropic medium, $x_1$ and $x_2$ can be
+replaced with three numbers $r_1 = |x_1|$, $r_2 = |x_2|$ and $r_3 = |x_2 - x_1|$
+to get a function of three scalar arguments.
 
@@
 \begin{align}
-  & S_3^n (x, 0) = S_3^n (0, x) = S_2^n(x) \\
-  & C_3^n (x, 0) = C_3^n (0, x) = C_2^n(x) \\
-  & \lim_{\substack{x_1 \to \infty \\ x_2 \to \infty}} S_3^n (x_1, x_2) =
-  \lim_{\substack{x_1 \to \infty \\ x_2 \to \infty}} C_3^n (x_1, x_2) = \phi_n^3
+  S_3^n (x, 0) = S_3^n (0, x) &= S_2^n(x) \\
+  C_3^n (x, 0) = C_3^n (0, x) &= C_2^n(x) \\
+  \lim_{\substack{x_1 \to \infty \\ x_2 \to \infty}} S_3^n (x_1, x_2) &= \phi_n^3
 \end{align}
@@
 that the criterion $C_{0.5} > 0.97$ holds for both of the samples. Images of the
-samples are on \cref{fig:samples}. On the plots of correlation functions we
-provide a family of curves with the first argument of the correlation function
-being fixed.
+samples are on \cref{fig:samples}. On plots of correlation functions we provide
+a family of curves with the first argument of the correlation function being
+fixed.
 

### 2023-10-30 paper.tex
Anisotropicity and comparison with other algorithms

@@
 
+\textcolor{red}{Where to put this?}
+We have made a comparison of our algorithm with two algorithms, one of which
+proposed by Malmir~et~al \cite{malmir2018} and another proposed by Smith and
+Torquato \cite{SMITH1988176}. The first algorithms generates a triangle with
+fixed sides $r_1$ and $r_2$ and an angle $\theta$ between them and places it in
+the medium firstly making a random translation and a rotation around a random
+vector by a random angle. By making a large number of trials the algorithm gets
+a value of a three-point correlation function at the point
+$(r_1, r_2, \theta)$. The second algorithm takes a precalculated triangle
+$(r_1, r_2, \theta)$ from a web pattern and places it in the medium without
+rotation, only applying a random translation. This way the algorithm preserves
+orientation of triangles stored in the pattern.
+
+Our algorithm fixes $\theta = \frac{pi}{2}$ and does not perform random
+rotations or trial triangles. It is sensitive to anisotropicity of the medium
+when it is stretched along one of the axes as shown in \cref{fig:ellipses}. The
+main advantage of our algorithm is its parallelizability and ease of
+implementation.
+\begin{figure}[tp]
+  \centering
+  \includegraphics[width=0.3\linewidth]{images/ellipse-0.png}
+  \hfill
+  \includegraphics[width=0.3\linewidth]{images/ellipse-45.png}
+  \hfill
+  \includegraphics[width=0.3\linewidth]{images/ellipse-90.png}
+  \vskip\baselineskip
+  \includegraphics[width=0.3\linewidth]{images/ellipse-0-s3.png}
+  \hfill
+  \includegraphics[width=0.3\linewidth]{images/ellipse-45-s3.png}
+  \hfill
+  \includegraphics[width=0.3\linewidth]{images/ellipse-90-s3.png}
+  \caption[]{$S_3$ function for anisotropic media (ellipses). Anisotropicity of
+    the medium can be seen on heatmaps of $S_3$ function when the medium is
+    stretched along one of the axes.}
+  \label{fig:ellipses}
+\end{figure}
+
 \appendix

### 2023-11-08 paper.tex
Add blue patterns

@@
     implementation. Vectors $x_1$ and $x_2$ are parallel to one of the axes $X$,
-    $Y$ or $Z$ and have lengths $r_1$ and $r_2$ respectively.}
+    $Y$ or $Z$ and have lengths $r_1$ and $r_2$ respectively. Red triangles
+    contribute to $S_3(2, 3)$ and blue triangles contribute to $S_3(1, 1)$.}
   \label{fig:pattern}

### 2023-11-09 paper.tex
Rotations! Rotations!

@@
 $(r_1, r_2, \theta)$. The second algorithm takes a precalculated triangle
-$(r_1, r_2, \theta)$ from a web pattern and places it in the medium without
+$(r_1, r_2, \theta)$ from a web-like pattern and places it in the medium without
 rotation, only applying a random translation. This way the algorithm preserves
@@
 rotations or trial triangles. It is sensitive to anisotropicity of the medium
-when it is stretched along one of the axes as shown in \cref{fig:ellipses}. The
+when it is stretched along one of the axes as shown in \cref{fig:aniso}. The
 main advantage of our algorithm is its parallelizability and ease of
-implementation.
+implementation. An equivalent operation for rotation of test triangles is a
+rotation of the whole input image which we have implemented in our
+CorrelationFunctions.jl package. By applying a rotation to the input first we
+made a rest of the algorithm cache-friendly by avoiding random memory access.
 \begin{figure}[tp]
   \centering
-  \includegraphics[width=0.3\linewidth]{images/ellipse-0.png}
+  \includegraphics[width=0.3\linewidth]{images/aniso.png}
   \hfill
-  \includegraphics[width=0.3\linewidth]{images/ellipse-45.png}
+  \includegraphics[width=0.3\linewidth]{images/aniso-s3.png}
   \hfill
-  \includegraphics[width=0.3\linewidth]{images/ellipse-90.png}
-  \vskip\baselineskip
-  \includegraphics[width=0.3\linewidth]{images/ellipse-0-s3.png}
-  \hfill
-  \includegraphics[width=0.3\linewidth]{images/ellipse-45-s3.png}
-  \hfill
-  \includegraphics[width=0.3\linewidth]{images/ellipse-90-s3.png}
-  \caption[]{$S_3$ function for anisotropic media (ellipses). Anisotropicity of
-    the medium can be seen on heatmaps of $S_3$ function when the medium is
-    stretched along one of the axes.}
-  \label{fig:ellipses}
+  \includegraphics[width=0.3\linewidth]{images/aniso-s3-avg.png}
+  \caption[]{$S_3$ function for anisotropic media (on the left) elongated along
+    the axis $Y$. Anisotropicity of the medium can be seen on a heatmap of $S_3$
+    function (in the middle). An average of 10 $S_3$ evaluations of the medium
+    rotated by a random angle is on the right.}
+  \label{fig:aniso}
 \end{figure}

### 2023-11-09 paper.tex
Replace pictures

@@
   \caption[]{$S_3$ function for anisotropic media (on the left) elongated along
-    the axis $Y$. Anisotropicity of the medium can be seen on a heatmap of $S_3$
-    function (in the middle). An average of 10 $S_3$ evaluations of the medium
-    rotated by a random angle is on the right.}
+    the vector $(1, 1)$. Anisotropicity of the medium can be seen on a heatmap
+    of $S_3$ function (in the middle). An average of 120 $S_3$ evaluations of
+    the medium rotated by a random angle is on the right.}
   \label{fig:aniso}

### 2023-11-27 paper.tex
Make plots bigger

@@
   \centering
-  \includegraphics[width=0.3\linewidth]{images/carb.npy-surf3.png}
+  \includegraphics[width=0.45\linewidth]{images/carb.npy-surf3.png}
   \hfill
-  \includegraphics[width=0.3\linewidth]{images/carb.npy-surf2void.png}
+  \includegraphics[width=0.45\linewidth]{images/carb.npy-surf2void.png}
+  \vskip\baselineskip
+  \includegraphics[width=0.45\linewidth]{images/carb.npy-surfvoid2.png}
   \hfill
-  \includegraphics[width=0.3\linewidth]{images/carb.npy-surfvoid2.png}
+  \includegraphics[width=0.45\linewidth]{images/carb.npy-s3.png}
   \vskip\baselineskip
-  \includegraphics[width=0.3\linewidth]{images/carb.npy-s3.png}
-  \includegraphics[width=0.3\linewidth]{images/carb.npy-c3.png}
+  \includegraphics[width=0.45\linewidth]{images/carb.npy-c3.png}
   \caption[]{Correlation functions for carbonate sample

### 2023-11-27 paper.tex
Add heatmaps of S₃ for highly anisotropic samples

@@
 \section{Results}
-In this section we compute correlation functions along the plane $XY$ for some
-real samples, namely one three-dimensional XCT and one two-dimensional SEM
-sample. Table \ref{tab:summary} contains information about these samples. Note
-that the criterion $C_{0.5} > 0.97$ holds for both of the samples. Images of the
-samples are on \cref{fig:samples}. On plots of correlation functions we provide
-a family of curves with the first argument of the correlation function being
-fixed.
+In this section we compute correlation functions along the plane $XY$ for 2- and
+3-dimensional real samples. Table \ref{tab:summary} contains information about
+these samples. Note that we compute surface correlation functions only for those
+samples for which the criterion $C_{0.5} > 0.97$ holds. Images of the samples
+are on \cref{fig:samples}. On plots of correlation functions we provide a family
+of curves with the first argument of the correlation function being fixed. For
+two highly anisotropic samples (the soil and the shale) we provide heatmaps of
+$S_3$ correlation function where anisotropicity can be easily seen. These two
+samples was preliminary rotated by $\frac{\pi}{4}$ around the axis $Z$ before
+calculation of correlation functions.
 
@@
 diameter.
+
+Heatmaps of $S_3$ for the two highly anisotropic samples can be seen on
+\cref{fig:heatmaps}.
+
 \begin{table}[!htp]
@@
     Limestone & XCT &  $600 \times 600 \times 600$ & 3.02 & 0.9712 \\
+    Soil & XCT & $160 \times 160 \times 160$ & \textcolor{red}{2.25} & 0.9210 \\
+    Shale & XCT & $160 \times 160 \times 160$ & \textcolor{red}{2.25} & 0.8912 \\
     Sandstone & SEM &  $1280 \times 869$ & 0.10 & 0.9703 \\
@@
     \label{fig:sample-sandstone}}
+  \vskip\baselineskip
+  \subfigure[Soil]{
+    \includegraphics[width=0.45\linewidth]{images/soil.png}
+    \label{fig:sample-soil}}
+  \hfill
+  \subfigure[Shale]{
+    \includegraphics[width=0.45\linewidth]{images/shale.png}
+    \label{fig:sample-shale}}
   \caption[]{Images of samples used for calculation of higher-order correlation
@@
 \end{figure}
+
+\begin{figure*}[tp]
+  \centering
+  \subfigure[Shale]{
+    \includegraphics[width=0.45\linewidth]{images/shale-c3.png}
+    \label{fig:shale-s3}}
+  \hfill
+  \subfigure[Soil]{
+    \includegraphics[width=0.45\linewidth]{images/soil-s3.png}
+    \label{fig:soil-s3}}
+  \hfill
+  \caption[]{Heatmaps of $S_3$ function for highly anisotropic samples of shale
+    and soil. $S_3$ function was clamped to the range $[0, 0.1]$ to make
+    anisotropicity more visible.}
+  \label{fig:heatmaps}
+\end{figure*}
 

### 2023-11-27 data/heatmap.py

@@ -1,0 +1,13 @@
+#!/usr/bin/env python
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+data = np.load('shale-c3.npy')
+
+plt.figure(figsize = (8, 8), dpi = 300)
+plt.rc('font', size = 20)
+plt.imshow(np.where(data < 0.1, data, 0.1), extent = (0, 160*2.25, 0, 160*2.25))
+plt.xlabel(r'$x, \mu m$')
+plt.ylabel(r'$y, \mu m$')
+plt.savefig('../images/shale-c3.png')

### 2023-11-27 paper.tex
Minor fixes

@@
 Now we can define the three-point correlation function
-$S_3: \mathbb{R}^2 \rightarrow [0, 1]$:
+$S_3: \mathbb{R}^{2n} \rightarrow [0, 1]$:
 \begin{equation}
@@
 This algorithm has a better computational complexity compared with the previous
-algorithms if the whole correlation map is needed ($O(n \log n)$ vs
-$O(n^2)$). The whole correlation map, however, requires a lot of memory and is
-rarely needed. Imagine, that the input array $A$ is of dimensions
-$500 \times 500$. Then, considering that single precision floating point numbers
-are used, $4 \cdot 2 \cdot 500^4 / 1000^3 = 500$ GB are needed to store Fourier
-image of the map. Moreover, Fourier image of the whole map is needed even if
-only one element of the map in spatial domain is required. The aforementioned
-limitations render this approach very impractical.
+algorithms if the whole correlation map is needed ($O(n^2 \log n)$ vs
+$O(n^3)$ where $n$ is a number of elements in the input array). The whole
+correlation map, however, requires a lot of memory and is rarely
+needed. Imagine, that the input array $A$ is of dimensions $500 \times 500$.
+Then, considering that single precision floating point numbers are used,
+$4 \cdot 2 \cdot 500^4 / 1000^3 = 500$ GB are needed to store Fourier image of
+the map. Moreover, Fourier image of the whole map is needed even if only one
+element of the map in spatial domain is required. The aforementioned limitations
+render this approach very impractical.
 
@@
 \begin{equation}
-  f(x, y, z) = [(2x)^{\frac{3}{2}} + y^{\frac{3}{2}} + z^{\frac{3}{2}}]^{\frac{2}{3}}
+  f(x, y, z) = (|2x|^{\frac{3}{2}} + |y|^{\frac{3}{2}} + |z|^{\frac{3}{2}})^{\frac{2}{3}}
 \end{equation}
@@
 \item Computation in frequency domain using Fourier transform. This approach has
-  computational complexity $O(n \log n)$ and computes the whole correlation
+  computational complexity $O(n^2 \log n)$ and computes the whole correlation
   map. Unfortunately, it requires $O(n^2)$ additional memory and therefore can
@@
   CorrelationFunctions.jl package. This approach calculates the full map with
-  complexity $O(n^2)$ but uses only $O(n)$ additional memory for shifted
+  complexity $O(n^3)$ but uses only $O(n)$ additional memory for shifted
   versions of the input. For our purposes the whole map is not needed and
@@
 transform is the only linear transform which allows computation of convolution
-in $O(n)$. It is still an open question if there are linear transforms which
-allow computation of convolution with complexity between $O(n)$ and $O(n^2)$
+in linear time. It is still an open question if there are linear transforms which
+allow computation of convolution faster than a naïve approach
 \cite{stone2008uniqueness,stone1998convolution}.

### 2023-11-27 paper.tex
Extended analysis of the samples

@@
 these samples. Note that we compute surface correlation functions only for those
-samples for which the criterion $C_{0.5} > 0.97$ holds. Images of the samples
-are on \cref{fig:samples}. On plots of correlation functions we provide a family
-of curves with the first argument of the correlation function being fixed. For
-two highly anisotropic samples (the soil and the shale) we provide heatmaps of
-$S_3$ correlation function where anisotropicity can be easily seen. These two
-samples was preliminary rotated by $\frac{\pi}{4}$ around the axis $Z$ before
-calculation of correlation functions.
+samples for which the criterion $C_{0.5} > 0.97$ holds (the sandstone and the
+limestone). Images of the samples are on \cref{fig:samples}. On plots of
+correlation functions we provide a family of curves with the first argument of
+the correlation function being fixed. For two highly anisotropic samples (the
+soil and the shale) we provide heatmaps of $S_3$ correlation function where
+anisotropicity can be easily seen. These two samples was preliminary rotated by
+$\frac{\pi}{4}$ around the axis $Z$ before calculation of correlation functions.
 
-Correlation functions for the XCT sample are on
+Correlation functions for the XCT sample of the limestone are on
 \cref{fig:sample-limestone-cf}. The plot of $S_3$ function allows us to estimate
@@
 
-Correlation functions for the SEM sample are on
+Correlation functions for the SEM sample (the sandstone) are on
 \cref{fig:sample-sandstone-cf}. Porosity of the sample is $\sim 0.3$ as follows
@@
 Heatmaps of $S_3$ for the two highly anisotropic samples can be seen on
-\cref{fig:heatmaps}.
+\cref{fig:heatmaps}. Anisotropicity of the both samples can be seen as a slower
+decay of $S_3$ in one of the directions. Additionally, it can be observed that
+elongated clusters of the void phase in the sample of soil are parallel to each
+other and have a regular spacing about \textcolor{red}{$150 \mu m$}.
 
@@
     and soil. $S_3$ function was clamped to the range $[0, 0.1]$ to make
-    anisotropicity more visible.}
+    anisotropicity more visible. It can be observed that the samples have
+    cavities elongated along the vector $(1, 1, 0)$.}
   \label{fig:heatmaps}

### 2023-11-27 data/heatmap.py
Fix images

@@ -3,11 +3,11 @@
 import numpy as np
 import matplotlib.pyplot as plt
 
-data = np.load('shale-c3.npy')
+data = np.load('shale-s3.npy')
 
 plt.figure(figsize = (8, 8), dpi = 300)
 plt.rc('font', size = 20)
-plt.imshow(np.where(data < 0.1, data, 0.1), extent = (0, 160*2.25, 0, 160*2.25))
+plt.imshow(np.where(data < 0.1, data, 0.1), extent = (0, 160*2.25, 160*2.25, 0))
 plt.xlabel(r'$x, \mu m$')
 plt.ylabel(r'$y, \mu m$')
-plt.savefig('../images/shale-c3.png')
+plt.savefig('../images/shale-s3.png')

### 2023-11-29 paper.tex
Fix images
Reorder images
Remove textcolor

@@
 elongated clusters of the void phase in the sample of soil are parallel to each
-other and have a regular spacing about \textcolor{red}{$150 \mu m$}.
+other and have a regular spacing about $50 \mu m$.
 
@@
     Limestone & XCT &  $600 \times 600 \times 600$ & 3.02 & 0.9712 \\
-    Soil & XCT & $160 \times 160 \times 160$ & \textcolor{red}{2.25} & 0.9210 \\
-    Shale & XCT & $160 \times 160 \times 160$ & \textcolor{red}{2.25} & 0.8912 \\
+    Soil & XCT & $160 \times 160 \times 160$ & 2.25 & 0.9210 \\
+    Shale & XCT & $160 \times 160 \times 160$ & 2.25 & 0.8912 \\
     Sandstone & SEM &  $1280 \times 869$ & 0.10 & 0.9703 \\
@@
   \subfigure[Shale]{
-    \includegraphics[width=0.45\linewidth]{images/shale-c3.png}
+    \includegraphics[width=0.45\linewidth]{images/shale-s3.png}
     \label{fig:shale-s3}}
@@
   \centering
-  \includegraphics[width=0.3\linewidth]{images/aniso.png}
+  \includegraphics[width=0.4\linewidth, frame]{images/aniso.png}
+  \vskip\baselineskip
+  \includegraphics[width=0.45\linewidth]{images/aniso-s3.png}
   \hfill
-  \includegraphics[width=0.3\linewidth]{images/aniso-s3.png}
-  \hfill
-  \includegraphics[width=0.3\linewidth]{images/aniso-s3-avg.png}
+  \includegraphics[width=0.45\linewidth]{images/aniso-s3-avg.png}
   \caption[]{$S_3$ function for anisotropic media (on the left) elongated along

### 2023-11-29 paper.tex
New truangles

@@
   \includegraphics[width=0.5\linewidth]{images/pattern.png}
-  \caption[]{Pattern used for calculation of $S_3$ function in out
+  \caption[]{The pattern used for calculation of $S_3$ function in our
     implementation. Vectors $x_1$ and $x_2$ are parallel to one of the axes $X$,
-    $Y$ or $Z$ and have lengths $r_1$ and $r_2$ respectively. Red triangles
-    contribute to $S_3(2, 3)$ and blue triangles contribute to $S_3(1, 1)$.}
+    $Y$ or $Z$ and have lengths $r_1$ and $r_2$ respectively. A red triangle
+    contributes to $S_3(2, 6)$ and blue triangles contribute to $S_3(1, 1)$.}
   \label{fig:pattern}

### 2023-11-29 data/plot-s2.py
Make another plot of S₃ for balls

@@ -10,23 +10,34 @@ def s2_th(x, λ, R):
 s2 = np.load('test-s2.npy')
 xs = np.linspace(0, 0.5, s2.size)
 
+#plt.figure(figsize = (10, 8), dpi = 300)
+#plt.rc('font', size = 25)
+#plt.plot(xs, s2)
+#plt.plot(xs, s2_th(xs, 5000, 0.02))
+#plt.xlabel(r'$r$')
+#plt.ylabel(r'$S_3(0, r)$')
+#plt.ticklabel_format(axis = "y", scilimits = (0, 0), useMathText = True)
+#plt.ticklabel_format(axis = "x", scilimits = (0, 0), useMathText = True)
+#plt.legend(['Calculation', 'Theory'])
+#plt.savefig('../images/balls-s3.png')
+
+#plt.figure(figsize = (10, 8), dpi = 300)
+#plt.rc('font', size = 30)
+#plt.plot(xs, s2)
+#plt.plot(xs, s2_th(xs, 5000, 0.02))
+#plt.ticklabel_format(axis = "y", scilimits = (0, 0), useMathText = True)
+#plt.ticklabel_format(axis = "x", scilimits = (0, 0), useMathText = True)
+#plt.xlim([0.03, 0.06])
+#plt.ylim([0.71, 0.73])
+#plt.savefig('../images/balls-s3-zoom.png')
+
 plt.figure(figsize = (10, 8), dpi = 300)
 plt.rc('font', size = 25)
 plt.plot(xs, s2)
 plt.plot(xs, s2_th(xs, 5000, 0.02))
-plt.xlabel(r'$r$')
-plt.ylabel(r'$S_3(0, r)$')
 plt.ticklabel_format(axis = "y", scilimits = (0, 0), useMathText = True)
 plt.ticklabel_format(axis = "x", scilimits = (0, 0), useMathText = True)
+plt.xlim([0.025, 0.055])
+plt.ylim([0.71, 0.74])
 plt.legend(['Calculation', 'Theory'])
 plt.savefig('../images/balls-s3.png')
-
-plt.figure(figsize = (10, 8), dpi = 300)
-plt.rc('font', size = 30)
-plt.plot(xs, s2)
-plt.plot(xs, s2_th(xs, 5000, 0.02))
-plt.ticklabel_format(axis = "y", scilimits = (0, 0), useMathText = True)
[…]

### 2023-12-01 paper.tex
Replace an ellipsoid with a dumbbell

@@
 that function for sets defined by inequation $f(x) \le T$, $x \in \mathbb{R}^3$
-with help of automatic differentiation \cite{postnicov20232}. We choose $f$
+with help of automatic differentiation \cite{postnicov20232}. We choose $f$ as
 \begin{equation}
-  f(x, y, z) = (|2x|^{\frac{3}{2}} + |y|^{\frac{3}{2}} + |z|^{\frac{3}{2}})^{\frac{2}{3}}
+  f(x, y, z) = y^2 + z^2 - a x^2 (b^2 - x^2)
 \end{equation}
-so inequation $f(x, y, z) \le T$ gives us an ellipsoid-like object
-(\cref{fig:sss-ellipsoid}).
+and parameters $a = 10$, $b = 0.45$, $T = 10^{-2}$, so inequation
+$f(x, y, z) \le T$ gives us a dumbbell-like object (\cref{fig:sss-dumbbell}).
 
-The test was performed by evaluating the inequation with the parameter $T = 0.4$
-in a cube $[-1, 1]^3$ and comparing $F_{sss}$ calculated by our algorithm with
-precise values. Pointwise relative error of $F_{sss}$ is on
-\cref{fig:sss-ellipsoid-error}. Maximal relative error in the area bound by
-inequations $x > 0.1$, $y > 0.1$ and $f(x, y) < 0.78$ is about 10\%.
+The test was performed by firstly evaluating the inequation in a cube
+$[-1, 1]^3$ and obtaining precise values of $F_{sss}$ and secondly computing
+$F_{sss}$ with our algorithm, giving a discretized $400 \times 400 \times 400$
+pixels wide image as the input. Pointwise relative error of $F_{sss}$ is on
+\cref{fig:sss-dumbbell-error}. Maximal relative error in the area distanced
+farther than 0.1 (20 pixels) from curves of discontinuity (look at
+\cref{fig:sss-dumbbell-precise}) is no more than 20\%.
 \begin{figure*}[tp]
   \centering
-  \subfigure[The ellipsoid-like object used in testing of $F_{sss}$ computation]{
-    \includegraphics[width=0.45\linewidth]{images/ellipsoid.png}
-    \label{fig:sss-ellipsoid}}
+  \subfigure[The dumbbell-like object used in testing of $F_{sss}$ computation]{
+    \includegraphics[width=0.45\linewidth]{images/dumbbell.png}
+    \label{fig:sss-dumbbell}}
   \hfill
   \subfigure[Relative error of computation]{
-    \includegraphics[width=0.45\linewidth]{images/ellipsoid-sss-diff.png}
-    \label{fig:sss-ellipsoid-error}}
+    \includegraphics[width=0.45\linewidth]{images/dumbbell-sss-err.png}
+    \label{fig:sss-dumbbell-error}}
   \vskip\baselineskip
-  \subfigure[$F_{sss}$: precise]{
-    \includegraphics[width=0.45\linewidth]{images/ellipsoid-sss.png}}
+  \subfigure[$F_{sss}$: precise. The correlation function is undefined (has type
+    II discontinuity) at curves A, B and C.]{
+    \includegraphics[width=0.45\linewidth]{images/dumbbell-sss-precise.png}
+    \label{fig:sss-dumbbell-precise}}
   \hfill
   \subfigure[$F_{sss}$: calculated with our approach]{
-    \includegraphics[width=0.45\linewidth]{images/ellipsoid-sss-julia.png}}
+    \includegraphics[width=0.45\linewidth]{images/dumbbell-sss-julia.png}}
   \caption[]{A comparison of $F_{sss}$ function calculated using our approach

### 2023-12-01 paper.tex
Remake plots

@@
 
-The test was performed by firstly evaluating the inequation in a cube
+The test is performed by firstly evaluating the inequation in a cube
 $[-1, 1]^3$ and obtaining precise values of $F_{sss}$ and secondly computing
 $F_{sss}$ with our algorithm, giving a discretized $400 \times 400 \times 400$
-pixels wide image as the input. Pointwise relative error of $F_{sss}$ is on
+pixels wide image as the input. $F_{sss}$ function is evaluated in $XY$
+plane. Pointwise relative error of $F_{sss}$ is on
 \cref{fig:sss-dumbbell-error}. Maximal relative error in the area distanced

### 2023-12-01 data/heatmap.py

@@ -3,11 +3,11 @@
 import numpy as np
 import matplotlib.pyplot as plt
 
-data = np.load('shale-s3.npy')
+data = np.load('soil-s3.npy')
 
 plt.figure(figsize = (8, 8), dpi = 300)
 plt.rc('font', size = 20)
 plt.imshow(np.where(data < 0.1, data, 0.1), extent = (0, 160*2.25, 160*2.25, 0))
-plt.xlabel(r'$x, \mu m$')
-plt.ylabel(r'$y, \mu m$')
-plt.savefig('../images/shale-s3.png')
+plt.xlabel(r'$r_1 \cdot (1, 1, 0), \mu m$')
+plt.ylabel(r'$r_2 \cdot (-1, 1, 0), \mu m$')
+plt.savefig('../images/soil-s3.png')

### 2023-12-01 data/plot-s2.py

@@ -39,5 +39,7 @@ plt.ticklabel_format(axis = "y", scilimits = (0, 0), useMathText = True)
 plt.ticklabel_format(axis = "x", scilimits = (0, 0), useMathText = True)
 plt.xlim([0.025, 0.055])
 plt.ylim([0.71, 0.74])
+plt.xlabel(r'$r$')
+plt.ylabel(r'$S_3(0, r)$')
 plt.legend(['Calculation', 'Theory'])
 plt.savefig('../images/balls-s3.png')

### 2023-12-07 paper.tex
More about shift operator

@@
 \begin{equation}
-  C_3^n(x_1, x_2) = \sum_{k=1}^K \langle \tilde{I}_k(x) \tilde{I}_k(x + x_1) \tilde{I}_k(x + x_2) \rangle
+  C_3^n(x_1, x_2) = \sum_{k=1}^K \langle \tilde{I}_k(x) \tilde{I}_k(x + x_1)
+  \tilde{I}_k(x + x_2) \rangle
 \end{equation}
@@
 Three-point correlation function $S_3$ can be computed either in spatial domain
-or in frequency domain via the convolution theorem. The simplest algorithm below
+or in frequency domain via the convolution theorem. Suppose that a finite
+countable set $A$ is defined as a multidimensional array. A point $x$ belongs to
+a subset $A_n$ if and only if $A[x] = n$. The simplest algorithm below
 calculates $S_3$ pointwise in spatial domain:
@@
   \State $A_n \gets I_n (A)$
-  \State $A'_n \gets \mathfrak{S}(A_n, x_1)$
-  \State $A''_n \gets \mathfrak{S}(A_n, x_2)$
+  \Comment Apply $I_n$ to the input array elementwise.
+  \State $A'_n \gets \mathfrak{S}_{x_1}(A_n)$
+  \State $A''_n \gets \mathfrak{S}_{x_2}(A_n)$
   \State $T \gets A_n \cdot A'_n \cdot A''_n$
@@
 to shift $A_n$ by vectors $x_1$ and $x_2$. Finally, the three arrays are
-multiplied pointwise and normalized sum of all elements of the product is
+multiplied pointwise and a normalized sum of all elements of the product is
 returned.
 
-There are two common boundary conditions when applying $\mathfrak{S}$. The first
-condition is to extend $A_n$ periodically (\cref{fig:s3-periodic}) when
-accessing out-of-bounds array elements. This is the same as circular-shifting
-$A_n$. In this case $Norm(A, x_1, x_2)$ does not depend on $x_1$ and $x_2$ and
+There are two common boundary conditions when applying $\mathfrak{S}$. The
+first condition is to extend $A_n$ periodically (\cref{fig:s3-periodic}) when
+accessing out-of-bounds array elements. In this case $\mathfrak{S}_z$ is a
+circular shift operator:
+\begin{equation}
+  A[x] \leftarrow A[x+z \mod d]
+\end{equation}
+In this case $Norm(A, x_1, x_2)$ does not depend on $x_1$ and $x_2$ and
 is equal to the total number of elements in $A$. The second condition is to
@@
 (\cref{fig:s3-zeros}). A formula for $Norm(A, x_1, x_2)$ in this case is in
-\ref{sec:number-of-trials}.
+\ref{sec:number-of-trials} and $\mathfrak{S}_z$ is defined as follows:
+\begin{equation}
+  A[x] \leftarrow \left\{
+  \begin{array}{ll}
+    A[x+z] & \quad \text{if $x+z$ is a correct index in $A$} \\
+    0 & \quad \text{otherwise}
+  \end{array}
+  \right.
+\end{equation}
 \begin{figure*}[tp]
@@
   \State $A_n \gets E_n (A)$
-  \State $A'_n \gets \mathfrak{S}(A_n, x_1)$
-  \State $A''_n \gets \mathfrak{S}(A_n, x_2)$
+  \State $A'_n \gets \mathfrak{S}_{x_1}(A_n)$
+  \State $A''_n \gets \mathfrak{S}_{x_2}(A_n)$
   \State $T \gets A_n \cdot A'_n \cdot A''_n$
@@
   \State $A_{(void)} \gets I_{(void)} (A)$
-  \State $A'_n \gets \mathfrak{S}(A_n, x_1)$
-  \State $A'_{(void)} \gets \mathfrak{S}(A_{(void)}, x_2)$
+  \State $A'_n \gets \mathfrak{S}_{x_1}(A_n)$
+  \State $A'_{(void)} \gets \mathfrak{S}_{x_2}(A_{(void)})$
   \State $T \gets A_n \cdot A'_n \cdot A'_{(void)}$
@@
   \State $A_{(void)} \gets I_{(void)} (A)$
-  \State $A'_{(void)} \gets \mathfrak{S}(A_{(void)}, x_1)$
-  \State $A''_{(void)} \gets \mathfrak{S}(A_{(void)}, x_2)$
+  \State $A'_{(void)} \gets \mathfrak{S}_{x_1}(A_{(void)})$
+  \State $A''_{(void)} \gets \mathfrak{S}_{x_2}(A_{(void)})$
   \State $T \gets A_n \cdot A'_{(void)} \cdot A''_{(void)}$
@@
   \State $C_n \gets \mathfrak{C}(A_n)$
-  \State $C'_n \gets \mathfrak{S}(C_n, x_1)$
-  \State $C''_n \gets \mathfrak{S}(C_n, x_2)$
+  \State $C'_n \gets \mathfrak{S}_{x_1}(C_n)$
+  \State $C''_n \gets \mathfrak{S}_{x_2}(C_n)$
   \State $T \gets C_n \odot C'_n \odot C''_n$

### 2023-12-11 paper.tex
More about anisotropy

@@
 rotations or trial triangles. It is sensitive to anisotropicity of the medium
-when it is stretched along one of the axes as shown in \cref{fig:aniso}. The
-main advantage of our algorithm is its parallelizability and ease of
+when it is stretched along one of the axes as shown in \cref{fig:aniso}. A
+direction of elongation for a $N$-dimensional image can be easily detected by
+firstly evaluating a $N \times N$ covariance matrix for points belonging to the
+phase of interest:
+\begin{equation}
+  C_{ij} = \sum_{x \in \left\{ \text{Coordinates of points in the
+      phase of interest} \right\}} (x_i - \overline{x_i})(x_j - \overline{x_j})
+\end{equation}
+and then decomposing $C$ as $T \Lambda T^{-1}$ where $T$ is a unitary matrix and
+$\Lambda$ is diagonal. $T$ can always be made so that it defines a rotation and
+can be used to align the elongation with the axes (compare \cref{fig:aniso-unrot}
+and \cref{fig:aniso-rot}).
+
+The main advantage of our algorithm is its parallelizability and ease of
 implementation. An equivalent operation for rotation of test triangles is a
@@
   \centering
-  \includegraphics[width=0.4\linewidth, frame]{images/aniso.png}
+
+  \subfigure[An original image of an anisotropic pore.]{
+    \includegraphics[width=0.45\linewidth, frame]{images/aniso.png}
+    \label{fig:aniso-unrot}}
+  \hfill
+  \subfigure[A rotated image of pore, so it is elongated along the axis $X$.]{
+    \includegraphics[width=0.45\linewidth, frame]{images/aniso-rot.png}
+    \label{fig:aniso-rot}}
   \vskip\baselineskip
-  \includegraphics[width=0.45\linewidth]{images/aniso-s3.png}
+  \subfigure[$S_3$ function for the original image]{
+    \includegraphics[width=0.3\linewidth]{images/aniso-s3.png}}
   \hfill
-  \includegraphics[width=0.45\linewidth]{images/aniso-s3-avg.png}
-  \caption[]{$S_3$ function for anisotropic media (on the left) elongated along
-    the vector $(1, 1)$. Anisotropicity of the medium can be seen on a heatmap
-    of $S_3$ function (in the middle). An average of 120 $S_3$ evaluations of
-    the medium rotated by a random angle is on the right.}
+  \subfigure[$S_3$ function for the rotated image. A vector $(0.92, -0.4)$ is a
+    direction of elongation of the pore.]{
+  \includegraphics[width=0.3\linewidth]{images/aniso-rot-s3.png}}
+  \hfill
+  \subfigure[$S_3$ function averaged across 100 random rotations.]{
+    \includegraphics[width=0.3\linewidth]{images/aniso-avg-s3.png}
+    \label{fig:aniso-avg}}
+  \caption[]{Behaviour of our algorithm for calculation of the $S_3$ function
+    when dealing with highly anisotropic media. The pattern \cref{fig:pattern}
+    which we use in our algorithm is most sensitive to anisotropy which is
+    directed along one of the axes. A result on \cref{fig:aniso-avg} is similar
+    to the algorithm proposed by Malmir~et~al.}
   \label{fig:aniso}

### 2023-12-11 paper.tex
Anisotropicity -> anisotropy: it seems these words means the same

@@
 soil and the shale) we provide heatmaps of $S_3$ correlation function where
-anisotropicity can be easily seen. These two samples was preliminary rotated by
+anisotropy can be easily seen. These two samples was preliminary rotated by
 $\frac{\pi}{4}$ around the axis $Z$ before calculation of correlation functions.
@@
 Heatmaps of $S_3$ for the two highly anisotropic samples can be seen on
-\cref{fig:heatmaps}. Anisotropicity of the both samples can be seen as a slower
+\cref{fig:heatmaps}. Anisotropy of the both samples can be seen as a slower
 decay of $S_3$ in one of the directions. Additionally, it can be observed that
@@
     and soil. $S_3$ function was clamped to the range $[0, 0.1]$ to make
-    anisotropicity more visible. It can be observed that the samples have
+    anisotropy more visible. It can be observed that the samples have
     cavities elongated along the vector $(1, 1, 0)$.}
@@
 Our algorithm fixes $\theta = \frac{pi}{2}$ and does not perform random
-rotations or trial triangles. It is sensitive to anisotropicity of the medium
+rotations or trial triangles. It is sensitive to anisotropy of the medium
 when it is stretched along one of the axes as shown in \cref{fig:aniso}. A

### 2023-12-18 paper.tex
added intro

--- 2023-12-07 paper.tex
@@
 \newcommand{\code}[1]{\colorbox{light-gray}{\texttt{#1}}}
+\newcommand{\highlight}[1]{{\color{red}{#1}}} % convinient for revised version
 
@@
   Dolgoprudny, 141701, Russia}
-%\affiliation{\textsuperscript{3}Oil and Gas Research Institute Russian Academy
-%  of Sciences (OGRI RAS) 3, Gubkina st., Moscow, 119333, Russian Federation}
 
-\title{Another paper with lots of text and fancy pictures}
+\title{Evaluation of 3-point correlation functions from structural images on CPU and GPU architectures: accounting for anisotropy effects}
 
@@
 
-\section{Theoretical background}
+\section{Introduction}
+Structures, or spatial arrangements of matter and energy, including some fields (e.g., velocity or pressure) are ubiquitous in research applications and frequently require description for subsequent analysis.
+Examples of such objects for studies include galaxy formations \cite{springel2006}, immiscible multiphase fluid flow patterns \cite{hopkins2015new,balashov2021}, rock and soil samples \cite{rozenbaum2014,karsanina2015,ledesma2018,chen2020super,prokhorov2021digital,vogel2010}, food specimens \cite{derossi2019,nagdalian2021}, biological tissue \cite{park2020}, vortexes during flow \cite{gorbunova2016precessing} and interstellar turbulence \cite{portillo2018developing}.
+The scale of interest may span orders of magnitude from angstroms and nm for materials \cite{garum2020,gerke2021,khlyupin2023molecular} to millions of light-years for star clusters \cite{takada2003three,hopkins2013stars}.
+The studied structure can be non-static -- it will  change with time, and this dynamics is usually also of great interest \cite{jiao2013,fomin2023soil}.
+Thus, description of the structure is of utmost importance for numerous applications:
+\begin{enumerate}
+  \item Elucidation of structure--property relationships in the form of theoretical expression \cite{Torquato_book,Sahimi_book}, e.g., rigorous bounds and such;
+  \item Prediction of material physical properties using machine (deep) learning \cite{obayashi2018persistence,kamrava2020linking,roding2020predicting};
+  \item Description of complex structures and fields for taxonomy, comparison and analysis \cite{takada2003three,hopkins2013stars,shivashankar2015felix,saadatfar2017pore,portillo2018developing,KarsaninaEJSS,PNM_Morse,khlyupin2023molecular}, which may include temporal dynamics or surface evolution \cite{jiao2013,PhysRevE.92.023301,prokhorov2022,chen2022,fomin2023soil};
+  \item Morphological representativity \cite{capek2009,rozenbaum2014,gerke2019tensor} and spatial stationarity analysis \cite{REVpaper,LavrukhinPRE};
+  \item Stochastic reconstructions from limited amount of input data \cite{Adler_recon,Y-T,tahmasebiPRL,Euras2012,EPL2,karsaninaPRL,rozanski2023} in the form of limited dimension structures or correlation functions;
+  \item Compress structural information for storage, analysis, training (feature extraction), and retrieval (by means of stochastic reconstructions) \cite{jiao2007,SciRep1,Havelka,KarsaninaEJSS};
+  \item Multiscale image fusion that is usually necessary due to trade-off between field-of-view and imaging resolution \cite{SciRep1,Geoderma2018,chen2020super,karimpouli2022}.
+\end{enumerate}
+
+The number of possible descriptors to quantify spatial structure developed within different disciplines is stunning, for example: phase ratio or porosity \cite{anovitz2015characterization}, surface area, radial distribution functions \cite{zimm1948scattering,becker2010radial}, Minkowski functionals \cite{vogel2010} and tensors \cite{schroder2011minkowski}, correlation functions \cite{Torquato_book}, persistence diagrams \cite{shivashankar2015felix,saadatfar2017pore,obayashi2018persistence}.
+The evolution of such metrics was mainly induced by the ease of measurement and interpretation -- this is startling to observe holy wars on the question which metric is superior to flare up occasionally, e.g.,\cite{vogel2022holistic,yudina2023dual}.
+In fact, we need a single universal descriptor defined by only one characteristic -- information content.
+The latter is an ability of the metric to describe the structure at hand with 100$\%$ meaning the ability to fully recover the structure back from this metric.
+Thus, universal descriptor has to possess following key properties: (1) high information content, (2) easy to assess, (3) high compression (i.e., descriptor is much "smaller" than the structure itself).
+
+The large portion of the research papers mentioned above \cite{rozenbaum2014,karsanina2015,ledesma2018,derossi2019,portillo2018developing,takada2003three,hopkins2013stars,jiao2013,Torquato_book,roding2020predicting,KarsaninaEJSS,capek2009,gerke2019tensor,REVpaper,LavrukhinPRE,Adler_recon,Y-T,tahmasebiPRL,Euras2012,EPL2,karsaninaPRL,jiao2007,SciRep1,Havelka,Geoderma2018} is based on so-called correlation functions (CFs).
+These functions define a probability that some events are occurring withing the structure (with some special cases of surface functions), for example, 2-point probability $S_2$ measures the probability that both ends of the line segment are within the same phase, 2-point cluster function $C_2$ - that both ends of the line segment are within the same interconnected cluster of same phase, and lineal path $L_2$ measures the probability that the whole segment lies within the phase (see \highlight{Fig.1}).
+Compared to other descriptors, CFs possess a number of features making them, in our opinion, a perfect candidate for universal descriptor:
+\begin{enumerate}
+  \item They contain the majority of other metrics inside.
+For example, porosity is $S_2(0)$ (and at zero correlation length of the majority of correlation functions except for surface ones), surface area is represented by in the derivative at $S_2(0)$ \cite{debye1957scattering} or the value of $F_{ss}(0)$ (or $F_{sss}(0)$).
+Connectivity is described by cluster functions $C_2$ or $C_3$.
+Pore-size distribution is related to pore-size function and partially by $L_2$ and $S_3$.
+Surface-void functions are interconnected with mean curvature and Euler characteristic \cite{ma2020generation}.
+All together, the classic set of correlation functions describes both the geometry and topology of the structure at hand;
+  \item While the extent to which such classical set describes any arbitrary structure is not yet known, compared to other complex descriptors  where are known pathways to assess the information content of correlation functions -- there is a methodology for $S_2$ \cite{Gommes2} and approaches for other functions \cite{Degeneraty.045306,cherkasov2023towards};
+  \item In addition to a possibility to compute correlation functions using images or other structural data, i.e., similar to all other descriptors, some CFs can be also determined experimentally \cite{debye1957scattering,barrall1992nmr,dietrich1995scattering,li2018accurate};
+  \item Correlation functions can be scaled \cite{karsaninaPRL} or manipulated, for example, to add functions into a single one \cite{moctezuma2002};
+  \item As opposed to scalar metrics such as porosity, surface area or Minkowski functionals, CFs can be computed in directions and describe anisotropic structures;
+  \item Numerous rigorous bounds to obtain thermal, elastic, electromagnetic and transport properties are known, among which the most known (and least useful due to the impractically huge gap between the bounds) are Hashin-Strikman bounds \cite{hashin1963variational}.
+Other expressions based on integration of higher order $S_n$ are known and were found to be close to direct simulations \cite{brown1955solid,beran1965use,milton1981bounds,hlushkou2015effective};
+  \item One can control both the size of the CFs-based descriptor and the information content via correlation length, number of functions in the set (including directions \cite{EPL2}), and by the order of functions (e.g., 2- and 3-point versions, or even more points).
+\end{enumerate}
+This list highlights that correlations functions are indeed possess necessary properties so satisfy key criteria stated above.
+
+However, while 2-point CFs are computed and used in multitude of studies, higher order functions, for example, 3-point correlation functions are not that widely used.
+The reason for this is straightforward -- 3-point correlation functions are more involved and, thus, require much more computational resources to assess.
+It has been shown that the amount of additional information content with each increase in number of points $n$ decreases \cite{yao1993high,Gommes2}.
+The trade-off between additional information and computational burden is still not clear.
+Nonetheless, the computation of 3-point statistics is known to be advantageous at least in the number of applications as related to cosmology, astrophysics and turbulence patterns analysis as they can probe non-Gaussian signatures in the distribution of matter and energy, which are not captured in 2-point counterparts \cite{TakadaJain,hopkins2013stars,gorbunova2016precessing,yoo2022non}.
+
+In this contribution we continue our initiative to develop a simple, efficient and open-source solution to compute all classical correlation functions on CPU and GPU architectures -- \code{CorrelationFunctions.jl} \cite{CFsjlpaper}.
+Here we build upon previous results in computations of higher order functions with n > 2, most notably by Malmir et al.
+\cite{malmir2018}, and our aim is to develop robust and computationally efficient methods.
+In addition, we also considered the case of anisotropic structures and how to describe them with 3-point correlation functions similar to directional 2-point CFs \cite {10.1063/1.4867611,EPL1}.
+
+\highlight{The paper is organized as follows:}
+
+\section{Methods}
+\subsection{3-point correlation functions}
 Let $A_1, A_2, \dots, A_n$ be pairwise disjoint subsets of a set
-$A \subset \mathbb{R}^n$. We introduce a family of indicator functions
+$A \subset \mathbb{R}^n$, where the index can be interpreted as a phase on the image $A$. We introduce a family of indicator functions
 $I_n(x) : A \rightarrow \{0,1\}$ defined as:
@@
 Another function closely related to the three-point correlation function is the
-cluster function which can be defined as
+cluster function which can be defined as:
 \begin{equation}
-  C_3^n(x_1, x_2) = \sum_{k=1}^K \langle \tilde{I}_k(x) \tilde{I}_k(x + x_1)
-  \tilde{I}_k(x + x_2) \rangle
+  C_3^n(x_1, x_2) = \sum_{k=1}^K \langle \tilde{I}_k(x) \tilde{I}_k(x + x_1) \tilde{I}_k(x + x_2) \rangle
 \end{equation}
@@
 ($F_{sss}$), surface-surface-void function ($F_{ssv}$) and surface-void-void
-function ($F_{svv}$). They are defined as
+function ($F_{svv}$). They are defined as:
 \begin{align}
@@
 
-\section{Computational algorithms}
+\subsection{Computational algorithms}
 Three-point correlation function $S_3$ can be computed either in spatial domain
-or in frequency domain via the convolution theorem. Suppose that a finite
-countable set $A$ is defined as a multidimensional array. A point $x$ belongs to
-a subset $A_n$ if and only if $A[x] = n$. The simplest algorithm below
+or in frequency domain via the convolution theorem. The simplest algorithm below
 calculates $S_3$ pointwise in spatial domain:
@@
   \State $A_n \gets I_n (A)$
-  \Comment Apply $I_n$ to the input array elementwise.
-  \State $A'_n \gets \mathfrak{S}_{x_1}(A_n)$
-  \State $A''_n \gets \mathfrak{S}_{x_2}(A_n)$
+  \State $A'_n \gets \mathfrak{S}(A_n, x_1)$
+  \State $A''_n \gets \mathfrak{S}(A_n, x_2)$
   \State $T \gets A_n \cdot A'_n \cdot A''_n$
@@
 to shift $A_n$ by vectors $x_1$ and $x_2$. Finally, the three arrays are
-multiplied pointwise and a normalized sum of all elements of the product is
+multiplied pointwise and normalized sum of all elements of the product is
 returned.
 
-There are two common boundary conditions when applying $\mathfrak{S}$. The
-first condition is to extend $A_n$ periodically (\cref{fig:s3-periodic}) when
-accessing out-of-bounds array elements. In this case $\mathfrak{S}_z$ is a
-circular shift operator:
-\begin{equation}
-  A[x] \leftarrow A[x+z \mod d]
-\end{equation}
-In this case $Norm(A, x_1, x_2)$ does not depend on $x_1$ and $x_2$ and
+There are two common boundary conditions when applying $\mathfrak{S}$. The first
+condition is to extend $A_n$ periodically (\cref{fig:s3-periodic}) when
+accessing out-of-bounds array elements. This is the same as circular-shifting
+$A_n$. In this case $Norm(A, x_1, x_2)$ does not depend on $x_1$ and $x_2$ and
 is equal to the total number of elements in $A$. The second condition is to
@@
 (\cref{fig:s3-zeros}). A formula for $Norm(A, x_1, x_2)$ in this case is in
-\ref{sec:number-of-trials} and $\mathfrak{S}_z$ is defined as follows:
-\begin{equation}
-  A[x] \leftarrow \left\{
-  \begin{array}{ll}
-    A[x+z] & \quad \text{if $x+z$ is a correct index in $A$} \\
-    0 & \quad \text{otherwise}
-  \end{array}
-  \right.
-\end{equation}
+\ref{sec:number-of-trials}.
 \begin{figure*}[tp]
@@
 domain. Suppose we have a function
-$f: \mathbb{R} \rightarrow \mathbb{R}$. Triple correlation for this function is
-a function
+$f: \mathbb{R} \rightarrow \mathbb{R}$. Triple correlation for this function is:
 \begin{equation}
-  g(t_1, t_2) = \int f(\tau) f(\tau + t_1) f(\tau + t_2) d \tau
+  g(t_1, t_2) = \int f(\tau) f(\tau + t_1) f(\tau + t_2) d \tau.
 \end{equation}
@@
 element of the map in spatial domain is required. The aforementioned limitations
-render this approach very impractical.
+render this approach impractical.
 
@@
   \State $A_n \gets E_n (A)$
-  \State $A'_n \gets \mathfrak{S}_{x_1}(A_n)$
-  \State $A''_n \gets \mathfrak{S}_{x_2}(A_n)$
+  \State $A'_n \gets \mathfrak{S}(A_n, x_1)$
+  \State $A''_n \gets \mathfrak{S}(A_n, x_2)$
   \State $T \gets A_n \cdot A'_n \cdot A''_n$
@@
   \State $A_{(void)} \gets I_{(void)} (A)$
-  \State $A'_n \gets \mathfrak{S}_{x_1}(A_n)$
-  \State $A'_{(void)} \gets \mathfrak{S}_{x_2}(A_{(void)})$
+  \State $A'_n \gets \mathfrak{S}(A_n, x_1)$
+  \State $A'_{(void)} \gets \mathfrak{S}(A_{(void)}, x_2)$
   \State $T \gets A_n \cdot A'_n \cdot A'_{(void)}$
@@
   \State $A_{(void)} \gets I_{(void)} (A)$
-  \State $A'_{(void)} \gets \mathfrak{S}_{x_1}(A_{(void)})$
-  \State $A''_{(void)} \gets \mathfrak{S}_{x_2}(A_{(void)})$
+  \State $A'_{(void)} \gets \mathfrak{S}(A_{(void)}, x_1)$
+  \State $A''_{(void)} \gets \mathfrak{S}(A_{(void)}, x_2)$
   \State $T \gets A_n \cdot A'_{(void)} \cdot A''_{(void)}$
@@
 $C_{0.5} > 0.97$ holds then the image is suitable for application of
-aforementioned algorithms for calculation of surface functions.
+aforementioned algorithms for calculation of surface functions, otherwise image's resolution
+can be improved with the help of interpolation prior to computations \cite{samarin2023robust}.
 
@@
 algorithm \cite{4728561,PhysRevB.14.3438} to label clusters. Then, again, a
-slightly modified algorithm for $S_3$ is used.
+slightly modified algorithm for $S_3$ is used to assess cluster function:
 \begin{algorithmic}[1]
@@
   \State $C_n \gets \mathfrak{C}(A_n)$
-  \State $C'_n \gets \mathfrak{S}_{x_1}(C_n)$
-  \State $C''_n \gets \mathfrak{S}_{x_2}(C_n)$
+  \State $C'_n \gets \mathfrak{S}(C_n, x_1)$
+  \State $C''_n \gets \mathfrak{S}(C_n, x_2)$
   \State $T \gets C_n \odot C'_n \odot C''_n$
@@
     1 & \quad x = y \\
-    0 & \quad \text{otherwise}
+    0 & \quad \text{otherwise}.
   \end{array}
@@
 
-\section{Verification}
+\section{Results}
+\subsection{Verification}
 To verify correctness of computation of $S_3$ and $C_3$ functions we use the
@@
       1 + \frac{3}{4} \frac{r}{R} - \frac{1}{16} (\frac{r}{R})^3 & \quad r < 2R \\
-      2 & \quad \text{otherwise}
+      2 & \quad \text{otherwise}.
     \end{array}
@@
 $\lambda=5000$ and a cube $[0, 1]^3$. Because $R \ll 1$, we can use
-\cref{eq:s2-balls} to verify our computations what we do on
+\cref{eq:s2-balls} to verify our computations -- this is exactly what we present on
 \cref{fig:balls-s3-comparison}.
@@
 To test $F_{sss}$ function we use a recently developed approach which computes
-that function for sets defined by inequation $f(x) \le T$, $x \in \mathbb{R}^3$
-with help of automatic differentiation \cite{postnicov20232}. We choose $f$ as
+that function for sets defined by inequality $f(x) \le T$, $x \in \mathbb{R}^3$
+with help of automatic differentiation \cite{postnicov20232}. We choose $f$ as:
 \begin{equation}
@@
 \cref{fig:sss-dumbbell-error}. Maximal relative error in the area distanced
-farther than 0.1 (20 pixels) from curves of discontinuity (look at
+farther than 0.1 (20 pixels) from curves of discontinuity (see
 \cref{fig:sss-dumbbell-precise}) is no more than 20\%.
@@
 To test $F_{ssv}$ and $F_{svv}$ we use the following relations for such a set
-$A$ where all non-void phase is covered by a ball $\mathfrak{O}(R)$:
+$A$ where all non-void phase is covered by a ball with radius $R$:
 \begin{align}
@@
 \end{align}
-The comparison of our algorithm against theory is on
-\cref{fig:surface-verification}. Radius of the ball is chosen $R=0.2$.
+The comparison of our algorithm against theory is shown on
+\cref{fig:surface-verification}. Radius of the ball is chosen to be $R=0.2$.
 \begin{figure*}[tp]
@@
 
-\section{Results}
+\subsection{Applications to material images}
 In this section we compute correlation functions along the plane $XY$ for 2- and
@@
 soil and the shale) we provide heatmaps of $S_3$ correlation function where
-anisotropicity can be easily seen. These two samples was preliminary rotated by
+anisotropy can be easily observed. These two samples were preliminary rotated by
 $\frac{\pi}{4}$ around the axis $Z$ before calculation of correlation functions.
@@
 points in the void phase are independent if the points are farther than
-$225\ \mu m$ from each other. We see that the sample is a little bit anisotropic
+$225\ \mu m$ from each other. We see that the sample is slightly anisotropic
 ($S_3(0, 225) \approx S_3(150, 0)$). From analysis of $C_3$ function it can be
@@
 elongated clusters of the void phase in the sample of soil are parallel to each
-other and have a regular spacing about $50 \mu m$.
+other and have a regular spacing of about $50 \mu m$.
 
@@
 
+We mentioned that classic set of correlation functions describes
+both the geometry and topology of the structure at hand - but this is to yet unknown extent.
+With the advent of analytical methods \cite{cherkasov2023towards} to assess information content of arbitrary descriptor for structure of any size, it will be possible to choose the most useful set of correlation functions and compare their information content against classical and other metrics.
+
 Our algorithm fixes $\theta = \frac{pi}{2}$ and does not perform random
@@
 \end{equation}
-For 3D case $S=172.96$ and for 2D case $S=30.46$.
+For 3D case $S=172.96$ and for 2D case $S=30.46$ \cite{postnicov20232}.
 

### 2023-12-19 paper.tex

@@
 Our algorithm fixes $\theta = \frac{pi}{2}$ and does not perform random
-rotations or trial triangles. It is sensitive to anisotropicity of the medium
-when it is stretched along one of the axes as shown in \cref{fig:aniso}. The
-main advantage of our algorithm is its parallelizability and ease of
+rotations or trial triangles. It is sensitive to anisotropy of the medium
+when it is stretched along one of the axes as shown in \cref{fig:aniso}. A
+direction of elongation for a $N$-dimensional image can be easily detected by
+firstly evaluating a $N \times N$ covariance matrix for points belonging to the
+phase of interest:
+\begin{equation}
+  C_{ij} = \sum_{x \in \left\{ \text{Coordinates of points in the
+      phase of interest} \right\}} (x_i - \overline{x_i})(x_j - \overline{x_j})
+\end{equation}
+and then decomposing $C$ as $T \Lambda T^{-1}$ where $T$ is a unitary matrix and
+$\Lambda$ is diagonal. $T$ can always be made so that it defines a rotation and
+can be used to align the elongation with the axes (compare \cref{fig:aniso-unrot}
+and \cref{fig:aniso-rot}).
+
+The main advantage of our algorithm is its parallelizability and ease of
 implementation. An equivalent operation for rotation of test triangles is a

### 2023-12-19 paper.tex
Fix formatting

@@
 
-\title{Evaluation of 3-point correlation functions from structural images on CPU and GPU architectures: accounting for anisotropy effects}
+\title{Evaluation of 3-point correlation functions from structural images on CPU
+  and GPU architectures: accounting for anisotropy effects}
 
@@
 \section{Introduction}
-Structures, or spatial arrangements of matter and energy, including some fields (e.g., velocity or pressure) are ubiquitous in research applications and frequently require description for subsequent analysis.
-Examples of such objects for studies include galaxy formations \cite{springel2006}, immiscible multiphase fluid flow patterns \cite{hopkins2015new,balashov2021}, rock and soil samples \cite{rozenbaum2014,karsanina2015,ledesma2018,chen2020super,prokhorov2021digital,vogel2010}, food specimens \cite{derossi2019,nagdalian2021}, biological tissue \cite{park2020}, vortexes during flow \cite{gorbunova2016precessing} and interstellar turbulence \cite{portillo2018developing}.
-The scale of interest may span orders of magnitude from angstroms and nm for materials \cite{garum2020,gerke2021,khlyupin2023molecular} to millions of light-years for star clusters \cite{takada2003three,hopkins2013stars}.
-The studied structure can be non-static -- it will  change with time, and this dynamics is usually also of great interest \cite{jiao2013,fomin2023soil}.
-Thus, description of the structure is of utmost importance for numerous applications:
+Structures, or spatial arrangements of matter and energy, including some fields
+(e.g., velocity or pressure) are ubiquitous in research applications and
+frequently require description for subsequent analysis. Examples of such objects
+for studies include galaxy formations \cite{springel2006}, immiscible multiphase
+fluid flow patterns \cite{hopkins2015new,balashov2021}, rock and soil samples
+\cite{rozenbaum2014,karsanina2015,ledesma2018,chen2020super,prokhorov2021digital,vogel2010},
+food specimens \cite{derossi2019,nagdalian2021}, biological tissue
+\cite{park2020}, vortexes during flow \cite{gorbunova2016precessing} and
+interstellar turbulence \cite{portillo2018developing}. The scale of interest may
+span orders of magnitude from angstroms and nm for materials
+\cite{garum2020,gerke2021,khlyupin2023molecular} to millions of light-years for
+star clusters \cite{takada2003three,hopkins2013stars}. The studied structure can
+be non-static -- it will change with time, and this dynamics is usually also of
+great interest \cite{jiao2013,fomin2023soil}. Thus, description of the structure
+is of utmost importance for numerous applications:
 \begin{enumerate}
-  \item Elucidation of structure--property relationships in the form of theoretical expression \cite{Torquato_book,Sahimi_book}, e.g., rigorous bounds and such;
-  \item Prediction of material physical properties using machine (deep) learning \cite{obayashi2018persistence,kamrava2020linking,roding2020predicting};
-  \item Description of complex structures and fields for taxonomy, comparison and analysis \cite{takada2003three,hopkins2013stars,shivashankar2015felix,saadatfar2017pore,portillo2018developing,KarsaninaEJSS,PNM_Morse,khlyupin2023molecular}, which may include temporal dynamics or surface evolution \cite{jiao2013,PhysRevE.92.023301,prokhorov2022,chen2022,fomin2023soil};
-  \item Morphological representativity \cite{capek2009,rozenbaum2014,gerke2019tensor} and spatial stationarity analysis \cite{REVpaper,LavrukhinPRE};
-  \item Stochastic reconstructions from limited amount of input data \cite{Adler_recon,Y-T,tahmasebiPRL,Euras2012,EPL2,karsaninaPRL,rozanski2023} in the form of limited dimension structures or correlation functions;
-  \item Compress structural information for storage, analysis, training (feature extraction), and retrieval (by means of stochastic reconstructions) \cite{jiao2007,SciRep1,Havelka,KarsaninaEJSS};
-  \item Multiscale image fusion that is usually necessary due to trade-off between field-of-view and imaging resolution \cite{SciRep1,Geoderma2018,chen2020super,karimpouli2022}.
+  \item Elucidation of structure--property relationships in the form of
+    theoretical expression \cite{Torquato_book,Sahimi_book}, e.g., rigorous
+    bounds and such;
+  \item Prediction of material physical properties using machine (deep) learning
+    \cite{obayashi2018persistence,kamrava2020linking,roding2020predicting};
+  \item Description of complex structures and fields for taxonomy, comparison
+    and analysis
+    \cite{takada2003three,hopkins2013stars,shivashankar2015felix,saadatfar2017pore,
+      portillo2018developing,KarsaninaEJSS,PNM_Morse,khlyupin2023molecular},
+    which may include temporal dynamics or surface evolution
+    \cite{jiao2013,PhysRevE.92.023301,prokhorov2022,chen2022,fomin2023soil};
+  \item Morphological representativity
+    \cite{capek2009,rozenbaum2014,gerke2019tensor} and spatial stationarity
+    analysis \cite{REVpaper,LavrukhinPRE};
+  \item Stochastic reconstructions from limited amount of input data
+    \cite{Adler_recon,Y-T,tahmasebiPRL,Euras2012,EPL2,karsaninaPRL,rozanski2023}
+    in the form of limited dimension structures or correlation functions;
+  \item Compress structural information for storage, analysis, training (feature
+    extraction), and retrieval (by means of stochastic reconstructions)
+    \cite{jiao2007,SciRep1,Havelka,KarsaninaEJSS};
+  \item Multiscale image fusion that is usually necessary due to trade-off
+    between field-of-view and imaging resolution
+    \cite{SciRep1,Geoderma2018,chen2020super,karimpouli2022}.
 \end{enumerate}
 
-The number of possible descriptors to quantify spatial structure developed within different disciplines is stunning, for example: phase ratio or porosity \cite{anovitz2015characterization}, surface area, radial distribution functions \cite{zimm1948scattering,becker2010radial}, Minkowski functionals \cite{vogel2010} and tensors \cite{schroder2011minkowski}, correlation functions \cite{Torquato_book}, persistence diagrams \cite{shivashankar2015felix,saadatfar2017pore,obayashi2018persistence}.
-The evolution of such metrics was mainly induced by the ease of measurement and interpretation -- this is startling to observe holy wars on the question which metric is superior to flare up occasionally, e.g.,\cite{vogel2022holistic,yudina2023dual}.
-In fact, we need a single universal descriptor defined by only one characteristic -- information content.
-The latter is an ability of the metric to describe the structure at hand with 100$\%$ meaning the ability to fully recover the structure back from this metric.
-Thus, universal descriptor has to possess following key properties: (1) high information content, (2) easy to assess, (3) high compression (i.e., descriptor is much "smaller" than the structure itself).
+The number of possible descriptors to quantify spatial structure developed
+within different disciplines is stunning, for example: phase ratio or porosity
+\cite{anovitz2015characterization}, surface area, radial distribution functions
+\cite{zimm1948scattering,becker2010radial}, Minkowski functionals
+\cite{vogel2010} and tensors \cite{schroder2011minkowski}, correlation functions
+\cite{Torquato_book}, persistence diagrams
+\cite{shivashankar2015felix,saadatfar2017pore,obayashi2018persistence}. The
+evolution of such metrics was mainly induced by the ease of measurement and
+interpretation -- this is startling to observe holy wars on the question which
+metric is superior to flare up occasionally,
+e.g.,\cite{vogel2022holistic,yudina2023dual}. In fact, we need a single
+universal descriptor defined by only one characteristic -- information
+content. The latter is an ability of the metric to describe the structure at
+hand with 100$\%$ meaning the ability to fully recover the structure back from
+this metric. Thus, universal descriptor has to possess following key properties:
+(1) high information content, (2) easy to assess, (3) high compression (i.e.,
+descriptor is much "smaller" than the structure itself).
 
-The large portion of the research papers mentioned above \cite{rozenbaum2014,karsanina2015,ledesma2018,derossi2019,portillo2018developing,takada2003three,hopkins2013stars,jiao2013,Torquato_book,roding2020predicting,KarsaninaEJSS,capek2009,gerke2019tensor,REVpaper,LavrukhinPRE,Adler_recon,Y-T,tahmasebiPRL,Euras2012,EPL2,karsaninaPRL,jiao2007,SciRep1,Havelka,Geoderma2018} is based on so-called correlation functions (CFs).
-These functions define a probability that some events are occurring withing the structure (with some special cases of surface functions), for example, 2-point probability $S_2$ measures the probability that both ends of the line segment are within the same phase, 2-point cluster function $C_2$ - that both ends of the line segment are within the same interconnected cluster of same phase, and lineal path $L_2$ measures the probability that the whole segment lies within the phase (see \highlight{Fig.1}).
-Compared to other descriptors, CFs possess a number of features making them, in our opinion, a perfect candidate for universal descriptor:
+The large portion of the research papers mentioned above
+\cite{rozenbaum2014,karsanina2015,ledesma2018,derossi2019,portillo2018developing,
+  takada2003three,hopkins2013stars,jiao2013,Torquato_book,roding2020predicting,
+  KarsaninaEJSS,capek2009,gerke2019tensor,REVpaper,LavrukhinPRE,Adler_recon,Y-T,
+  tahmasebiPRL,Euras2012,EPL2,karsaninaPRL,jiao2007,SciRep1,Havelka,Geoderma2018}
+is based on so-called correlation functions (CFs). These functions define a
+probability that some events are occurring withing the structure (with some
+special cases of surface functions), for example, 2-point probability $S_2$
+measures the probability that both ends of the line segment are within the same
+phase, 2-point cluster function $C_2$ -- that both ends of the line segment are
+within the same interconnected cluster of same phase, and lineal path $L_2$
+measures the probability that the whole segment lies within the phase (see
+\highlight{Fig.1}). Compared to other descriptors, CFs possess a number of
+features making them, in our opinion, a perfect candidate for universal
+descriptor:
 \begin{enumerate}
-  \item They contain the majority of other metrics inside.
-For example, porosity is $S_2(0)$ (and at zero correlation length of the majority of correlation functions except for surface ones), surface area is represented by in the derivative at $S_2(0)$ \cite{debye1957scattering} or the value of $F_{ss}(0)$ (or $F_{sss}(0)$).
-Connectivity is described by cluster functions $C_2$ or $C_3$.
-Pore-size distribution is related to pore-size function and partially by $L_2$ and $S_3$.
-Surface-void functions are interconnected with mean curvature and Euler characteristic \cite{ma2020generation}.
-All together, the classic set of correlation functions describes both the geometry and topology of the structure at hand;
-  \item While the extent to which such classical set describes any arbitrary structure is not yet known, compared to other complex descriptors  where are known pathways to assess the information content of correlation functions -- there is a methodology for $S_2$ \cite{Gommes2} and approaches for other functions \cite{Degeneraty.045306,cherkasov2023towards};
-  \item In addition to a possibility to compute correlation functions using images or other structural data, i.e., similar to all other descriptors, some CFs can be also determined experimentally \cite{debye1957scattering,barrall1992nmr,dietrich1995scattering,li2018accurate};
-  \item Correlation functions can be scaled \cite{karsaninaPRL} or manipulated, for example, to add functions into a single one \cite{moctezuma2002};
-  \item As opposed to scalar metrics such as porosity, surface area or Minkowski functionals, CFs can be computed in directions and describe anisotropic structures;
-  \item Numerous rigorous bounds to obtain thermal, elastic, electromagnetic and transport properties are known, among which the most known (and least useful due to the impractically huge gap between the bounds) are Hashin-Strikman bounds \cite{hashin1963variational}.
-Other expressions based on integration of higher order $S_n$ are known and were found to be close to direct simulations \cite{brown1955solid,beran1965use,milton1981bounds,hlushkou2015effective};
-  \item One can control both the size of the CFs-based descriptor and the information content via correlation length, number of functions in the set (including directions \cite{EPL2}), and by the order of functions (e.g., 2- and 3-point versions, or even more points).
+  \item They contain the majority of other metrics inside. For example, porosity
+    is $S_2(0)$ (and at zero correlation length of the majority of correlation
+    functions except for surface ones), surface area is represented by in the
+    derivative at $S_2(0)$ \cite{debye1957scattering} or the value of
+    $F_{ss}(0)$ (or $F_{sss}(0)$). Connectivity is described by cluster
+    functions $C_2$ or $C_3$. Pore-size distribution is related to pore-size
+    function and partially by $L_2$ and $S_3$. Surface-void functions are
+    interconnected with mean curvature and Euler characteristic
+    \cite{ma2020generation}. All together, the classic set of correlation
+    functions describes both the geometry and topology of the structure at hand;
+  \item While the extent to which such classical set describes any arbitrary
+    structure is not yet known, compared to other complex descriptors where are
+    known pathways to assess the information content of correlation functions --
+    there is a methodology for $S_2$ \cite{Gommes2} and approaches for other
+    functions \cite{Degeneraty.045306,cherkasov2023towards};
+  \item In addition to a possibility to compute correlation functions using
+    images or other structural data, i.e., similar to all other descriptors,
+    some CFs can be also determined experimentally
+    \cite{debye1957scattering,barrall1992nmr,dietrich1995scattering,li2018accurate};
+  \item Correlation functions can be scaled \cite{karsaninaPRL} or manipulated,
+    for example, to add functions into a single one \cite{moctezuma2002};
+  \item As opposed to scalar metrics such as porosity, surface area or Minkowski
+    functionals, CFs can be computed in directions and describe anisotropic
+    structures;
+  \item Numerous rigorous bounds to obtain thermal, elastic, electromagnetic and
+    transport properties are known, among which the most known (and least useful
+    due to the impractically huge gap between the bounds) are Hashin-Strikman
+    bounds \cite{hashin1963variational}. Other expressions based on integration
+    of higher order $S_n$ are known and were found to be close to direct
+    simulations
+    \cite{brown1955solid,beran1965use,milton1981bounds,hlushkou2015effective};
+  \item One can control both the size of the CFs-based descriptor and the
+    information content via correlation length, number of functions in the set
+    (including directions \cite{EPL2}), and by the order of functions (e.g., 2-
+    and 3-point versions, or even more points).
 \end{enumerate}
-This list highlights that correlations functions are indeed possess necessary properties so satisfy key criteria stated above.
+This list highlights that correlations functions are indeed possess necessary
+properties so satisfy key criteria stated above.
 
-However, while 2-point CFs are computed and used in multitude of studies, higher order functions, for example, 3-point correlation functions are not that widely used.
-The reason for this is straightforward -- 3-point correlation functions are more involved and, thus, require much more computational resources to assess.
-It has been shown that the amount of additional information content with each increase in number of points $n$ decreases \cite{yao1993high,Gommes2}.
-The trade-off between additional information and computational burden is still not clear.
-Nonetheless, the computation of 3-point statistics is known to be advantageous at least in the number of applications as related to cosmology, astrophysics and turbulence patterns analysis as they can probe non-Gaussian signatures in the distribution of matter and energy, which are not captured in 2-point counterparts \cite{TakadaJain,hopkins2013stars,gorbunova2016precessing,yoo2022non}.
+However, while 2-point CFs are computed and used in multitude of studies, higher
+order functions, for example, 3-point correlation functions are not that widely
+used. The reason for this is straightforward -- 3-point correlation functions
+are more involved and, thus, require much more computational resources to
+assess. It has been shown that the amount of additional information content with
+each increase in number of points $n$ decreases \cite{yao1993high,Gommes2}. The
+trade-off between additional information and computational burden is still not
+clear. Nonetheless, the computation of 3-point statistics is known to be
+advantageous at least in the number of applications as related to cosmology,
+astrophysics and turbulence patterns analysis as they can probe non-Gaussian
+signatures in the distribution of matter and energy, which are not captured in
+2-point counterparts
+\cite{TakadaJain,hopkins2013stars,gorbunova2016precessing,yoo2022non}.
 
-In this contribution we continue our initiative to develop a simple, efficient and open-source solution to compute all classical correlation functions on CPU and GPU architectures -- \code{CorrelationFunctions.jl} \cite{CFsjlpaper}.
-Here we build upon previous results in computations of higher order functions with n > 2, most notably by Malmir et al.
-\cite{malmir2018}, and our aim is to develop robust and computationally efficient methods.
-In addition, we also considered the case of anisotropic structures and how to describe them with 3-point correlation functions similar to directional 2-point CFs \cite {10.1063/1.4867611,EPL1}.
+In this contribution we continue our initiative to develop a simple, efficient
+and open-source solution to compute all classical correlation functions on CPU
+and GPU architectures -- \code{CorrelationFunctions.jl} \cite{CFsjlpaper}. Here
+we build upon previous results in computations of higher order functions with n
+> 2, most notably by Malmir et al. \cite{malmir2018}, and our aim is to develop
+robust and computationally efficient methods. In addition, we also considered
+the case of anisotropic structures and how to describe them with 3-point
+correlation functions similar to directional 2-point CFs \cite
+{10.1063/1.4867611,EPL1}.
 
@@
 Let $A_1, A_2, \dots, A_n$ be pairwise disjoint subsets of a set
-$A \subset \mathbb{R}^n$, where the index can be interpreted as a phase on the image $A$. We introduce a family of indicator functions
+$A \subset \mathbb{R}^n$, where the index can be interpreted as a phase on the
+image $A$. We introduce a family of indicator functions
 $I_n(x) : A \rightarrow \{0,1\}$ defined as:
@@
 $C_{0.5} > 0.97$ holds then the image is suitable for application of
-aforementioned algorithms for calculation of surface functions, otherwise image's resolution
-can be improved with the help of interpolation prior to computations \cite{samarin2023robust}.
+aforementioned algorithms for calculation of surface functions, otherwise
+image's resolution can be improved with the help of interpolation prior to
+computations \cite{samarin2023robust}.
 
@@
 We mentioned that classic set of correlation functions describes
-both the geometry and topology of the structure at hand - but this is to yet unknown extent.
-With the advent of analytical methods \cite{cherkasov2023towards} to assess information content of arbitrary descriptor for structure of any size, it will be possible to choose the most useful set of correlation functions and compare their information content against classical and other metrics.
+both the geometry and topology of the structure at hand -- but this is to yet
+unknown extent. With the advent of analytical methods
+\cite{cherkasov2023towards} to assess information content of arbitrary
+descriptor for structure of any size, it will be possible to choose the most
+useful set of correlation functions and compare their information content
+against classical and other metrics.
 

### 2023-12-19 paper.tex
Change documentclass to revtex4-1

@@
-\documentclass[1p]{elsarticle}
+\documentclass[reprint,amsmath,amssymb,aps,pre,showkeys,showpacs]{revtex4-1}
 
@@
 \usepackage[T1]{fontenc}
-\usepackage{amsmath}
-\usepackage{amssymb}
 \usepackage{bm}
@@
 
-\bibliographystyle{elsarticle-num}
-\journal{Physica A: Statistical Mechanics and its Applications}
+\begin{document}
+\preprint{APS/123-QED}
 
-\begin{document}
+\author{Vasily~Postnicov\textsuperscript{1}}
+\author{Marina~V.~Karsanina\textsuperscript{1}}
+\author{Aleksey~Khlyupin\textsuperscript{1,2}}
+\author{Kirill~M.~Gerke\textsuperscript{1}}
+\email{kg@ifz.ru}
 
-\author[Smith]{Vasily~Postnicov}
-\author[Smith]{Marina~V.~Karsanina}
-\author[Smith,MIT]{Aleksey~Khlyupin}
-\author[Smith]{Kirill~M.~Gerke\corref{maincorr}}
-\cortext[maincorr]{Corresponding author}
-\ead{kg@ifz.ru}
-
-\address[Smith]{Schmidt Institute of Physics of the Earth of Russian Academy of
-  Sciences, Moscow, 107031, Russia}
-\address[MIT]{Moscow Institute of Physics and Technology,
+\affiliation{\textsuperscript{1}Schmidt Institute of Physics of the Earth of
+  Russian Academy of Sciences, Moscow, 107031, Russia}
+\affiliation{\textsuperscript{2}Moscow Institute of Physics and Technology,
   Dolgoprudny, 141701, Russia}
@@
 
-\begin{keyword}
-  Arrays, multiplication, addition
-\end{keyword}
+\keywords{Arrays, multiplication, addition}
 
@@
   \subfigure[Periodic boundary conditions]{
-    \includegraphics[width=0.45\linewidth]{images/periodic.png}
+    \includegraphics[width=0.4\linewidth]{images/periodic.png}
     \label{fig:s3-periodic}}
@@
   \subfigure[Zero padding]{
-    \includegraphics[width=0.45\linewidth]{images/zeros.png}
+    \includegraphics[width=0.4\linewidth]{images/zeros.png}
     \label{fig:s3-zeros}}
@@
   \subfigure[Realization of overlapping balls]{
-    \includegraphics[width=0.45\linewidth]{images/balls.png}
+    \includegraphics[width=0.4\linewidth]{images/balls.png}
     \label{fig:balls}}
@@
     formula.]{
-    \includegraphics[width=0.45\linewidth]{images/balls-s3.png}
+    \includegraphics[width=0.4\linewidth]{images/balls-s3.png}
     \label{fig:balls-s3-comparison}}
@@
   \subfigure[The dumbbell-like object used in testing of $F_{sss}$ computation]{
-    \includegraphics[width=0.45\linewidth]{images/dumbbell.png}
+    \includegraphics[width=0.4\linewidth]{images/dumbbell.png}
     \label{fig:sss-dumbbell}}
@@
   \subfigure[Relative error of computation]{
-    \includegraphics[width=0.45\linewidth]{images/dumbbell-sss-err.png}
+    \includegraphics[width=0.4\linewidth]{images/dumbbell-sss-err.png}
     \label{fig:sss-dumbbell-error}}
@@
     II discontinuity) at curves A, B and C.]{
-    \includegraphics[width=0.45\linewidth]{images/dumbbell-sss-precise.png}
+    \includegraphics[width=0.4\linewidth]{images/dumbbell-sss-precise.png}
     \label{fig:sss-dumbbell-precise}}
@@
   \subfigure[$F_{sss}$: calculated with our approach]{
-    \includegraphics[width=0.45\linewidth]{images/dumbbell-sss-julia.png}}
+    \includegraphics[width=0.4\linewidth]{images/dumbbell-sss-julia.png}}
   \caption[]{A comparison of $F_{sss}$ function calculated using our approach
@@
   \subfigure[$F_{ssv}$]{
-    \includegraphics[width=0.45\linewidth]{images/ball-ssv.png}
+    \includegraphics[width=0.4\linewidth]{images/ball-ssv.png}
     \label{fig:balls-ssv}}
@@
   \subfigure[$F_{svv}$]{
-    \includegraphics[width=0.45\linewidth]{images/ball-svv.png}
+    \includegraphics[width=0.4\linewidth]{images/ball-svv.png}
     \label{fig:ball-svv}}
@@
 
-\begin{table}[!htp]
+\begin{table*}[!htp]
   \centering
@@
   \label{tab:summary}
-\end{table}
+\end{table*}
 
@@
   \subfigure[Limestone]{
-    \includegraphics[width=0.45\linewidth]{images/carb.png}
+    \includegraphics[width=0.4\linewidth]{images/carb.png}
     \label{fig:sample-limestone}}
@@
   \subfigure[Sandstone (different clusters of void phase are shown in color)]{
-    \includegraphics[width=0.45\linewidth, frame]{images/sandstone1.png}
+    \includegraphics[width=0.4\linewidth, frame]{images/sandstone1.png}
     \label{fig:sample-sandstone}}
@@
   \subfigure[Soil]{
-    \includegraphics[width=0.45\linewidth]{images/soil.png}
+    \includegraphics[width=0.4\linewidth]{images/soil.png}
     \label{fig:sample-soil}}
@@
   \subfigure[Shale]{
-    \includegraphics[width=0.45\linewidth]{images/shale.png}
+    \includegraphics[width=0.4\linewidth]{images/shale.png}
     \label{fig:sample-shale}}
@@
 
-\begin{figure}[tp]
+\begin{figure*}[tp]
   \centering
-  \includegraphics[width=0.45\linewidth]{images/carb.npy-surf3.png}
+  \includegraphics[width=0.4\linewidth]{images/carb.npy-surf3.png}
   \hfill
-  \includegraphics[width=0.45\linewidth]{images/carb.npy-surf2void.png}
+  \includegraphics[width=0.4\linewidth]{images/carb.npy-surf2void.png}
   \vskip\baselineskip
-  \includegraphics[width=0.45\linewidth]{images/carb.npy-surfvoid2.png}
+  \includegraphics[width=0.4\linewidth]{images/carb.npy-surfvoid2.png}
   \hfill
-  \includegraphics[width=0.45\linewidth]{images/carb.npy-s3.png}
+  \includegraphics[width=0.4\linewidth]{images/carb.npy-s3.png}
   \vskip\baselineskip
-  \includegraphics[width=0.45\linewidth]{images/carb.npy-c3.png}
+  \includegraphics[width=0.4\linewidth]{images/carb.npy-c3.png}
   \caption[]{Correlation functions for carbonate sample
@@
   \label{fig:sample-limestone-cf}
-\end{figure}
+\end{figure*}
 
-\begin{figure}[tp]
+\begin{figure*}[tp]
   \centering
-  \includegraphics[width=0.45\linewidth]{images/sandstone1.png-surf2void.png}
+  \includegraphics[width=0.4\linewidth]{images/sandstone1.png-surf2void.png}
   \hfill
-  \includegraphics[width=0.45\linewidth]{images/sandstone1.png-surfvoid2.png}
+  \includegraphics[width=0.4\linewidth]{images/sandstone1.png-surfvoid2.png}
   \vskip\baselineskip
-  \includegraphics[width=0.45\linewidth]{images/sandstone1.png-s3.png}
+  \includegraphics[width=0.4\linewidth]{images/sandstone1.png-s3.png}
   \hfill
-  \includegraphics[width=0.45\linewidth]{images/sandstone1.png-c3.png}
+  \includegraphics[width=0.4\linewidth]{images/sandstone1.png-c3.png}
   \caption[]{Correlation functions for sandstone sample
@@
   \label{fig:sample-sandstone-cf}
-\end{figure}
+\end{figure*}
 
@@
   \subfigure[Shale]{
-    \includegraphics[width=0.45\linewidth]{images/shale-s3.png}
+    \includegraphics[width=0.4\linewidth]{images/shale-s3.png}
     \label{fig:shale-s3}}
@@
   \subfigure[Soil]{
-    \includegraphics[width=0.45\linewidth]{images/soil-s3.png}
+    \includegraphics[width=0.4\linewidth]{images/soil-s3.png}
     \label{fig:soil-s3}}
@@
 made a rest of the algorithm cache-friendly by avoiding random memory access.
-\begin{figure}[tp]
+\begin{figure*}[tp]
   \centering
-
   \subfigure[An original image of an anisotropic pore.]{
-    \includegraphics[width=0.45\linewidth, frame]{images/aniso.png}
+    \includegraphics[width=0.4\linewidth, frame]{images/aniso.png}
     \label{fig:aniso-unrot}}
@@
   \subfigure[A rotated image of pore, so it is elongated along the axis $X$.]{
-    \includegraphics[width=0.45\linewidth, frame]{images/aniso-rot.png}
+    \includegraphics[width=0.4\linewidth, frame]{images/aniso-rot.png}
     \label{fig:aniso-rot}}
@@
   \label{fig:aniso}
-\end{figure}
+\end{figure*}
 

### 2023-12-19 paper.tex
Paper organization

@@
 and GPU architectures -- \code{CorrelationFunctions.jl} \cite{CFsjlpaper}. Here
-we build upon previous results in computations of higher order functions with n
-> 2, most notably by Malmir et al. \cite{malmir2018}, and our aim is to develop
-robust and computationally efficient methods. In addition, we also considered
-the case of anisotropic structures and how to describe them with 3-point
-correlation functions similar to directional 2-point CFs \cite
-{10.1063/1.4867611,EPL1}.
+we build upon previous results in computations of higher order functions with
+$n > 2$, most notably by Malmir et al. \cite{malmir2018}, and our aim is to
+develop robust and computationally efficient methods. In addition, we also
+considered the case of anisotropic structures and how to describe them with
+3-point correlation functions similar to directional 2-point CFs
+\cite{10.1063/1.4867611,EPL1}.
 
-\highlight{The paper is organized as follows:}
+The paper is organized as follows: in \cref{sec:methods} we provide
+mathematical background and describe methods for computation of 3-point
+correlation functions. Verification of these methods along with some results for
+real-world samples (limestone, soil etc.) is described in
+\cref{sec:results}. Section \ref{sec:discussion} provides the discussion, a
+comparison with other existing methods and summarizes possible directions for
+improvement.
 
 \section{Methods}
+\label{sec:methods}
 \subsection{3-point correlation functions}
@@
 \section{Results}
+\label{sec:results}
 \subsection{Verification}
@@
 \section{Discussion}
+\label{sec:discussion}
 In this paper we have provided two approaches to compute three-point correlation

### 2023-12-19 paper.tex
Replace 'width 7' with 'width 7 pixels'

@@
 \label{sec:filter}
-For edge detection we use a kernel with the width 7 with coefficients inversely
-proportional to distance to kernel's central element. The central element has
-such value, so all elements of the kernel sum to zero:
+For edge detection we use a kernel with the width 7 pixels with coefficients
+inversely proportional to distance to acentral element of the kernel. The
+central element is determined by a property that all elements of the kernel sum
+to zero:
 \begin{equation}

### 2023-12-19 paper.tex
Fix a very long formula

@@
 \begin{equation}
-  C_{ij} = \sum_{x \in \left\{ \text{Coordinates of points in the
-      phase of interest} \right\}} (x_i - \overline{x_i})(x_j - \overline{x_j})
+  C_{ij} = \sum_{x \in \left\{
+    \begin{array}{l}
+      \text{Coordinates of points} \\
+      \text{in the phase of interset}
+    \end{array}
+    \right\}} (x_i - \overline{x_i})(x_j - \overline{x_j})
 \end{equation}
@@
   \hfill
-  \subfigure[A rotated image of pore, so it is elongated along the axis $X$.]{
+  \subfigure[A rotated image of the pore, so it is elongated along the axis
+    $X$.]{
     \includegraphics[width=0.4\linewidth, frame]{images/aniso-rot.png}

### 2023-12-21 paper.tex
More about anisotropic samples

@@
 
+\subsection{Analysis of anisotropic media}
+When an analized sample is anisotropic, i.e. it is stretched or oriented along
+some specific direction, it may be desired to align one of the catheti of the
+scanning pattern \cref{fig:pattern} with that direction. In this case the
+anisotropicity present in the sample will be featured in a produced correlation
+function \textcolor{red}{most well. voobshe eto po-angliyski?}
+
+To detect the direction of anisotropy we use an $N \times N$ (where $N$ is
+dimensionality of the sample) covariance matrix for coordinates of points in the
+phase of interest:
+\begin{equation}
+  C_{ij} = \sum_{x \in \left\{
+    \begin{array}{l}
+      \text{Coordinates of points} \\
+      \text{in the phase of interset}
+    \end{array}
+    \right\}} (x_i - \overline{x_i})(x_j - \overline{x_j})
+\end{equation}
+and decompose $C$ as $T \Lambda T^{-1}$ where $T$ is a unitary matrix and
+$\Lambda$ is diagonal. $T$ can always be made so that it defines a rotation (by
+multiplication of one of the columns by $-1$ if needed, so that
+$\det T = 1$. Application of this rotation to the sample makes the direction of
+anisotropicity parallel to one of the axes, so anisotropicity can be better
+featured in the correlation function \cref{fig:aniso}.
+\begin{figure*}[tp]
+  \centering
+  \subfigure[An original image of an anisotropic pore.]{
+    \includegraphics[width=0.4\linewidth, frame]{images/aniso.png}
+    \label{fig:aniso-unrot}}
+  \hfill
+  \subfigure[A rotated image of the pore, so it is elongated along the axis
+    $X$.]{
+    \includegraphics[width=0.4\linewidth, frame]{images/aniso-rot.png}
+    \label{fig:aniso-rot}}
+  \vskip\baselineskip
+  \subfigure[$S_3$ function for the original image]{
+    \includegraphics[width=0.3\linewidth]{images/aniso-s3.png}}
+  \hfill
+  \subfigure[$S_3$ function for the rotated image. A vector $(0.92, -0.4)$ is a
+    direction of elongation of the pore.]{
+  \includegraphics[width=0.3\linewidth]{images/aniso-rot-s3.png}}
+  \hfill
+  \subfigure[$S_3$ function averaged across 100 random rotations.]{
+    \includegraphics[width=0.3\linewidth]{images/aniso-avg-s3.png}
+    \label{fig:aniso-avg}}
+  \caption[]{Behaviour of our algorithm for calculation of the $S_3$ function
+    when dealing with highly anisotropic media. The pattern \cref{fig:pattern}
+    which we use in our algorithm is most sensitive to anisotropy which is
+    directed along one of the axes. A result on \cref{fig:aniso-avg} averaged
+    across rotations is similar to the algorithm proposed by Malmir~et~al.}
+  \label{fig:aniso}
+\end{figure*}
+The above said holds for every algorithm introduced in the paper.
+
+When a sample is known to be isotropic, the correlation function may be
+calculated multiple times, each time applying a random rotation of the sample,
+and then averaged across rotations to gather more statistics. This process is
+illustrated on \cref{fig:workflow}.
+\begin{figure*}[tp]
+  \centering
+  \includegraphics[width=0.6\linewidth]{images/workflow.png}
+  \caption[]{A possible workflow for computation of correlation functions
+    (clockwise from top left to bottom right ): 1.~rotating a sample in random
+    directions (which is equivalent to rotating the sampling pattern),
+    2.~calculating the correlation function for each direction, 3.~avegaring
+    results across rotations, 4.~representing the result as a family of 2D
+    plots.}
+  \label{fig:workflow}
+\end{figure*}
+
 \section{Results}
@@
 made a rest of the algorithm cache-friendly by avoiding random memory access.
-\begin{figure*}[tp]
-  \centering
-  \subfigure[An original image of an anisotropic pore.]{
-    \includegraphics[width=0.4\linewidth, frame]{images/aniso.png}
-    \label{fig:aniso-unrot}}
-  \hfill
-  \subfigure[A rotated image of the pore, so it is elongated along the axis
-    $X$.]{
-    \includegraphics[width=0.4\linewidth, frame]{images/aniso-rot.png}
-    \label{fig:aniso-rot}}
-  \vskip\baselineskip
-  \subfigure[$S_3$ function for the original image]{
-    \includegraphics[width=0.3\linewidth]{images/aniso-s3.png}}
-  \hfill
-  \subfigure[$S_3$ function for the rotated image. A vector $(0.92, -0.4)$ is a
-    direction of elongation of the pore.]{
-  \includegraphics[width=0.3\linewidth]{images/aniso-rot-s3.png}}
-  \hfill
-  \subfigure[$S_3$ function averaged across 100 random rotations.]{
-    \includegraphics[width=0.3\linewidth]{images/aniso-avg-s3.png}
-    \label{fig:aniso-avg}}
-  \caption[]{Behaviour of our algorithm for calculation of the $S_3$ function
-    when dealing with highly anisotropic media. The pattern \cref{fig:pattern}
-    which we use in our algorithm is most sensitive to anisotropy which is
-    directed along one of the axes. A result on \cref{fig:aniso-avg} is similar
-    to the algorithm proposed by Malmir~et~al.}
-  \label{fig:aniso}
-\end{figure*}
 

### 2023-12-25 paper.tex
I'm tired

@@
 correlation functions. Verification of these methods along with some results for
-real-world samples (limestone, soil etc.) is described in
+real-world samples (sandstone, soil etc.) is described in
 \cref{sec:results}. Section \ref{sec:discussion} provides the discussion, a
@@
 scanning pattern \cref{fig:pattern} with that direction. In this case the
-anisotropicity present in the sample will be featured in a produced correlation
+anisotropy present in the sample will be featured in a produced correlation
 function \textcolor{red}{most well. voobshe eto po-angliyski?}
@@
 $\det T = 1$. Application of this rotation to the sample makes the direction of
-anisotropicity parallel to one of the axes, so anisotropicity can be better
-featured in the correlation function \cref{fig:aniso}.
+anisotropy parallel to one of the axes, so anisotropy can be better featured in
+the correlation function \cref{fig:aniso}.
 \begin{figure*}[tp]
@@
     direction of elongation of the pore.]{
-  \includegraphics[width=0.3\linewidth]{images/aniso-rot-s3.png}}
+    \includegraphics[width=0.3\linewidth]{images/aniso-rot-s3.png}
+    \label{fig:aniso-rot-s3}}
   \hfill
@@
 \subsection{Applications to material images}
-In this section we compute correlation functions along the plane $XY$ for 2- and
-3-dimensional real samples. Table \ref{tab:summary} contains information about
-these samples. Note that we compute surface correlation functions only for those
-samples for which the criterion $C_{0.5} > 0.97$ holds (the sandstone and the
-limestone). Images of the samples are on \cref{fig:samples}. On plots of
-correlation functions we provide a family of curves with the first argument of
-the correlation function being fixed. For two highly anisotropic samples (the
-soil and the shale) we provide heatmaps of $S_3$ correlation function where
-anisotropy can be easily observed. These two samples were preliminary rotated by
-$\frac{\pi}{4}$ around the axis $Z$ before calculation of correlation functions.
+In this section we compute correlation functions for 2- and 3-dimensional real
+samples. Table \ref{tab:summary} contains information about these samples. Note
+that we compute surface correlation functions only for those samples for which
+the criterion $C_{0.5} > 0.97$ holds (the two sandstones and the \textcolor{red}{shale}). Images
+of the samples are on \cref{fig:samples}. On plots of correlation functions for
+isotropic samples we provide a family of curves with the first argument of the
+correlation function being fixed. For anisotropic samples we provide heatmaps of
+correlation functions where anisotropy can be easily observed.
 
-Correlation functions for the XCT sample of the limestone are on
-\cref{fig:sample-limestone-cf}. The plot of $S_3$ function allows us to estimate
-porosity of the sample to be $\sim 0.04$ (note, that the curve with $r_1 = 0$ is
-actually $S_2$ function). The two-point correlation function reaches plateau at
-$r_2 \approx 200\div 225\ \mu m$ which means that two events of finding two
-points in the void phase are independent if the points are farther than
-$225\ \mu m$ from each other. We see that the sample is slightly anisotropic
-($S_3(0, 225) \approx S_3(150, 0)$). From analysis of $C_3$ function it can be
-stated that the sample has clusters of void phase which are $\sim 200\ \mu m$ in
-diameter.
+Correlation functions for the XCT sample of a sandstone are on
+\cref{fig:sample-sandstone-xct-cf}. The plot of $S_3$ function allows us to
+estimate porosity of the sample to be $\sim 0.19$ (note that the curve with
+$r_1 = 0$ is actually $S_2$ function). The two-point correlation function
+reaches plateau at $r_2 \approx 60 \mu m$ which means that two events
+of finding two points in the void phase are independent if the points are
+farther than $60 \mu m$ from each other. We see that the sample is isotropic
+($S_3(0, 56.25) \approx S_3(56.25, 0)$). From similarity of the $C_3$ and $S_3$
+functions it can be stated that the pore phase in this sample forms one big
+interconnected pore system.
 
@@
 \cref{fig:sample-sandstone-cf}. Porosity of the sample is $\sim 0.3$ as follows
-from the plot of $S_3$ function at $r_1 = 0$. The funcion $S_3(0, r_2)$ reaches
+from the plot of $S_3$ function at $r_1 = 0$. The function $S_3(0, r_2)$ reaches
 plateau at $r_2 \approx 20\ \mu m$. The sample is highly anisotropic (elongated
@@
     \hline
-    Limestone & XCT &  $600 \times 600 \times 600$ & 3.02 & 0.9712 \\
+    Sandstone & XCT &  $500 \times 500 \times 500$ & 2.25 & 0.9703 \\
     Soil & XCT & $160 \times 160 \times 160$ & 2.25 & 0.9210 \\
@@
   \centering
-  \subfigure[Limestone]{
-    \includegraphics[width=0.4\linewidth]{images/carb.png}
-    \label{fig:sample-limestone}}
+  \subfigure[Sanstone XCT]{
+    \includegraphics[width=0.4\linewidth]{images/15581.png}
+    \label{fig:sample-sandstone-xct}}
   \hfill
-  \subfigure[Sandstone (different clusters of void phase are shown in color)]{
+  \subfigure[Sandstone SEM (different clusters of void phase are shown in color)]{
     \includegraphics[width=0.4\linewidth, frame]{images/sandstone1.png}
@@
   \centering
-  \includegraphics[width=0.4\linewidth]{images/carb.npy-surf3.png}
+  \includegraphics[width=0.4\linewidth]{images/15581-surf3.png}
   \hfill
-  \includegraphics[width=0.4\linewidth]{images/carb.npy-surf2void.png}
+  \includegraphics[width=0.4\linewidth]{images/15581-surf2void.png}
   \vskip\baselineskip
-  \includegraphics[width=0.4\linewidth]{images/carb.npy-surfvoid2.png}
+  \includegraphics[width=0.4\linewidth]{images/15581-surfvoid2.png}
   \hfill
-  \includegraphics[width=0.4\linewidth]{images/carb.npy-s3.png}
+  \includegraphics[width=0.4\linewidth]{images/15581-s3.png}
   \vskip\baselineskip
-  \includegraphics[width=0.4\linewidth]{images/carb.npy-c3.png}
-  \caption[]{Correlation functions for carbonate sample
-    (\cref{fig:sample-limestone}).}
-  \label{fig:sample-limestone-cf}
+  \includegraphics[width=0.4\linewidth]{images/15581-c3.png}
+  \caption[]{Correlation functions for the sandstone XCT sample
+    (\cref{fig:sample-sandstone-xct}).}
+  \label{fig:sample-sandstone-xct-cf}
 \end{figure*}
@@
   \includegraphics[width=0.4\linewidth]{images/sandstone1.png-c3.png}
-  \caption[]{Correlation functions for sandstone sample
+  \caption[]{Correlation functions for the sandstone SEM sample
     (\cref{fig:sample-sandstone}).}
@@
 Torquato \cite{SMITH1988176}. The first algorithms generates a triangle with
-fixed sides $r_1$ and $r_2$ and an angle $\theta$ between them and places it in
-the medium firstly making a random translation and a rotation around a random
-vector by a random angle. By making a large number of trials the algorithm gets
-a value of a three-point correlation function at the point
+fixed sides $r_1$ and $r_2$ and an arbitrary angle $\theta$ between them and
+places it in the medium firstly making a random translation and a rotation
+around a random vector by a random angle. By making a large number of trials the
+algorithm gets a value of a three-point correlation function at the point
 $(r_1, r_2, \theta)$. The second algorithm takes a precalculated triangle
@@
 rotation, only applying a random translation. This way the algorithm preserves
-orientation of triangles stored in the pattern.
+orientation of triangles stored in the pattern. The main advantage of our
+algorithm is its parallelizability and ease of implementation. A drawback is
+that an angle between catheti of the sampling pattern is fixed to be
+$\theta = \frac{\pi}{2}$ but the pattern can be rotated as a whole by an
+equivalent operation of rotation of a sample. These rotations can be random as
+in the Malmir's algorithm (\cref{fig:aniso-avg}), or it can be a single rotation
+to align catheti of the sampling triangle with the direction of anisotropy
+(\cref{fig:aniso-rot-s3}).
 
@@
 against classical and other metrics.
-
-Our algorithm fixes $\theta = \frac{pi}{2}$ and does not perform random
-rotations or trial triangles. It is sensitive to anisotropy of the medium
-when it is stretched along one of the axes as shown in \cref{fig:aniso}. A
-direction of elongation for a $N$-dimensional image can be easily detected by
-firstly evaluating a $N \times N$ covariance matrix for points belonging to the
-phase of interest:
-\begin{equation}
-  C_{ij} = \sum_{x \in \left\{
-    \begin{array}{l}
-      \text{Coordinates of points} \\
-      \text{in the phase of interset}
-    \end{array}
-    \right\}} (x_i - \overline{x_i})(x_j - \overline{x_j})
-\end{equation}
-and then decomposing $C$ as $T \Lambda T^{-1}$ where $T$ is a unitary matrix and
-$\Lambda$ is diagonal. $T$ can always be made so that it defines a rotation and
-can be used to align the elongation with the axes (compare \cref{fig:aniso-unrot}
-and \cref{fig:aniso-rot}).
-
-The main advantage of our algorithm is its parallelizability and ease of
-implementation. An equivalent operation for rotation of test triangles is a
-rotation of the whole input image which we have implemented in our
-CorrelationFunctions.jl package. By applying a rotation to the input first we
-made a rest of the algorithm cache-friendly by avoiding random memory access.
 

### 2023-12-25 paper.tex
More images

@@
 \subsection{Applications to material images}
-In this section we compute correlation functions for 2- and 3-dimensional real
-samples. Table \ref{tab:summary} contains information about these samples. Note
-that we compute surface correlation functions only for those samples for which
-the criterion $C_{0.5} > 0.97$ holds (the two sandstones and the \textcolor{red}{shale}). Images
-of the samples are on \cref{fig:samples}. On plots of correlation functions for
-isotropic samples we provide a family of curves with the first argument of the
-correlation function being fixed. For anisotropic samples we provide heatmaps of
-correlation functions where anisotropy can be easily observed.
-
-Correlation functions for the XCT sample of a sandstone are on
-\cref{fig:sample-sandstone-xct-cf}. The plot of $S_3$ function allows us to
-estimate porosity of the sample to be $\sim 0.19$ (note that the curve with
-$r_1 = 0$ is actually $S_2$ function). The two-point correlation function
-reaches plateau at $r_2 \approx 60 \mu m$ which means that two events
-of finding two points in the void phase are independent if the points are
-farther than $60 \mu m$ from each other. We see that the sample is isotropic
-($S_3(0, 56.25) \approx S_3(56.25, 0)$). From similarity of the $C_3$ and $S_3$
-functions it can be stated that the pore phase in this sample forms one big
-interconnected pore system.
-
-Correlation functions for the SEM sample (the sandstone) are on
-\cref{fig:sample-sandstone-cf}. Porosity of the sample is $\sim 0.3$ as follows
-from the plot of $S_3$ function at $r_1 = 0$. The function $S_3(0, r_2)$ reaches
-plateau at $r_2 \approx 20\ \mu m$. The sample is highly anisotropic (elongated
-along the ordinate). The samples has clusters which are $\sim 45\ \mu m$ in
-diameter.
-
-Heatmaps of $S_3$ for the two highly anisotropic samples can be seen on
-\cref{fig:heatmaps}. Anisotropy of the both samples can be seen as a slower
-decay of $S_3$ in one of the directions. Additionally, it can be observed that
-elongated clusters of the void phase in the sample of soil are parallel to each
-other and have a regular spacing of about $50 \mu m$.
-
 \begin{table*}[!htp]
@@
 \end{table*}
-
+In this section we compute correlation functions for 2- and 3-dimensional real
+samples. Table \ref{tab:summary} contains information about these samples. Note
+that we compute surface correlation functions only for those samples for which
+the criterion $C_{0.5} > 0.97$ holds (the two sandstones and the \textcolor{red}{shale}). Images
+of the samples are on \cref{fig:samples}. On plots of correlation functions for
+isotropic samples we provide a family of curves with the first argument of the
+correlation function being fixed. For anisotropic samples we provide heatmaps of
+correlation functions where anisotropy can be easily observed.
 \begin{figure*}[tp]
@@
 \end{figure*}
+
+Correlation functions for the XCT sample of a sandstone are on
+\cref{fig:sample-sandstone-xct-cf}. The plot of $S_3$ function allows us to
+estimate porosity of the sample to be $\sim 0.19$ (note that the curve with
+$r_1 = 0$ is actually $S_2$ function). The two-point correlation function
+reaches plateau at $r_2 \approx 60 \mu m$ which means that two events
+of finding two points in the void phase are independent if the points are
+farther than $60 \mu m$ from each other. We see that the sample is isotropic
+($S_3(0, 56.25) \approx S_3(56.25, 0)$). From similarity of the $C_3$ and $S_3$
+functions it can be stated that the pore phase in this sample forms one big
+interconnected pore system.
+
+Correlation functions for the SEM sample (the sandstone) are on
+\cref{fig:sample-sandstone-cf}. Porosity of the sample is $\sim 0.3$ as follows
+from the plot of $S_3$ function at $r_1 = 0$. The function $S_3(0, r_2)$ reaches
+plateau at $r_2 \approx 20\ \mu m$. The sample is highly anisotropic (elongated
+along the ordinate). The samples has clusters which are $\sim 45\ \mu m$ in
+diameter.
+
+The anisotropic samples (the soil and the shale) were preliminarily rotated with
+periodic boundary conditions to align elongated pores with coordinate axes. The
+result of rotation can be seen on \cref{fig:samples-rot}. Heatmaps of $S_3$
+function for these samples can be seen on \cref{fig:heatmaps}. It can be
+observed that elongated clusters of the void phase in the sample of soil form a
+structure which resembles a regular grid with spacing of about $60 \mu m$. The
+sample of shale shows less regular yet still anisotropic structure.
 
@@
   \centering
+  \subfigure[Soil]{
+    \includegraphics[width=0.4\linewidth]{images/soil-rot.png}}
+  \hfill
   \subfigure[Shale]{
-    \includegraphics[width=0.4\linewidth]{images/shale-s3.png}
-    \label{fig:shale-s3}}
-  \hfill
+    \includegraphics[width=0.4\linewidth]{images/shale-rot.png}}
+  \caption[]{Rotations of anisotropic samples with pores aligned with the
+    coordinate axes.}
+  \label{fig:samples-rot}
+\end{figure*}
+
+\begin{figure*}[tp]
+  \centering
   \subfigure[Soil]{
@@
   \hfill
+  \subfigure[Shale]{
+    \includegraphics[width=0.4\linewidth]{images/shale-s3.png}
+    \label{fig:shale-s3}}
   \caption[]{Heatmaps of $S_3$ function for highly anisotropic samples of shale
-    and soil. $S_3$ function was clamped to the range $[0, 0.1]$ to make
-    anisotropy more visible. It can be observed that the samples have
-    cavities elongated along the vector $(1, 1, 0)$.}
+    and soil.}
   \label{fig:heatmaps}

### 2023-12-26 paper.tex
Even more images
Change figure caption

@@
   \centering
-  \subfigure[Soil]{
   \includegraphics[width=0.4\linewidth]{images/soil-s3.png}
-    \label{fig:soil-s3}}
   \hfill
-  \subfigure[Shale]{
   \includegraphics[width=0.4\linewidth]{images/shale-s3.png}
-    \label{fig:shale-s3}}
-  \caption[]{Heatmaps of $S_3$ function for highly anisotropic samples of shale
-    and soil.}
+  \vskip\baselineskip
+  \includegraphics[width=0.4\linewidth]{images/soil-avg.png}
+  \hfill
+  \includegraphics[width=0.4\linewidth]{images/shale-avg.png}
+  \caption[]{Heatmaps of $S_3$ function for highly anisotropic samples. On the
+    left: soil, on the right: shale. On the top: the function calculated for a
+    rotation of the sample which aligns the direction of anisotropy with the
+    axes, on the bottom: the function averaged across 100 random rotations.}
   \label{fig:heatmaps}

### 2023-12-28 timings/timings.jl
Add timings information

@@ -1,0 +1,32 @@
+module Shit
+import CorrelationFunctions.Directional as D
+using NPZ
+
+const functions = [
+    :s3, :c3, :surf3, :surf2void, :surfvoid2
+]
+
+function counttime(thunk)
+    t = time()
+    thunk()
+    return time() - t
+end
+
+function do_it()
+    x = 125000:2500000:27000000
+    sides = round.(Int, cbrt.(x))
+    for sym in functions
+        println(sym)
+        fn = D.eval(sym)
+        times = map(sides) do side
+            println(side)
+            GC.gc()
+            data = rand(Bool, (side, side, side))
+            counttime(() -> fn(data, true; periodic = true))
+        end
+        npzwrite("$(sym).npy", hcat(sides, times))
+    end
+    return nothing
+end
+
+end

### 2023-12-28 timings/timings.py

@@ -1,0 +1,22 @@
+#!/usr/bin/env python
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+legend = ['$S_3$', '$C_3$', '$F_{sss}$', '$F_{ssv}$', '$F_{svv}$']
+names = map(lambda name: name + '.npy', ['s3', 'c3', 'surf3', 'surf2void', 'surfvoid2'])
+colors = ['b', 'r', 'g', 'k', 'm']
+
+plt.figure(figsize = (10, 8), dpi = 300)
+plt.rc('font', size = 25)
+
+for (name, color) in zip(names, colors):
+    data = np.load('gpu/' + name)
+    plt.plot(data[:,0]**3, data[:,1], color + '.-')
+
+plt.legend(legend)
+plt.yscale('log')
+plt.xscale('log')
+plt.xlabel('Number of voxels')
+plt.ylabel('Time of execution, s')
+plt.savefig('timings-gpu.png')

### 2023-12-28 paper.tex
Forgot a closing parenthesis
Add a subsection about timings

@@
 multiplication of one of the columns by $-1$ if needed, so that
-$\det T = 1$. Application of this rotation to the sample makes the direction of
+$\det T = 1$). Application of this rotation to the sample makes the direction of
 anisotropy parallel to one of the axes, so anisotropy can be better featured in
@@
 
+\subsection{Execution times for our algorithms}
+In this section we measure execution times of our algorithms for random
+3-dimensional arrays of bits (i.e. each element can be either 0 or 1). The
+arrays have equal number of elements along each direction therefore
+representing cubes of 2-phase porous media. The number of voxels in each cube
+increases from $1.25 \cdot 10^5$ to $2.7 \cdot 10^7$ linearly. The time of execution
+is measured for each function executed on a CPU and a GPU. Hardware and software
+components used for testing are listed in \cref{tab:machine}.
+\begin{table*}[!htp]
+  \centering
+  \begin{tabular}{|c|c|}
+    CPU & Intel Celeron 333 MHz \\
+    RAM & 100500 GB DDR4 PC-XXXX \\
+    GPU & AMD Navi 21 \\
+    Julia & 1.10.0 \\
+    CUDA.jl & 4.0
+  \end{tabular}
+  \caption{Parameters of the machine used to measure execution times of the
+    algorithms described in this paper.}
+  \label{tab:machine}
+\end{table*}
+\begin{figure*}[tp]
+  \centering
+  \subfigure[CPU]{
+    \includegraphics[width=0.4\linewidth]{images/timings-cpu.png}}
+  \hfill
+  \subfigure[GPU]{
+    \includegraphics[width=0.4\linewidth]{images/timings-gpu.png}}
+  \caption[]{Execution times of the algorithms proposed in this paper.}
+  \label{fig:timings}
+\end{figure*}
+The results are on \cref{fig:timings}. It can be observed that the time of
+execution is a power function of number of voxels. GPU gives a
+10x-100x performance boost depending on the correlation function.
+
 \section{Discussion}

### 2024-01-09 paper.tex
Number of triangles

@@
 arrays have equal number of elements along each direction therefore
-representing cubes of 2-phase porous media. The number of voxels in each cube
-increases from $1.25 \cdot 10^5$ to $2.7 \cdot 10^7$ linearly. The time of execution
-is measured for each function executed on a CPU and a GPU. Hardware and software
-components used for testing are listed in \cref{tab:machine}.
+representing cubes of 2-phase porous media. The number of voxels $N$ in each
+cube increases from $1.25 \cdot 10^5$ to $2.7 \cdot 10^7$ linearly. Times of
+execution are measured for each function executed on a CPU and a GPU. Hardware
+and software components used for testing are listed in \cref{tab:machine}. Each
+computation of a correlation function is equivalent to testing $N^{5/3}$ pattern
+triangles thrown into the sample.
 \begin{table*}[!htp]

### 2024-01-09 paper.tex
Mehr sinnlose Bilder

@@
   \centering
-  \begin{tabular}{|c|c|c|c|c|}
+  \begin{tabular}{|c|c|c|c|c|c|}
     \hline
-    Sample name & Image type & Dimensions (pixels) & Image resolution ($\mu m$) & $C_{0.5}$\\
+    Sample name & Image type & Dimensions (pixels) & Image resolution ($\mu m / px$)
+    & $C_{0.5}$ & Comment \\
     \hline
-    Sandstone & XCT &  $500 \times 500 \times 500$ & 2.25 & 0.9703 \\
-    Soil & XCT & $160 \times 160 \times 160$ & 2.25 & 0.9210 \\
-    Shale & XCT & $160 \times 160 \times 160$ & 2.25 & 0.8912 \\
-    Sandstone & SEM &  $1280 \times 869$ & 0.10 & 0.9703 \\
+    Sandstone & XCT &  $500 \times 500 \times 500$ & 2.25 & 0.9703 & \\
+    Soil & XCT & $500 \times 500 \times 500$ & 0.72 & 0.9431 & Digitally
+    magnified \\
+    Shale & XCT & $160 \times 160 \times 160$ & 2.25 & 0.8912 & \\
+    Sandstone & SEM &  $1280 \times 869$ & 0.10 & 0.9613 & \\
     \hline
@@
 that we compute surface correlation functions only for those samples for which
-the criterion $C_{0.5} > 0.97$ holds (the two sandstones and the \textcolor{red}{shale}). Images
+the criterion $C_{0.5} > 0.97$ holds (the two sandstones and the soil). Images
 of the samples are on \cref{fig:samples}. On plots of correlation functions for
@@
 structure which resembles a regular grid with spacing of about $60 \mu m$. The
-sample of shale shows less regular yet still anisotropic structure.
+sample of shale shows less regular yet still anisotropic structure. We provide
+the rest of correlation functions for the sample of soil on
+\cref{fig:soil-maps}.
 
@@
   \label{fig:heatmaps}
+\end{figure*}
+
+\begin{figure*}[tp]
+  \centering
+  \subfigure[$C_3$]{
+    \includegraphics[width=0.4\linewidth]{images/c3-map.png}}
+  \hfill
+  \subfigure[$F_{sss}$]{
+    \includegraphics[width=0.4\linewidth]{images/surf3-map.png}}
+  \vskip\baselineskip
+  \subfigure[$F_{ssv}$]{
+    \includegraphics[width=0.4\linewidth]{images/surf2void-map.png}}
+  \hfill
+  \subfigure[$F_{svv}$]{
+    \includegraphics[width=0.4\linewidth]{images/surfvoid2-map.png}}
+  \caption[]{Correlation maps for the sample of soil.}
+  \label{fig:soil-maps}
 \end{figure*}

### 2024-02-11 paper.tex
filized methods discussion and other parts

@@
 \begin{abstract}
-  Wow, we can multiply arrays and tell you how cool it is.
+Structures, or spatial arrangements of matter and energy, including some fields
+(e.g., velocity or pressure) are ubiquitous in research applications and
+frequently require description for subsequent analysis, or stochastic reconstruction from limited data.
+The classical descriptors are 2-point correlation functions (CFs), but the computation of 3-point statistics is known to be
+advantageous in some cases as they can probe non-Gaussian signatures, not captured by their 2-point counterparts.
+Moreover, 3-point and CFs with $n>3$ are believed to possess larger information content and provide 
+more information about studies structures. In this paper, we have developed algorithms and code to compute 
+$S_3, C_3, F_{sss}, F_{ssv}$ and $F_{svv}$ with a right-angle triangle pattern. This pattern is much
+easier to vectorize and parallelize compared to previously used random triangle or spider-web sampling patterns. Moreover,
+it allows to easily implement computations of directional 3-point CFs. The execution times
+for the same number of sample are orders of magnitude lower than existing published counterparts. We showed that the volume of
+data produced get unwieldy very easily, especially if computations are performed in frequency domain. For these reasons until
+information content of different sets of correlation functions with different "n-pointness" is not known, 
+advantages of CFs with $n>3$ are not clear. Nonetheless, developed algorithms and code are universal enough to be
+easily extendable to any $n$ (with increasing computational and RAM burden). All results are available as part of open source
+package \code{CorrelationFunctions.jl} [Postnicov et al., 2024, Comp.Phys.Commun(accepted)]. As described in this paper, 
+3-point CFs computations can be immediately applied in a great number of
+research applications, for example: 1) flow and transport velocity fields analysis or any data with non-Gaussian signatures,
+2) deep learning for structural and physical properties, 3) structure taxonomy and categorization. 
+In all these and numerous other potential cases the ability
+to compute directional 3-point functions may be crucial. Notably, the organization of the code functions allows computation
+of cross-correlation, i.e., one can compute 3-point CFs for multiphase images (while binary structures were used in this paper
+for simplicity of explanations).
 \end{abstract}
 
-\keywords{Arrays, multiplication, addition}
+%\keywords{Arrays, multiplication, addition}
 
@@
 \section{Introduction}
+\label{sec:intro}
 Structures, or spatial arrangements of matter and energy, including some fields
@@
 evolution of such metrics was mainly induced by the ease of measurement and
-interpretation -- this is startling to observe holy wars on the question which
-metric is superior to flare up occasionally,
-e.g.,\cite{vogel2022holistic,yudina2023dual}. In fact, we need a single
-universal descriptor defined by only one characteristic -- information
+interpretation. In fact, we need a single universal descriptor defined by only one characteristic -- information
 content. The latter is an ability of the metric to describe the structure at
@@
 this metric. Thus, universal descriptor has to possess following key properties:
-(1) high information content, (2) easy to assess, (3) high compression (i.e.,
+(1) high information content, (2) ease of assess, (3) high compression ratio (i.e.,
 descriptor is much "smaller" than the structure itself).
@@
     functions except for surface ones), surface area is represented by in the
-    derivative at $S_2(0)$ \cite{debye1957scattering} or the value of
-    $F_{ss}(0)$ (or $F_{sss}(0)$). Connectivity is described by cluster
+    derivative at $S_2(0)$ \cite{debye1957scattering}. Connectivity is described by cluster
     functions $C_2$ or $C_3$. Pore-size distribution is related to pore-size
@@
     interconnected with mean curvature and Euler characteristic
-    \cite{ma2020generation}. All together, the classic set of correlation
+    \cite{ma2020generation}. Altogether, the classic set of correlation
     functions describes both the geometry and topology of the structure at hand;
@@
 astrophysics and turbulence patterns analysis as they can probe non-Gaussian
-signatures in the distribution of matter and energy, which are not captured in
+signatures in the distribution of matter and energy, which are not captured by their
 2-point counterparts
@@
 correlation functions. Verification of these methods along with some results for
-real-world samples (sandstone, soil etc.) is described in
+real-world samples (sandstone, soil, etc.) is described in
 \cref{sec:results}. Section \ref{sec:discussion} provides the discussion, a
 comparison with other existing methods and summarizes possible directions for
-improvement.
+future research.
 
@@
 
-Introduce a function $M_n(x) = |\nabla I_n(x)|$ which is a so-called interface
-indicator function. With this function we can define three additional
-correlation functions, which are the surface-surface-surface function
+By introducing a function $M_n(x) = |\nabla I_n(x)|$ which is a so-called interface
+indicator function, we can define three additional
+correlation functions -- these are the surface-surface-surface function
 ($F_{sss}$), surface-surface-void function ($F_{ssv}$) and surface-void-void
@@
 of probability and have the units of measurement inversely proportional to
-volume, surface and length, respectively (e.g. $\mu m^{-3}$, $\mu m^{-2}$ and
-$\mu m^{-1}$). These functions describe the interface of the subset $A_n$ and
+volume, surface and length, respectively (e.g., can be measured in $\mu m^{-3}$, $\mu m^{-2}$ and
+$\mu m^{-1}$ or other convenient dimensionless units depending on the problem to be solved). 
+These functions describe the interface of the subset $A_n$ and
 its spatial configuration with respect to $A_v$.
@@
 a subset $A_n$ if and only if $A[x] = n$. The simplest algorithm below
-calculates $S_3$ pointwise in spatial domain:
+calculates $S_3$ pointwise in the spatial domain:
 \begin{algorithmic}[1]
@@
 replace out-of-bound elements with zeros (so-called zero padding)
-(\cref{fig:s3-zeros}). A formula for $Norm(A, x_1, x_2)$ in this case is in
+(\cref{fig:s3-zeros}). A formula for $Norm(A, x_1, x_2)$ in this case is in Appendix
 \ref{sec:number-of-trials} and $\mathfrak{S}_z$ is defined as follows:
@@
 
-The second approach is to compute the whole correlation map in Fourier
+The second approach is to compute the whole correlation map in the Fourier
 domain. Suppose we have a function
@@
 $4 \cdot 2 \cdot 500^4 / 1000^3 = 500$ GB are needed to store Fourier image of
-the map. Moreover, Fourier image of the whole map is needed even if only one
+the map. Moreover, Fourier image of the whole map has to be computed even if only one
 element of the map in spatial domain is required. The aforementioned limitations
@@
 Our implementation fixes $x_1$ and $x_2$ to be parallel to one of the axes $X$,
-$Y$ or $Z$ with restriction $x_1 \perp x_2$ (\cref{fig:pattern}). Thus, the
+$Y$ or $Z$ with restriction $x_1 \perp x_2$ (\cref{fig:pattern}) \cite{dimitrakopoulos2010high}. Thus, the
 output has dimensions $D_1 \times D_2$ where $D_1$ and $D_2$ are dimensions of
-the input array along selected axes.
+the input array along selected axes. Note that shift operators with such $x_1$ and $x_2$
+represent a 3-point function computed within a 3D domain, but along a predefined direction (see below).
 \begin{figure}[ht]
@@
 replace an indicator function $I_n$ with an edge detection operator $E_n$
-(see \ref{sec:filter}). Then the algorithms are straightforward:
+(see Appendix \ref{sec:filter}). Then the algorithms are straightforward:
 \begin{algorithmic}[1]
@@
 \subsection{Analysis of anisotropic media}
-When an analized sample is anisotropic, i.e. it is stretched or oriented along
-some specific direction, it may be desired to align one of the catheti of the
-scanning pattern \cref{fig:pattern} with that direction. In this case the
-anisotropy present in the sample will be featured in a produced correlation
-function \textcolor{red}{most well. voobshe eto po-angliyski?}
+When an analyzed sample is anisotropic, i.e., it is stretched or oriented along
+some specific direction, it may be beneficial to align one of the cathetus of 
+sampling triangle \cref{fig:pattern} with that direction. In this case the
+anisotropy present in the sample will be properly captured by computed 3-pint correlation function.
 
@@
 $\det T = 1$). Application of this rotation to the sample makes the direction of
-anisotropy parallel to one of the axes, so anisotropy can be better featured in
+anisotropy parallel to one of the axes, so anisotropy can be better represented in
 the correlation function \cref{fig:aniso}.
@@
     directed along one of the axes. A result on \cref{fig:aniso-avg} averaged
-    across rotations is similar to the algorithm proposed by Malmir~et~al.}
+    across rotations is similar to the algorithm described in \cite{berryman1988,SMITH1988176,malmir2018}. \highlight{Make empty image over (e)}}
   \label{fig:aniso}
 \end{figure*}
-The above said holds for every algorithm introduced in the paper.
 
+\subsection{Directional and averaged computations}
 When a sample is known to be isotropic, the correlation function may be
@@
 and then averaged across rotations to gather more statistics. This process is
-illustrated on \cref{fig:workflow}.
+illustrated on \cref{fig:workflow}. This way we obtain similar results to sampling procedures
+used in \cite{berryman1988,SMITH1988176,malmir2018}.
+
+Another approach is to fix a number of directions, for example, orthogonal and
+diagonal ones \cite{EPL1,EPL2,CFsjlpaper}. In other words, the sample is rotated with periodic boundary conditions
+to orient along predefined directions. After each rotation we compute correlation functions
+as described above and obtain a number of matrices $D_1 \times D_2$ that are then
+stacked to represent 3-point correlation functions computed in directions \cref{fig:workflow}.
+
+To summarize, \code{CorrelationFunctions.jl} allows to compute 3-point correlation functions
+averaged in all directions (by randomly rotating the sample), along predefined number of directions
+(e.g., orthogonal and diagonal by rotation in these directions)
+or along the direction of major anisotropy (that can be determined using \code{$detect\_anisotropy$} function).
+Full correlation map for 3-point functions is impractical due its huge size and is not implemented.
+
 \begin{figure*}[tp]
@@
     results across rotations, 4.~representing the result as a family of 2D
-    plots.}
+    plots. \highlight{Show "random rotation" at the slice, "Stack of directional functions" on the right-upper.}}
   \label{fig:workflow}
@@
 centers generated with Poisson process with parameter $\lambda$. In this case
-the expression for $S_2$ is following:
+the expression for $S_2$ is the following:
 \begin{equation}
@@
 On \cref{fig:balls} there is an intersection of such a set with $R = 0.02$ and
-$\lambda=5000$ and a cube $[0, 1]^3$. Because $R \ll 1$, we can use
+$\lambda=5000$ within a cube $[0, 1]^3$. Because $R \ll 1$, we can use
 \cref{eq:s2-balls} to verify our computations -- this is exactly what we present on
@@
 $[-1, 1]^3$ and obtaining precise values of $F_{sss}$ and secondly computing
-$F_{sss}$ with our algorithm, giving a discretized $400 \times 400 \times 400$
-pixels wide image as the input. $F_{sss}$ function is evaluated in $XY$
+$F_{sss}$ with our algorithm, giving a discretized volume of $400^3$
+voxels as the input. For ease of comparison, $F_{sss}$ function is evaluated within $XY$
 plane. Pointwise relative error of $F_{sss}$ is on
@@
   \caption[]{A comparison of $F_{sss}$ function calculated using our approach
-    with its precise values.}
+    with its precise values. \highlight{Make dumbbell around 20 percent smaller}}
   \label{fig:sss-verification}
@@
 \subsection{Applications to material images}
+
 \begin{table*}[!htp]
@@
     \hline
-    Sample name & Image type & Dimensions (pixels) & Image resolution ($\mu m / px$)
+    Sample name & Image type & Dimensions (pixels/voxels) & Image resolution ($\mu m$)
     & $C_{0.5}$ & Comment \\
@@
     Sandstone & XCT &  $500 \times 500 \times 500$ & 2.25 & 0.9703 & \\
-    Soil & XCT & $500 \times 500 \times 500$ & 0.72 & 0.9431 & Digitally
+    Soil & Reconstruction & $500 \times 500 \times 500$ & 0.72 & 0.9431 & Digitally
     magnified \\
-    Shale & XCT & $160 \times 160 \times 160$ & 2.25 & 0.8912 & \\
+    Shale & Reconstruction & $160 \times 160 \times 160$ & 2.25 & 0.8912 & \\
     Sandstone & SEM &  $1280 \times 869$ & 0.10 & 0.9613 & \\
@@
   \end{tabular}
-  \caption{Summary of samples used for calculation of correlation functions.}
+  \caption{Summary of samples used for calculation of correlation functions. \highlight{Remove comments?}}
   \label{tab:summary}
 \end{table*}
-In this section we compute correlation functions for 2- and 3-dimensional real
-samples. Table \ref{tab:summary} contains information about these samples. Note
+In this section we compute correlation functions for 2- and 3-dimensional
+porous media samples. Table \ref{tab:summary} contains information about these samples. Note
 that we compute surface correlation functions only for those samples for which
-the criterion $C_{0.5} > 0.97$ holds (the two sandstones and the soil). Images
-of the samples are on \cref{fig:samples}. On plots of correlation functions for
+the criterion $C_{0.5} > 0.97$ holds (the two sandstones and the soil) \cite{samarin2023robust}. Images
+of the samples are presented on \cref{fig:samples}. On plots of correlation functions for
 isotropic samples we provide a family of curves with the first argument of the
@@
 plateau at $r_2 \approx 20\ \mu m$. The sample is highly anisotropic (elongated
-along the ordinate). The samples has clusters which are $\sim 45\ \mu m$ in
+along the ordinate). The samples have clusters which are $\sim 45\ \mu m$ in
 diameter.
@@
 The anisotropic samples (the soil and the shale) were preliminarily rotated with
-periodic boundary conditions to align elongated pores with coordinate axes. The
-result of rotation can be seen on \cref{fig:samples-rot}. Heatmaps of $S_3$
-function for these samples can be seen on \cref{fig:heatmaps}. It can be
-observed that elongated clusters of the void phase in the sample of soil form a
+periodic boundary conditions to align elongated pores with coordinate axes. Rotated samples 
+are presented on \cref{fig:samples-rot} and heatmaps of $S_3$
+function for these samples -- on \cref{fig:heatmaps}. Based on the analysis of correlation functions it is
+evident that elongated clusters of the void phase within the Soil sample form a
 structure which resembles a regular grid with spacing of about $60 \mu m$. The
@@
 the rest of correlation functions for the sample of soil on
-\cref{fig:soil-maps}.
+\cref{fig:soil-maps} - \highlight{and what can we see here?}.
 
@@
 \subsection{Execution times for our algorithms}
-In this section we measure execution times of our algorithms for random
-3-dimensional arrays of bits (i.e. each element can be either 0 or 1). The
-arrays have equal number of elements along each direction therefore
-representing cubes of 2-phase porous media. The number of voxels $N$ in each
+In this section we assess execution times of proposed computational algorithms for random
+3-dimensional arrays of bits (i.e. each element can be either 0 or 1). For ease of analysis, the
+arrays have the equal number of elements along each direction therefore
+representing cubes of binary porous media. The number of voxels $V$ in each
 cube increases from $1.25 \cdot 10^5$ to $2.7 \cdot 10^7$ linearly. Times of
-execution are measured for each function executed on a CPU and a GPU. Hardware
+execution are measured separately for each function executed on a CPU and a GPU. Hardware
 and software components used for testing are listed in \cref{tab:machine}. Each
-computation of a correlation function is equivalent to testing $N^{5/3}$ pattern
-triangles thrown into the sample.
+computation of a correlation function is equivalent to throwing of $V^{5/3}$ pattern
+triangles into the sample.
 \begin{table*}[!htp]
@@
 \end{figure*}
-The results are on \cref{fig:timings}. It can be observed that the time of
-execution is a power function of number of voxels. GPU gives a
-10x-100x performance boost depending on the correlation function.
+
+Wall times are shown in \cref{fig:timings}. It can be seen that the time of
+execution is a power function of voxels number. GPU gives a
+10x-100x performance boost depending on the correlation function. Note that
+random pixel/voxel patterns are a hard test for some functions, especially for
+$C_3$, as it produces a huge number of separate clusters. Thus, for real samples
+execution times can be even smaller compared to those reported on \cref{fig:timings}.
+
+Direct comparison against existing modern approaches, namely described by Malmir et al. \cite{malmir2018}
+and by Sun et al. \cite{sun2022third}, is not always straightforward due to algorithmic differences.
+In particular, the latter cited work computes 3-point correlation functions for sphere packings in the continuous domain;
+however, on a GPU it takes approximately 28 hours to perform $2\times10^6$ samplings (see Table 1 in \cite{sun2022third}). 
+Considering verification results in \cref{sec:results}, it seems that it would be much faster to discretize the sphere packing
+with appropriate $C_{0.5} > 0.97$ and to utilize our package to assess correlation functions within tens of minutes without any loss in accuracy.
+For $S_3$ and 3-point surface functions, Malmir et al. reported computation times of a couple of minutes for a $128^3$ voxels 
+3D image with $2\times10^5$ samples on CPU (see section IV in \cite{malmir2018}).
+In our case, we sample $\approx 31\times10^9$ triangles within 2 sec on CPU, and less than a second on GPU.
+Our implementation of $C_3$ is even more performant compared to existing counterparts.
 
@@
 \label{sec:discussion}
-In this paper we have provided two approaches to compute three-point correlation
-function:
+In this contribution we have presented two approaches to compute three-point correlation
+function $S_3$ which is used as a basis to assess $C_3, F_{sss}, F_{ssv}$ and $F_{svv}$:
 \begin{enumerate}
@@
   be used only with small inputs. Moreover, the whole Fourier image of the input
-  is needed even if we need only a small part of the correlation map.
-\item Computation in spatial domain. This approach is implemented by us in
-  CorrelationFunctions.jl package. This approach calculates the full map with
+  is needed even if only a small portion of the correlation map is of interest.
+\item Computation in spatial domain. This approach is implemented in
+  \code{CorrelationFunctions.jl} package. This approach calculates the full map with
   complexity $O(n^3)$ but uses only $O(n)$ additional memory for shifted
@@
 It's tempting to create an algorithm which unites advantages of both approaches
-(fast speed of the first and low memory consumption of the second) which
-computes some desired slices of correlation map. It is known that Fourier
+(fast speed of the first and low memory consumption of the second) to
+compute some desired slices of the full correlation map. It is known that Fourier
 transform is the only linear transform which allows computation of convolution
@@
 
-\textcolor{red}{Where to put this?}
-We have made a comparison of our algorithm with two algorithms, one of which
-proposed by Malmir~et~al \cite{malmir2018} and another proposed by Smith and
-Torquato \cite{SMITH1988176}. The first algorithms generates a triangle with
+We have made execuation time comparisons of our algorithm with existing algorithms.
+However, it is also beneficial to compare some algorithmic details against existing digital approaches --
+proposed by Malmir~et~al \cite{malmir2018} and another one by Smith and
+Torquato \cite{SMITH1988176}. The first algorithm generates a triangle with
 fixed sides $r_1$ and $r_2$ and an arbitrary angle $\theta$ between them and
@@
 orientation of triangles stored in the pattern. The main advantage of our
-algorithm is its parallelizability and ease of implementation. A drawback is
+approach based on right triangle is in its parallelizability and ease of implementation. A drawback is
 that an angle between catheti of the sampling pattern is fixed to be
-$\theta = \frac{\pi}{2}$ but the pattern can be rotated as a whole by an
+$\theta = \frac{\pi}{2}$, but can be mitigated by rotation of the pattern as a whole by an
 equivalent operation of rotation of a sample. These rotations can be random as
-in the Malmir's algorithm (\cref{fig:aniso-avg}), or it can be a single rotation
+in the Malmir et al. algorithm (\cref{fig:aniso-avg}), or it can be a single rotation
 to align catheti of the sampling triangle with the direction of anisotropy
-(\cref{fig:aniso-rot-s3}).
+(\cref{fig:aniso-rot-s3}). The latter allows computing directional 3-point correlation functions
+for anisotropic structures similar to 2-point counterparts \cite{10.1063/1.4867611,EPL1}.
+
+As was mentioned in the \cref{sec:intro} section, computation of 3-point correlation functions can be beneficial
+for some applications, yet the trade-off between computational/storage burden due to higher orders and information content
+is still not clear. The same goes for representation of the correlation functions -- either in the form of
+averaged or directional functions, or as a full correlation map. The latter is larger than the original image
+and was found beneficial only in a limited number of applications, for example, in 3D stochastic reconstructions 
+from 2D cuts \cite{cherkasov2021adaptive}. Computation of 3-point functions for 3D image even along a single direction with
+a simplified pattern in the form of right-angle triangle produces a 2D matrix similar in size to a 2D cut through
+the sample at hand \cref{fig:workflow}. Averaging over a huge number of directions produces the same volume of
+data, but looses all information about directional differences within the structure. Computation of CFs with n > 3 results
+in multidimensional matrices larger than the 3D image. The only way to keep this profusion 
+of floats at bay is to utilize the pattern that can be described with a single parameter while shifting without 
+rotations \cite{chen2019hierarchical,chen2022}. In this fashion the results can be still represented by a single function
+similar to 2-point CFs. But weather this approach produces the descriptors with higher information content is an open question.
+In light of this discussion, at this point we decided to limit \code{CorrelationFunctions.jl} with $n=3$, keeping in mind that
+extension of our algorithms to $n>3$ for $S_n, C_n, F_{s...s}$ and $F_{s...v}$ 
+is actually not that complicated \cite{dimitrakopoulos2010high}.
 
@@
 useful set of correlation functions and compare their information content
-against classical and other metrics.
+against classical and other metrics. If computationally effective methodology 
+for information content assessment will be developed, it should amend all
+aforementioned uncertainties and provide a clear winner -- a plethora of different 2-point CFs
+or a less numerous set of higher-order functions. Such long awaited answer
+would not be universal thought and depends not only on descriptor's information content versus
+data volume ratio, but also on its applicability to solve particular problems. For example,
+it is well known that cluster $C_2$ function provides a lot of information in addition to $S_2$ \cite{JiaoPNAS},
+yet it's application in stochastic reconstructions is very limited due to computational burden of cluster
+relabeling during annealing \cite{PLoS_ONE}. Still, effective information content assessment techniques
+will provide a possibility to account for such additional application constraints.
+
+As described in this paper, 3-point CFs computations can be immediately applied in a great number of
+research applications, for example: 1) flow and transport velocity fields analysis or any data with non-Gaussian signatures,
+2) deep learning for structural and physical properties (at least to observe the differences between 2-point and 3-point based
+training datasets), 3) structure taxonomy and categorization. In all these and numerous other potential cases the ability
+to compute directional 3-point functions may be crucial. Notably, the organization of the code functions for 3-point CFs
+computation is similar to those previously developed for 2-point functions \cite{CFsjlpaper}, thus, allowing computation
+of cross-correlation, i.e., one can compute 3-point CFs for multiphase images (while binary structures were used in this paper
+for simplicity).
+
+\section{Summary}
+In this paper, we have considered the problem of computing n-point correlation functions, namely $S_n, C_n, F_{s...s}$ and $F_{s...v}$,
+for which computationally efficient algorithms can be developed (including computations on GPU). For $n=3$ we have developed code in
+Julia language to compute $S_3, C_3, F_{sss}, F_{ssv}$ and $F_{svv}$ with a right-angle triangle pattern. This pattern is much
+easier to vectorize and parallelize compared to previously used random triangle or spider-web sampling patterns. Moreover,
+it allows to easily implement computations of directional 3-point CFs. The execution times
+for the same number of sample are orders of magnitude lower than existing published counterparts. We showed that the volume of
+data produced get unwieldy very easily, especially if computations are performed in frequency domain. For these reasons until
+information content of different sets of correlation functions with different "n-pointness" is not known, it is seemingly
+no much reason to increase the number of points. Nonetheless, developed algorithms and code are universal enough to be
+easily extendable to any $n$ (with increasing computational and RAM burden). All results are available as part of open source
+package \code{CorrelationFunctions.jl}, developed by our group and freely available to the public with numerous Jupiter
+notebooks showing examples of applications to assess 3-point correlation functions for 2D and 3D images.
 

### 2024-02-12 paper.tex
Smaller dumpbell
Remove comments in the table

@@
   \caption[]{A comparison of $F_{sss}$ function calculated using our approach
-    with its precise values. \highlight{Make dumbbell around 20 percent smaller}}
+    with its precise values.}
   \label{fig:sss-verification}
@@
   \centering
-  \begin{tabular}{|c|c|c|c|c|c|}
+  \begin{tabular}{|c|c|c|c|c|}
     \hline
     Sample name & Image type & Dimensions (pixels/voxels) & Image resolution ($\mu m$)
-    & $C_{0.5}$ & Comment \\
+    & $C_{0.5}$ \\
     \hline
-    Sandstone & XCT &  $500 \times 500 \times 500$ & 2.25 & 0.9703 & \\
-    Soil & Reconstruction & $500 \times 500 \times 500$ & 0.72 & 0.9431 & Digitally
-    magnified \\
-    Shale & Reconstruction & $160 \times 160 \times 160$ & 2.25 & 0.8912 & \\
-    Sandstone & SEM &  $1280 \times 869$ & 0.10 & 0.9613 & \\
+    Sandstone & XCT &  $500 \times 500 \times 500$ & 2.25 & 0.9703 \\
+    Soil & Reconstruction & $500 \times 500 \times 500$ & 0.72 & 0.9431 \\
+    Shale & Reconstruction & $160 \times 160 \times 160$ & 2.25 & 0.8912 \\
+    Sandstone & SEM &  $1280 \times 869$ & 0.10 & 0.9613 \\
     \hline
   \end{tabular}
-  \caption{Summary of samples used for calculation of correlation functions. \highlight{Remove comments?}}
+  \caption{Summary of samples used for calculation of correlation functions.}
   \label{tab:summary}

### 2024-02-12 paper.tex
A significant contribution from Marina Karsanina

@@
 
+\begin{figure*}[ht]
+  \centering
+  \includegraphics[width=0.8\linewidth]{images/3point.png}
+  \caption[]{A schematic representation of a binary porous media (pores are
+    shaded) with examples of CFs computations (all classic two- and three-point
+    correlation functions are presented according to the legend on the left
+    side). Computations take into account all possible configurations of a line
+    segment which either make a contribution to the CF (conventionally shown as
+    ``CF = 1'') or do not make a contribution (``CF = 0'').}
+  \label{fig:3point-scheme}
+\end{figure*}
 The large portion of the research papers mentioned above
@@
 measures the probability that the whole segment lies within the phase (see
-\highlight{Fig.1}). Compared to other descriptors, CFs possess a number of
-features making them, in our opinion, a perfect candidate for universal
+\cref{fig:3point-scheme}). Compared to other descriptors, CFs possess a number
+of features making them, in our opinion, a perfect candidate for universal
 descriptor:

### 2024-02-12 paper.tex
One more significant contribution from Marina Karsanina

@@
   \caption[]{The pattern used for calculation of $S_3$ function in our
-    implementation. Vectors $x_1$ and $x_2$ are parallel to one of the axes $X$,
-    $Y$ or $Z$ and have lengths $r_1$ and $r_2$ respectively. A red triangle
-    contributes to $S_3(2, 6)$ and blue triangles contribute to $S_3(1, 1)$.}
+    implementation.}
   \label{fig:pattern}

### 2024-02-12 paper.tex
Las noch eine wertvolle Bemerkung erwägen

@@
 the correlation function \cref{fig:aniso}.
-\begin{figure*}[tp]
+\begin{figure*}[!htp]
   \centering
-  \subfigure[An original image of an anisotropic pore.]{
-    \includegraphics[width=0.4\linewidth, frame]{images/aniso.png}
-    \label{fig:aniso-unrot}}
-  \hfill
-  \subfigure[A rotated image of the pore, so it is elongated along the axis
-    $X$.]{
-    \includegraphics[width=0.4\linewidth, frame]{images/aniso-rot.png}
-    \label{fig:aniso-rot}}
-  \vskip\baselineskip
-  \subfigure[$S_3$ function for the original image]{
-    \includegraphics[width=0.3\linewidth]{images/aniso-s3.png}}
-  \hfill
-  \subfigure[$S_3$ function for the rotated image. A vector $(0.92, -0.4)$ is a
-    direction of elongation of the pore.]{
-    \includegraphics[width=0.3\linewidth]{images/aniso-rot-s3.png}
-    \label{fig:aniso-rot-s3}}
-  \hfill
-  \subfigure[$S_3$ function averaged across 100 random rotations.]{
-    \includegraphics[width=0.3\linewidth]{images/aniso-avg-s3.png}
-    \label{fig:aniso-avg}}
-  \caption[]{Behaviour of our algorithm for calculation of the $S_3$ function
+  \begin{tabular}{ccc}
+    \includegraphics[width=0.3\linewidth, frame]{images/aniso.png} &
+    \includegraphics[width=0.3\linewidth, frame]{images/aniso-rot.png} & \\
+    \includegraphics[width=0.3\linewidth]{images/aniso-s3.png} &
+    \includegraphics[width=0.3\linewidth]{images/aniso-rot-s3.png} &
+    \includegraphics[width=0.3\linewidth]{images/aniso-avg-s3.png} \\
+  \end{tabular}
+  \caption{Behaviour of our algorithm for calculation of the $S_3$ function
     when dealing with highly anisotropic media. The pattern \cref{fig:pattern}
     which we use in our algorithm is most sensitive to anisotropy which is
-    directed along one of the axes. A result on \cref{fig:aniso-avg} averaged
-    across rotations is similar to the algorithm described in \cite{berryman1988,SMITH1988176,malmir2018}. \highlight{Make empty image over (e)}}
+    directed along one of the axes. \\
+    From top down, left to right: an original image of an anisotropic pore; a
+    rotated image of the pore, so it is elongated along the axis; $S_3$ function
+    for the original pore; $S_3$ function for the rotated pore with a vector
+    $(0.92, -0.4)$ being a direction of elongation of the pore; $S_3$ function
+    averaged across rotations similar to the algorithm described in
+    \cite{berryman1988,SMITH1988176,malmir2018}.}
   \label{fig:aniso}
@@
 equivalent operation of rotation of a sample. These rotations can be random as
-in the Malmir et al. algorithm (\cref{fig:aniso-avg}), or it can be a single rotation
+in the Malmir et al. algorithm, or it can be a single rotation
 to align catheti of the sampling triangle with the direction of anisotropy
-(\cref{fig:aniso-rot-s3}). The latter allows computing directional 3-point correlation functions
+(\cref{fig:aniso}). The latter allows computing directional 3-point correlation functions
 for anisotropic structures similar to 2-point counterparts \cite{10.1063/1.4867611,EPL1}.

### 2024-02-12 paper.tex
Fix formatting

@@
 (e.g., velocity or pressure) are ubiquitous in research applications and
-frequently require description for subsequent analysis, or stochastic reconstruction from limited data.
-The classical descriptors are 2-point correlation functions (CFs), but the computation of 3-point statistics is known to be
-advantageous in some cases as they can probe non-Gaussian signatures, not captured by their 2-point counterparts.
-Moreover, 3-point and CFs with $n>3$ are believed to possess larger information content and provide 
-more information about studies structures. In this paper, we have developed algorithms and code to compute 
-$S_3, C_3, F_{sss}, F_{ssv}$ and $F_{svv}$ with a right-angle triangle pattern. This pattern is much
-easier to vectorize and parallelize compared to previously used random triangle or spider-web sampling patterns. Moreover,
-it allows to easily implement computations of directional 3-point CFs. The execution times
-for the same number of sample are orders of magnitude lower than existing published counterparts. We showed that the volume of
-data produced get unwieldy very easily, especially if computations are performed in frequency domain. For these reasons until
-information content of different sets of correlation functions with different "n-pointness" is not known, 
-advantages of CFs with $n>3$ are not clear. Nonetheless, developed algorithms and code are universal enough to be
-easily extendable to any $n$ (with increasing computational and RAM burden). All results are available as part of open source
-package \code{CorrelationFunctions.jl} [Postnicov et al., 2024, Comp.Phys.Commun(accepted)]. As described in this paper, 
-3-point CFs computations can be immediately applied in a great number of
-research applications, for example: 1) flow and transport velocity fields analysis or any data with non-Gaussian signatures,
-2) deep learning for structural and physical properties, 3) structure taxonomy and categorization. 
-In all these and numerous other potential cases the ability
-to compute directional 3-point functions may be crucial. Notably, the organization of the code functions allows computation
-of cross-correlation, i.e., one can compute 3-point CFs for multiphase images (while binary structures were used in this paper
-for simplicity of explanations).
+frequently require description for subsequent analysis, or stochastic
+reconstruction from limited data.  The classical descriptors are 2-point
+correlation functions (CFs), but the computation of 3-point statistics is known
+to be advantageous in some cases as they can probe non-Gaussian signatures, not
+captured by their 2-point counterparts.  Moreover, 3-point and CFs with $n>3$
+are believed to possess larger information content and provide more information
+about studies structures. In this paper, we have developed algorithms and code
+to compute $S_3, C_3, F_{sss}, F_{ssv}$ and $F_{svv}$ with a right-angle
+triangle pattern. This pattern is much easier to vectorize and parallelize
+compared to previously used random triangle or spider-web sampling
+patterns. Moreover, it allows to easily implement computations of directional
+3-point CFs. The execution times for the same number of sample are orders of
+magnitude lower than existing published counterparts. We showed that the volume
+of data produced get unwieldy very easily, especially if computations are
+performed in frequency domain. For these reasons until information content of
+different sets of correlation functions with different "n-pointness" is not
+known, advantages of CFs with $n>3$ are not clear. Nonetheless, developed
+algorithms and code are universal enough to be easily extendable to any $n$
+(with increasing computational and RAM burden). All results are available as
+part of open source package \code{CorrelationFunctions.jl} [Postnicov et al.,
+  2024, Comp.Phys.Commun(accepted)]. As described in this paper, 3-point CFs
+computations can be immediately applied in a great number of research
+applications, for example: 1) flow and transport velocity fields analysis or any
+data with non-Gaussian signatures, 2) deep learning for structural and physical
+properties, 3) structure taxonomy and categorization.  In all these and numerous
+other potential cases the ability to compute directional 3-point functions may
+be crucial. Notably, the organization of the code functions allows computation
+of cross-correlation, i.e., one can compute 3-point CFs for multiphase images
+(while binary structures were used in this paper for simplicity of
+explanations).
 \end{abstract}
@@
 evolution of such metrics was mainly induced by the ease of measurement and
-interpretation. In fact, we need a single universal descriptor defined by only one characteristic -- information
-content. The latter is an ability of the metric to describe the structure at
-hand with 100$\%$ meaning the ability to fully recover the structure back from
-this metric. Thus, universal descriptor has to possess following key properties:
-(1) high information content, (2) ease of assess, (3) high compression ratio (i.e.,
-descriptor is much "smaller" than the structure itself).
+interpretation. In fact, we need a single universal descriptor defined by only
+one characteristic -- information content. The latter is an ability of the
+metric to describe the structure at hand with 100\% meaning the ability to
+fully recover the structure back from this metric. Thus, universal descriptor
+has to possess following key properties: (1) high information content, (2) ease
+of assess, (3) high compression ratio (i.e., descriptor is much "smaller" than
+the structure itself).
 
@@
 Our implementation fixes $x_1$ and $x_2$ to be parallel to one of the axes $X$,
-$Y$ or $Z$ with restriction $x_1 \perp x_2$ (\cref{fig:pattern}) \cite{dimitrakopoulos2010high}. Thus, the
-output has dimensions $D_1 \times D_2$ where $D_1$ and $D_2$ are dimensions of
-the input array along selected axes. Note that shift operators with such $x_1$ and $x_2$
-represent a 3-point function computed within a 3D domain, but along a predefined direction (see below).
+$Y$ or $Z$ with restriction $x_1 \perp x_2$ (\cref{fig:pattern})
+\cite{dimitrakopoulos2010high}. Thus, the output has dimensions $D_1 \times D_2$
+where $D_1$ and $D_2$ are dimensions of the input array along selected
+axes. Note that shift operators with such $x_1$ and $x_2$ represent a 3-point
+function computed within a 3D domain, but along a predefined direction (see
+below).
 \begin{figure}[ht]
@@
 sampling triangle \cref{fig:pattern} with that direction. In this case the
-anisotropy present in the sample will be properly captured by computed 3-pint correlation function.
+anisotropy present in the sample will be properly captured by computed 3-point
+correlation function.
 
@@
 and then averaged across rotations to gather more statistics. This process is
-illustrated on \cref{fig:workflow}. This way we obtain similar results to sampling procedures
-used in \cite{berryman1988,SMITH1988176,malmir2018}.
+illustrated on \cref{fig:workflow}. This way we obtain similar results to
+sampling procedures used in \cite{berryman1988,SMITH1988176,malmir2018}.
 
 Another approach is to fix a number of directions, for example, orthogonal and
-diagonal ones \cite{EPL1,EPL2,CFsjlpaper}. In other words, the sample is rotated with periodic boundary conditions
-to orient along predefined directions. After each rotation we compute correlation functions
-as described above and obtain a number of matrices $D_1 \times D_2$ that are then
-stacked to represent 3-point correlation functions computed in directions \cref{fig:workflow}.
-
-To summarize, \code{CorrelationFunctions.jl} allows to compute 3-point correlation functions
-averaged in all directions (by randomly rotating the sample), along predefined number of directions
-(e.g., orthogonal and diagonal by rotation in these directions)
-or along the direction of major anisotropy (that can be determined using \code{$detect\_anisotropy$} function).
-Full correlation map for 3-point functions is impractical due its huge size and is not implemented.
+diagonal ones \cite{EPL1,EPL2,CFsjlpaper}. In other words, the sample is rotated
+with periodic boundary conditions to orient along predefined directions. After
+each rotation we compute correlation functions as described above and obtain a
+number of matrices $D_1 \times D_2$ that are then stacked to represent 3-point
+correlation functions computed in directions \cref{fig:workflow}.
+
+To summarize, \code{CorrelationFunctions.jl} allows to compute 3-point
+correlation functions averaged in all directions (by randomly rotating the
+sample), along predefined number of directions (e.g., orthogonal and diagonal by
+rotation in these directions) or along the direction of major anisotropy (that
+can be determined using \code{$detect\_anisotropy$} function).  Full correlation
+map for 3-point functions is impractical due its huge size and is not
+implemented.
 
@@
     results across rotations, 4.~representing the result as a family of 2D
-    plots. \highlight{Show "random rotation" at the slice, "Stack of directional functions" on the right-upper.}}
+    plots. \highlight{Show "random rotation" at the slice, "Stack of directional
+      functions" on the right-upper.}}
   \label{fig:workflow}
@@
 \end{table*}
-In this section we compute correlation functions for 2- and 3-dimensional
-porous media samples. Table \ref{tab:summary} contains information about these samples. Note
-that we compute surface correlation functions only for those samples for which
-the criterion $C_{0.5} > 0.97$ holds (the two sandstones and the soil) \cite{samarin2023robust}. Images
-of the samples are presented on \cref{fig:samples}. On plots of correlation functions for
-isotropic samples we provide a family of curves with the first argument of the
-correlation function being fixed. For anisotropic samples we provide heatmaps of
-correlation functions where anisotropy can be easily observed.
+In this section we compute correlation functions for 2- and 3-dimensional porous
+media samples. Table \ref{tab:summary} contains information about these
+samples. Note that we compute surface correlation functions only for those
+samples for which the criterion $C_{0.5} > 0.97$ holds (the two sandstones and
+the soil) \cite{samarin2023robust}. Images of the samples are presented on
+\cref{fig:samples}. On plots of correlation functions for isotropic samples we
+provide a family of curves with the first argument of the correlation function
+being fixed. For anisotropic samples we provide heatmaps of correlation
+functions where anisotropy can be easily observed.
 \begin{figure*}[tp]
@@
 The anisotropic samples (the soil and the shale) were preliminarily rotated with
-periodic boundary conditions to align elongated pores with coordinate axes. Rotated samples 
-are presented on \cref{fig:samples-rot} and heatmaps of $S_3$
-function for these samples -- on \cref{fig:heatmaps}. Based on the analysis of correlation functions it is
-evident that elongated clusters of the void phase within the Soil sample form a
-structure which resembles a regular grid with spacing of about $60 \mu m$. The
-sample of shale shows less regular yet still anisotropic structure. We provide
-the rest of correlation functions for the sample of soil on
-\cref{fig:soil-maps} - \highlight{and what can we see here?}.
+periodic boundary conditions to align elongated pores with coordinate
+axes. Rotated samples are presented on \cref{fig:samples-rot} and heatmaps of
+$S_3$ function for these samples -- on \cref{fig:heatmaps}. Based on the
+analysis of correlation functions it is evident that elongated clusters of the
+void phase within the Soil sample form a structure which resembles a regular
+grid with spacing of about $60 \mu m$. The sample of shale shows less regular
+yet still anisotropic structure. We provide the rest of correlation functions
+for the sample of soil on \cref{fig:soil-maps} - \highlight{and what can we see
+  here?}.
 
@@
 \subsection{Execution times for our algorithms}
-In this section we assess execution times of proposed computational algorithms for random
-3-dimensional arrays of bits (i.e. each element can be either 0 or 1). For ease of analysis, the
-arrays have the equal number of elements along each direction therefore
-representing cubes of binary porous media. The number of voxels $V$ in each
-cube increases from $1.25 \cdot 10^5$ to $2.7 \cdot 10^7$ linearly. Times of
-execution are measured separately for each function executed on a CPU and a GPU. Hardware
-and software components used for testing are listed in \cref{tab:machine}. Each
-computation of a correlation function is equivalent to throwing of $V^{5/3}$ pattern
-triangles into the sample.
+In this section we assess execution times of proposed computational algorithms
+for random 3-dimensional arrays of bits (i.e. each element can be either 0 or
+1). For ease of analysis, the arrays have the equal number of elements along
+each direction therefore representing cubes of binary porous media. The number
+of voxels $V$ in each cube increases from $1.25 \cdot 10^5$ to $2.7 \cdot 10^7$
+linearly. Times of execution are measured separately for each function executed
+on a CPU and a GPU. Hardware and software components used for testing are listed
+in \cref{tab:machine}. Each computation of a correlation function is equivalent
+to throwing of $V^{5/3}$ pattern triangles into the sample.
 \begin{table*}[!htp]
@@
 
-Direct comparison against existing modern approaches, namely described by Malmir et al. \cite{malmir2018}
-and by Sun et al. \cite{sun2022third}, is not always straightforward due to algorithmic differences.
-In particular, the latter cited work computes 3-point correlation functions for sphere packings in the continuous domain;
-however, on a GPU it takes approximately 28 hours to perform $2\times10^6$ samplings (see Table 1 in \cite{sun2022third}). 
-Considering verification results in \cref{sec:results}, it seems that it would be much faster to discretize the sphere packing
-with appropriate $C_{0.5} > 0.97$ and to utilize our package to assess correlation functions within tens of minutes without any loss in accuracy.
-For $S_3$ and 3-point surface functions, Malmir et al. reported computation times of a couple of minutes for a $128^3$ voxels 
-3D image with $2\times10^5$ samples on CPU (see section IV in \cite{malmir2018}).
-In our case, we sample $\approx 31\times10^9$ triangles within 2 sec on CPU, and less than a second on GPU.
-Our implementation of $C_3$ is even more performant compared to existing counterparts.
+Direct comparison against existing modern approaches, namely described by Malmir
+et al. \cite{malmir2018} and by Sun et al. \cite{sun2022third}, is not always
+straightforward due to algorithmic differences.  In particular, the latter cited
+work computes 3-point correlation functions for sphere packings in the
+continuous domain; however, on a GPU it takes approximately 28 hours to perform
+$2\times10^6$ samplings (see Table 1 in \cite{sun2022third}).  Considering
+verification results in \cref{sec:results}, it seems that it would be much
+faster to discretize the sphere packing with appropriate $C_{0.5} > 0.97$ and to
+utilize our package to assess correlation functions within tens of minutes
+without any loss in accuracy.  For $S_3$ and 3-point surface functions, Malmir
+et al. reported computation times of a couple of minutes for a $128^3$ voxels 3D
+image with $2\times10^5$ samples on CPU (see section IV in \cite{malmir2018}).
+In our case, we sample $\approx 31\times10^9$ triangles within 2 sec on CPU, and
+less than a second on GPU.  Our implementation of $C_3$ is even more performant
+compared to existing counterparts.
 
@@
 
-We have made execuation time comparisons of our algorithm with existing algorithms.
-However, it is also beneficial to compare some algorithmic details against existing digital approaches --
-proposed by Malmir~et~al \cite{malmir2018} and another one by Smith and
-Torquato \cite{SMITH1988176}. The first algorithm generates a triangle with
-fixed sides $r_1$ and $r_2$ and an arbitrary angle $\theta$ between them and
-places it in the medium firstly making a random translation and a rotation
-around a random vector by a random angle. By making a large number of trials the
-algorithm gets a value of a three-point correlation function at the point
-$(r_1, r_2, \theta)$. The second algorithm takes a precalculated triangle
-$(r_1, r_2, \theta)$ from a web-like pattern and places it in the medium without
-rotation, only applying a random translation. This way the algorithm preserves
-orientation of triangles stored in the pattern. The main advantage of our
-approach based on right triangle is in its parallelizability and ease of implementation. A drawback is
-that an angle between catheti of the sampling pattern is fixed to be
-$\theta = \frac{\pi}{2}$, but can be mitigated by rotation of the pattern as a whole by an
-equivalent operation of rotation of a sample. These rotations can be random as
-in the Malmir et al. algorithm, or it can be a single rotation
-to align catheti of the sampling triangle with the direction of anisotropy
-(\cref{fig:aniso}). The latter allows computing directional 3-point correlation functions
-for anisotropic structures similar to 2-point counterparts \cite{10.1063/1.4867611,EPL1}.
-
-As was mentioned in the \cref{sec:intro} section, computation of 3-point correlation functions can be beneficial
-for some applications, yet the trade-off between computational/storage burden due to higher orders and information content
-is still not clear. The same goes for representation of the correlation functions -- either in the form of
-averaged or directional functions, or as a full correlation map. The latter is larger than the original image
-and was found beneficial only in a limited number of applications, for example, in 3D stochastic reconstructions 
-from 2D cuts \cite{cherkasov2021adaptive}. Computation of 3-point functions for 3D image even along a single direction with
-a simplified pattern in the form of right-angle triangle produces a 2D matrix similar in size to a 2D cut through
-the sample at hand \cref{fig:workflow}. Averaging over a huge number of directions produces the same volume of
-data, but looses all information about directional differences within the structure. Computation of CFs with n > 3 results
-in multidimensional matrices larger than the 3D image. The only way to keep this profusion 
-of floats at bay is to utilize the pattern that can be described with a single parameter while shifting without 
-rotations \cite{chen2019hierarchical,chen2022}. In this fashion the results can be still represented by a single function
-similar to 2-point CFs. But weather this approach produces the descriptors with higher information content is an open question.
-In light of this discussion, at this point we decided to limit \code{CorrelationFunctions.jl} with $n=3$, keeping in mind that
-extension of our algorithms to $n>3$ for $S_n, C_n, F_{s...s}$ and $F_{s...v}$ 
-is actually not that complicated \cite{dimitrakopoulos2010high}.
-
-We mentioned that classic set of correlation functions describes
-both the geometry and topology of the structure at hand -- but this is to yet
-unknown extent. With the advent of analytical methods
-\cite{cherkasov2023towards} to assess information content of arbitrary
-descriptor for structure of any size, it will be possible to choose the most
-useful set of correlation functions and compare their information content
-against classical and other metrics. If computationally effective methodology 
-for information content assessment will be developed, it should amend all
-aforementioned uncertainties and provide a clear winner -- a plethora of different 2-point CFs
-or a less numerous set of higher-order functions. Such long awaited answer
-would not be universal thought and depends not only on descriptor's information content versus
-data volume ratio, but also on its applicability to solve particular problems. For example,
-it is well known that cluster $C_2$ function provides a lot of information in addition to $S_2$ \cite{JiaoPNAS},
-yet it's application in stochastic reconstructions is very limited due to computational burden of cluster
-relabeling during annealing \cite{PLoS_ONE}. Still, effective information content assessment techniques
-will provide a possibility to account for such additional application constraints.
-
-As described in this paper, 3-point CFs computations can be immediately applied in a great number of
-research applications, for example: 1) flow and transport velocity fields analysis or any data with non-Gaussian signatures,
-2) deep learning for structural and physical properties (at least to observe the differences between 2-point and 3-point based
-training datasets), 3) structure taxonomy and categorization. In all these and numerous other potential cases the ability
-to compute directional 3-point functions may be crucial. Notably, the organization of the code functions for 3-point CFs
-computation is similar to those previously developed for 2-point functions \cite{CFsjlpaper}, thus, allowing computation
-of cross-correlation, i.e., one can compute 3-point CFs for multiphase images (while binary structures were used in this paper
-for simplicity).
+We have made execuation time comparisons of our algorithm with existing
+algorithms.  However, it is also beneficial to compare some algorithmic details
+against existing digital approaches -- proposed by Malmir~et~al
+\cite{malmir2018} and another one by Smith and Torquato \cite{SMITH1988176}. The
+first algorithm generates a triangle with fixed sides $r_1$ and $r_2$ and an
+arbitrary angle $\theta$ between them and places it in the medium firstly making
+a random translation and a rotation around a random vector by a random angle. By
+making a large number of trials the algorithm gets a value of a three-point
+correlation function at the point $(r_1, r_2, \theta)$. The second algorithm
+takes a precalculated triangle $(r_1, r_2, \theta)$ from a web-like pattern and
+places it in the medium without rotation, only applying a random
+translation. This way the algorithm preserves orientation of triangles stored in
+the pattern. The main advantage of our approach based on right triangle is in
+its parallelizability and ease of implementation. A drawback is that an angle
+between catheti of the sampling pattern is fixed to be $\theta = \frac{\pi}{2}$,
+but can be mitigated by rotation of the pattern as a whole by an equivalent
+operation of rotation of a sample. These rotations can be random as in the
+Malmir et al. algorithm, or it can be a single rotation to align catheti of the
+sampling triangle with the direction of anisotropy (\cref{fig:aniso}). The
+latter allows computing directional 3-point correlation functions for
+anisotropic structures similar to 2-point counterparts
+\cite{10.1063/1.4867611,EPL1}.
+
+As was mentioned in the \cref{sec:intro} section, computation of 3-point
+correlation functions can be beneficial for some applications, yet the trade-off
+between computational/storage burden due to higher orders and information
+content is still not clear. The same goes for representation of the correlation
+functions -- either in the form of averaged or directional functions, or as a
+full correlation map. The latter is larger than the original image and was found
+beneficial only in a limited number of applications, for example, in 3D
+stochastic reconstructions from 2D cuts
+\cite{cherkasov2021adaptive}. Computation of 3-point functions for 3D image even
+along a single direction with a simplified pattern in the form of right-angle
+triangle produces a 2D matrix similar in size to a 2D cut through the sample at
+hand \cref{fig:workflow}. Averaging over a huge number of directions produces
+the same volume of data, but looses all information about directional
+differences within the structure. Computation of CFs with n > 3 results in
+multidimensional matrices larger than the 3D image. The only way to keep this
+profusion of floats at bay is to utilize the pattern that can be described with
+a single parameter while shifting without rotations
+\cite{chen2019hierarchical,chen2022}. In this fashion the results can be still
+represented by a single function similar to 2-point CFs. But weather this
+approach produces the descriptors with higher information content is an open
+question.  In light of this discussion, at this point we decided to limit
+\code{CorrelationFunctions.jl} with $n=3$, keeping in mind that extension of our
+algorithms to $n>3$ for $S_n, C_n, F_{s...s}$ and $F_{s...v}$ is actually not
+that complicated \cite{dimitrakopoulos2010high}.
+
+We mentioned that classic set of correlation functions describes both the
+geometry and topology of the structure at hand -- but this is to yet unknown
+extent. With the advent of analytical methods \cite{cherkasov2023towards} to
+assess information content of arbitrary descriptor for structure of any size, it
+will be possible to choose the most useful set of correlation functions and
+compare their information content against classical and other metrics. If
+computationally effective methodology for information content assessment will be
+developed, it should amend all aforementioned uncertainties and provide a clear
+winner -- a plethora of different 2-point CFs or a less numerous set of
+higher-order functions. Such long awaited answer would not be universal thought
+and depends not only on descriptor's information content versus data volume
+ratio, but also on its applicability to solve particular problems. For example,
+it is well known that cluster $C_2$ function provides a lot of information in
+addition to $S_2$ \cite{JiaoPNAS}, yet it's application in stochastic
+reconstructions is very limited due to computational burden of cluster
+relabeling during annealing \cite{PLoS_ONE}. Still, effective information
+content assessment techniques will provide a possibility to account for such
+additional application constraints.
+
+As described in this paper, 3-point CFs computations can be immediately applied
+in a great number of research applications, for example: 1) flow and transport
+velocity fields analysis or any data with non-Gaussian signatures, 2) deep
+learning for structural and physical properties (at least to observe the
+differences between 2-point and 3-point based training datasets), 3) structure
+taxonomy and categorization. In all these and numerous other potential cases the
+ability to compute directional 3-point functions may be crucial. Notably, the
+organization of the code functions for 3-point CFs computation is similar to
+those previously developed for 2-point functions \cite{CFsjlpaper}, thus,
+allowing computation of cross-correlation, i.e., one can compute 3-point CFs for
+multiphase images (while binary structures were used in this paper for
+simplicity).
 
 \section{Summary}
-In this paper, we have considered the problem of computing n-point correlation functions, namely $S_n, C_n, F_{s...s}$ and $F_{s...v}$,
-for which computationally efficient algorithms can be developed (including computations on GPU). For $n=3$ we have developed code in
-Julia language to compute $S_3, C_3, F_{sss}, F_{ssv}$ and $F_{svv}$ with a right-angle triangle pattern. This pattern is much
-easier to vectorize and parallelize compared to previously used random triangle or spider-web sampling patterns. Moreover,
-it allows to easily implement computations of directional 3-point CFs. The execution times
-for the same number of sample are orders of magnitude lower than existing published counterparts. We showed that the volume of
-data produced get unwieldy very easily, especially if computations are performed in frequency domain. For these reasons until
-information content of different sets of correlation functions with different "n-pointness" is not known, it is seemingly
-no much reason to increase the number of points. Nonetheless, developed algorithms and code are universal enough to be
-easily extendable to any $n$ (with increasing computational and RAM burden). All results are available as part of open source
-package \code{CorrelationFunctions.jl}, developed by our group and freely available to the public with numerous Jupiter
-notebooks showing examples of applications to assess 3-point correlation functions for 2D and 3D images.
+In this paper, we have considered the problem of computing n-point correlation
+functions, namely $S_n, C_n, F_{s...s}$ and $F_{s...v}$, for which
+computationally efficient algorithms can be developed (including computations on
+GPU). For $n=3$ we have developed code in Julia language to compute $S_3, C_3,
+F_{sss}, F_{ssv}$ and $F_{svv}$ with a right-angle triangle pattern. This
+pattern is much easier to vectorize and parallelize compared to previously used
+random triangle or spider-web sampling patterns. Moreover, it allows to easily
+implement computations of directional 3-point CFs. The execution times for the
+same number of sample are orders of magnitude lower than existing published
+counterparts. We showed that the volume of data produced get unwieldy very
+easily, especially if computations are performed in frequency domain. For these
+reasons until information content of different sets of correlation functions
+with different "n-pointness" is not known, it is seemingly no much reason to
+increase the number of points. Nonetheless, developed algorithms and code are
+universal enough to be easily extendable to any $n$ (with increasing
+computational and RAM burden). All results are available as part of open source
+package \code{CorrelationFunctions.jl}, developed by our group and freely
+available to the public with numerous Jupiter notebooks showing examples of
+applications to assess 3-point correlation functions for 2D and 3D images.
 

### 2024-02-12 paper.tex
Pfeile

@@
     results across rotations, 4.~representing the result as a family of 2D
-    plots. \highlight{Show "random rotation" at the slice, "Stack of directional
-      functions" on the right-upper.}}
+    plots.}
   \label{fig:workflow}

### 2024-02-12 paper.tex
Remove red highlights
Actual hardware & software specifications

@@
 yet still anisotropic structure. We provide the rest of correlation functions
-for the sample of soil on \cref{fig:soil-maps} - \highlight{and what can we see
-  here?}.
+for the sample of soil on \cref{fig:soil-maps}.
 
@@
   \begin{tabular}{|c|c|}
-    CPU & Intel Celeron 333 MHz \\
-    RAM & 100500 GB DDR4 PC-XXXX \\
-    GPU & AMD Navi 21 \\
-    Julia & 1.10.0 \\
-    CUDA.jl & 4.0
+    CPU & Intel Xeon Gold 6248R @ 3GHz \\
+    RAM & 1TB DDR4-2933 \\
+    GPU & Nvidia Tesla V100 with 16 GB of RAM \\
+    Julia & 1.9.3 \\
+    CorrelationFunctions.jl & 0.10.3
   \end{tabular}

### 2024-02-12 paper.tex
An invaluable contribution from Alexey Khlupin

@@
 to be advantageous in some cases as they can probe non-Gaussian signatures, not
-captured by their 2-point counterparts.  Moreover, 3-point and CFs with $n>3$
+captured by their 2-point counterparts. Moreover, $n$-point CFs with $n \ge 3$
 are believed to possess larger information content and provide more information
@@
     there is a methodology for $S_2$ \cite{Gommes2} and approaches for other
-    functions \cite{Degeneraty.045306,cherkasov2023towards};
+    functions \cite{Degeneraty.045306,CHERKASOV2024129400};
   \item In addition to a possibility to compute correlation functions using
@@
 Let $A_1, A_2, \dots, A_n$ be pairwise disjoint subsets of a set
-$A \subset \mathbb{R}^n$, where the index can be interpreted as a phase on the
+$A \subset \mathbb{R}^m$, where the index can be interpreted as a phase on the
 image $A$. We introduce a family of indicator functions
@@
 Now we can define the three-point correlation function
-$S_3: \mathbb{R}^{2n} \rightarrow [0, 1]$:
+$S_3: \mathbb{R}^{2m} \rightarrow [0, 1]$:
 \begin{equation}
@@
 \end{equation}
-where $\langle \dots \rangle$ means average over all points in $A$. It can be
-understood as the probability that all three vertices of a triangle
-$(0, x_1, x_2)$ will appear in the subset $A_n$ when the triangle is randomly
-thrown in $A$. When $A$ represent isotropic medium, $x_1$ and $x_2$ can be
-replaced with three numbers $r_1 = |x_1|$, $r_2 = |x_2|$ and $r_3 = |x_2 - x_1|$
-to get a function of three scalar arguments.
+where $\langle \dots \rangle$ means ensemble average. It can be understood as
+the probability that all three vertices of a triangle $(0, x_1, x_2)$ will
+appear in the subset $A_n$ when the triangle is randomly thrown in $A$. When $A$
+represent isotropic medium, $x_1$ and $x_2$ can be replaced with three numbers
+$r_1 = |x_1|$, $r_2 = |x_2|$ and $r_3 = |x_2 - x_1|$ to get a function of three
+scalar arguments.
 
@@
 \begin{equation}
-  C_3^n(x_1, x_2) = \sum_{k=1}^K \langle \tilde{I}_k(x) \tilde{I}_k(x + x_1)
-  \tilde{I}_k(x + x_2) \rangle
-\end{equation}
-where $\tilde{I}_k$ is an indicator function for $k$-th cluster and $K$ is a
-total number of clusters. A cluster is a subset of $A_n$ so that any two points
-in this subset can be connected with a curve belonging to that subset.
+  C_3^n(x_1, x_2) = \sum_{k=1}^K \langle I_n^k(x) I_n^k(x + x_1) I_n^k(x + x_2) \rangle
+\end{equation}
+where $I_n^k$ is an indicator function for $k$-th cluster of $A_n$ and $K$
+is a total number of clusters. A cluster is a subset of $A_n$ so that any two
+points in this subset can be connected with a curve belonging to that subset.
 
@@
   F_{sss}^n(x_1, x_2) &= \langle M_n(x) M_n(x + x_1) M_n(x + x_2) \rangle \\
-  F_{ssv}^n(x_1, x_2) &= \langle M_n(x) M_v(x + x_1) I_v(x + x_2) \rangle \\
-  F_{svv}^n(x_1, x_2) &= \langle M_n(x) I_v(x + x_1) I_v(x + x_2) \rangle
+  F_{ssv}^n(x_1, x_2) &= \langle M_n(x) M_{(void)}(x + x_1) I_{(void)}(x + x_2) \rangle \\
+  F_{svv}^n(x_1, x_2) &= \langle M_n(x) I_{(void)}(x + x_1) I_{(void)}(x + x_2) \rangle
 \end{align}
-Here $I_v$ is an indicator function for the subset of the void phase
+Here $I_{(void)}$ is an indicator function for the subset of the void phase
 $A_v$. Unlike $S_3$ and $C_3$ functions, these functions do not have the meaning
 of probability and have the units of measurement inversely proportional to
-volume, surface and length, respectively (e.g., can be measured in $\mu m^{-3}$, $\mu m^{-2}$ and
-$\mu m^{-1}$ or other convenient dimensionless units depending on the problem to be solved). 
-These functions describe the interface of the subset $A_n$ and
-its spatial configuration with respect to $A_v$.
+volume, surface and length, respectively (e.g., can be measured in $\mu m^{-3}$,
+$\mu m^{-2}$ and $\mu m^{-1}$ or other convenient dimensionless units depending
+on the problem to be solved).  These functions describe the interface of the
+subset $A_n$ and its spatial configuration with respect to $A_v$.
 
@@
 accessing out-of-bounds array elements. In this case $\mathfrak{S}_z$ is a
-circular shift operator:
-\begin{equation}
-  A[x] \leftarrow A[x+z \mod d]
+circular shift operator (here ``$x \mod y$'' means a vector
+$(x_1 \mod y_1, x_2 \mod y_2, \dots)$):
+\begin{equation}
+  A[x] \leftarrow A[x+z \mod shape(A)]
 \end{equation}
@@
     \includegraphics[width=0.4\linewidth]{images/surfvoid2-map.png}}
-  \caption[]{Correlation maps for the sample of soil.}
+  \caption[]{Correlation maps for the cluster function and the surface functions
+    of the sample of soil. The functions are calculated for a rotation of the
+    sample which aligns the direction of anisotropy with the axes.}
   \label{fig:soil-maps}
@@
 geometry and topology of the structure at hand -- but this is to yet unknown
-extent. With the advent of analytical methods \cite{cherkasov2023towards} to
+extent. With the advent of analytical methods \cite{CHERKASOV2024129400} to
 assess information content of arbitrary descriptor for structure of any size, it

### 2024-04-23 paper.tex
Error of the rotation

@@
 anisotropy parallel to one of the axes, so anisotropy can be better represented in
-the correlation function \cref{fig:aniso}.
+the correlation function \cref{fig:aniso}. In our implementation we use rotation
+with nearest-neighbor interpolcation which affects quality of computations as
+discussed in \cref{sec:rotqua}.
 \begin{figure*}[!htp]
@@
 
+\section{Influence of sample rotation on quality of computations}
+\label{sec:rotqua}
+\begin{figure*}[tp]
+  \centering
+  \subfigure[A sample of value noise]{
+    \includegraphics[width=0.4\linewidth]{images/noise.png}
+    \label{fig:roterror-noise}}
+  \hfill
+  \subfigure[Relative error of computation]{
+    \includegraphics[width=0.4\linewidth]{images/roterror.png}
+    \label{fig:roterror-error}}
+  \caption[]{A plot of dependency of maximal pointwise relative error
+    \cref{eq:relerr} in computation of correlation functions introduced by a
+    rotation of the sample \cref{fig:roterror-noise} from the rotation
+    angle. The rotation is performed around $Z$ axis counter-clockwise using
+    nearest-neighbor interpolation.}
+  \label{fig:roterror}
+\end{figure*}
+Our edge extraction filter works only for binary samples, therefore it is
+natural to require that a rotated image remains binary. The simpliest way to do
+so is to use nearest-neighbor interpolation when sampling subvoxel data during
+rotation. This results only in minimal precision loss in computation of
+correlation functions.
+
+Speculatively, the loss in precision should be minimal for three-point and
+cluster correlation functions, because they are calculated
+``in the whole volume'' of the sample. The biggest loss should be for $F_{sss}$
+function because it takes into account only a small volume of the sample which
+lies closely to the interface between phases and this volume is the only volume
+affected by the rotation.
+
+To estimate the error introduced by rotation, consider a
+$300 \times 300 \times 300$ sample of value noise \cref{fig:roterror-noise}
+which is defined as $f(x, y, z) > T$ where $f$ is a value noise function and $T$
+is a threshold. We produce images of the noise rotated around $Z$ axis by $\phi$
+radians by discretizing an inequation $f(p(x'), p(y'), p(z')) > T$ where
+\begin{equation*}
+  \begin{aligned}
+    x' &= x \cos \phi + y \sin \phi \\
+    y' &= y \cos \phi - x \sin \phi \\
+    z' &= z
+  \end{aligned}
+\end{equation*}
+and
+\begin{equation*}
+  \begin{aligned}
+    p(x) &= \left\{
+    \begin{array}{ll}
+      x'     & \quad x' < 1 \\
+      2 - x' & \quad \text{otherwise}
+    \end{array}
+    \right. \\
+    x ' &= x \mod 2
+  \end{aligned}
+\end{equation*}
+Therefore we assume the noise to be periodic with the period equal to
+$2$ and the interface between phases is continuous. Discretizing for different
+values of $\phi \in [0, \pi/4]$ we obtain the first dataset which contains the
+best possible discretization of the rotated noise.
+
+The second dataset is constructed by discretizing the noise with $\phi = 0$ and
+then rotating the discretized image using nearest-neighbor interpolation.
+
+We compute $S_3$ and $F_{sss}$ functions in periodic mode for the both datasets
+and calculate pointwisely a relative error introduced by the rotation as
+\begin{equation}
+  \varepsilon = \frac{|F_1 - F_2|}{F_1}
+  \label{eq:relerr}
+\end{equation}
+where $F_1$ is a correlation function for a sample from the first dataset and
+$F_2$ is a correlation function for a sample from the second dataset. The we
+calculate the maximal relative error for each $\phi$ as the maximum of all
+pointwise errors for a given rotation angle.
+
+Plots of maximal relative errors for functions $S_3$ and $F_{sss}$ are on
+\cref{fig:roterror-error}. For the surface-surface-surface function we omit
+values $F_{sss}(s_1, s_2)$ if either of its arguments is less than 10 voxels
+because this function is undefined for either $s_1$ or $s_2$ being equal to zero
+and our edge detection filter gives at least 7 voxel transition zone where the
+correlation function is affected by this indeterminacy. The maximal error for
+all $\phi$'s are 0.6\% for $S_3$ and 4.4\% for $F_{sss}$.
+
 \bibliography{paper}

### 2024-04-23 data/error/calculate.jl

@@ -1,0 +1,20 @@
+module Shit
+import CorrelationFunctions.Directional as D
+import CorrelationFunctions.Utilities as U
+using NPZ
+using CUDA
+
+const fns = [D.surf3, D.s3]
+
+function foo(path)
+    for fn in fns
+        for s in 1:9
+            println(s)
+            data = joinpath(path, "data-$(s)-300.npy") |> npzread |> CuArray
+            cf = fn(data; periodic = true)[D.PlaneXY()]
+            npzwrite(joinpath(path, "data-$(s)-300-$(fn).npy"), cf)
+        end
+    end
+end
+
+end

### 2024-04-23 data/error/compare.jl

@@ -1,0 +1,53 @@
+module Shit
+import CorrelationFunctions.Directional as D
+import CorrelationFunctions.Utilities as U
+using FileIO
+using Images
+using NPZ
+
+#const sides = 100:200:1200
+#const fns = [D.s3, D.c3]
+
+const sides = 700:200:1200
+const fns = [D.surf3]
+
+function foo!()
+    for side in sides
+        for s in 1:9
+            datajulia = load("julia-lin/data-$(s)-$(side).tga") .|> Gray .|> Float64 .|> round
+            datalisp = load("lisp/data-$(s)-$(side).tga")  .|> Gray .|> Float64
+
+            for fn in fns
+                fnlisp  = fn(datalisp;  periodic = true, filter = U.ConvKernel(7))[D.PlaneXY()]
+                fnjulia = fn(datajulia; periodic = true, filter = U.ConvKernel(7))[D.PlaneXY()]
+                err = @. abs(fnlisp - fnjulia) / fnlisp
+                npzwrite("result-rounded/$(fn)-$(s)-$(side).npy", err)
+            end
+        end
+    end
+end
+
+function bar!()
+    map(sides) do side
+        datalisp  = load("julia/data-0-$(side).tga") .|> Gray |> BitArray
+        U.lowfreq_energy_ratio(datalisp)
+    end
+end
+
+function baz!()
+    for side in sides
+        perjl = map(1:9) do s
+            data = load("julia-lin/data-$(s)-$(side).tga") .|> Gray .|> Float64 .|> round
+            sum(U.extract_edges(data, U.ConvKernel(7), U.Torus()))
+        end
+
+        perlisp = map(1:9) do s
+            data = load("lisp/data-$(s)-$(side).tga") .|> Gray .|> Float64
+            sum(U.extract_edges(data, U.ConvKernel(7), U.Torus()))
+        end
+
+        npzwrite("per/$(side).npy", hcat(perjl, perlisp))
+    end
+end
+
+end

### 2024-04-23 data/error/plot.py

@@ -1,0 +1,34 @@
+#!/usr/bin/env python
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+def err(i, n, name):
+    datal = np.load("lisp/data-%i-300-%s.npy" % (i, name))
+    dataj = np.load("julia/data-%i-300-%s.npy" % (i, name))
+    err = np.abs(datal - dataj) / datal
+    err = err[n:, n:]
+    return np.max(err)
+
+def toangle(i):
+    return np.pi/4 * i/10
+
+xs = np.arange(1,10)
+xs = toangle(xs)
+
+errs3 = np.array(list(map(lambda i: err(i, 0, "s3"), range(1, 10))))
+errsss = np.array(list(map(lambda i: err(i, 10, "surf3"), range(1, 10))))
+
+plt.figure(figsize = (10, 8), dpi = 300)
+plt.rc('font', size = 25)
+ax1 = plt.gca()
+ax2 = ax1.twinx()
+p1, = ax1.plot(xs, errsss, 'b.-', label = r'$F_{sss}$')
+p2, = ax2.plot(xs, errs3, 'r.-', label = r'$S_3$')
+ax1.set_xlabel(r'$\phi$')
+ax1.set_ylabel(r'$\max (\varepsilon)$, $F_{sss}$')
+ax2.set_ylabel(r'$\max (\varepsilon)$, $S_3$')
+ax1.ticklabel_format(axis = "y", scilimits = (0, 0), useMathText = True)
+ax2.ticklabel_format(axis = "y", scilimits = (0, 0), useMathText = True)
+ax1.legend(handles = [p1, p2])
+plt.savefig('../../images/roterror-s3.png')

### 2024-04-23 data/error/rotate.jl

@@ -1,0 +1,20 @@
+module Shit
+import CorrelationFunctions.Utilities as U
+using NPZ
+using StaticArrays
+
+const sides = [300]
+
+function foo!()
+    for side in sides
+        data = npzread("lisp/data-0-$(side).npy")
+        for s in 1:9
+            angle = s/10 * π/4
+            rot = U.make_rotation(SVector(0, 0, 1), angle)
+            datarot = U.rotate_array(data, rot, U.Torus())
+            npzwrite("julia/data-$(s)-$(side).npy", datarot)
+        end
+    end
+end
+
+end

### 2024-04-23 paper.tex
Renaming

@@
   \State $A''_n \gets \mathfrak{S}_{x_2}(A_n)$
-  \State $T \gets A_n \cdot A'_n \cdot A''_n$
-  \State \textbf{return} $Sum(T) / Norm(A, x_1, x_2)$
+  \State $Tmp \gets A_n \cdot A'_n \cdot A''_n$
+  \State \textbf{return} $Sum(Tmp) / Norm(A, x_1, x_2)$
   \EndProcedure
@@
   \State $A'_{(void)} \gets \mathfrak{S}_{x_2}(A_{(void)})$
-  \State $T \gets A_n \cdot A'_n \cdot A'_{(void)}$
-  \State \textbf{return} $Sum(T) / Norm(A, x_1, x_2)$
+  \State $Tmp \gets A_n \cdot A'_n \cdot A'_{(void)}$
+  \State \textbf{return} $Sum(Tmp) / Norm(A, x_1, x_2)$
   \EndProcedure
@@
   \State $A''_{(void)} \gets \mathfrak{S}_{x_2}(A_{(void)})$
-  \State $T \gets A_n \cdot A'_{(void)} \cdot A''_{(void)}$
-  \State \textbf{return} $Sum(T) / Norm(A, x_1, x_2)$
+  \State $Tmp \gets A_n \cdot A'_{(void)} \cdot A''_{(void)}$
+  \State \textbf{return} $Sum(Tmp) / Norm(A, x_1, x_2)$
   \EndProcedure
@@
   \State $C''_n \gets \mathfrak{S}_{x_2}(C_n)$
-  \State $T \gets C_n \odot C'_n \odot C''_n$
-  \State \textbf{return} $Sum(T) / Norm(A, x_1, x_2)$
+  \State $Tmp \gets C_n \odot C'_n \odot C''_n$
+  \State \textbf{return} $Sum(Tmp) / Norm(A, x_1, x_2)$
   \EndProcedure
@@
 To test $F_{sss}$ function we use a recently developed approach which computes
-that function for sets defined by inequality $f(x) \le T$, $x \in \mathbb{R}^3$
+that function for sets defined by inequality $f(x) \le U$, $x \in \mathbb{R}^3$
 with help of automatic differentiation \cite{postnicov20232}. We choose $f$ as:
@@
 \end{equation}
-and parameters $a = 10$, $b = 0.45$, $T = 10^{-2}$, so inequation
-$f(x, y, z) \le T$ gives us a dumbbell-like object (\cref{fig:sss-dumbbell}).
+and parameters $a = 10$, $b = 0.45$, $U = 10^{-2}$, so inequation
+$f(x, y, z) \le U$ gives us a dumbbell-like object (\cref{fig:sss-dumbbell}).
 
@@
 $300 \times 300 \times 300$ sample of value noise \cref{fig:roterror-noise}
-which is defined as $f(x, y, z) > T$ where $f$ is a value noise function and $T$
+which is defined as $f(x, y, z) > U$ where $f$ is a value noise function and $U$
 is a threshold. We produce images of the noise rotated around $Z$ axis by $\phi$
-radians by discretizing an inequation $f(p(x'), p(y'), p(z')) > T$ where
+radians by discretizing an inequation $f(p(x'), p(y'), p(z')) > U$ where
 \begin{equation*}

### 2024-04-24 paper.tex
Two cases for teh error of rotation

@@
 lies closely to the interface between phases and this volume is the only volume
-affected by the rotation.
-
-To estimate the error introduced by rotation, consider a
-$300 \times 300 \times 300$ sample of value noise \cref{fig:roterror-noise}
-which is defined as $f(x, y, z) > U$ where $f$ is a value noise function and $U$
-is a threshold. We produce images of the noise rotated around $Z$ axis by $\phi$
-radians by discretizing an inequation $f(p(x'), p(y'), p(z')) > U$ where
+affected by rotation.
+
+To estimate the error introduced by rotation, consider a two-phase medium
+\cref{fig:roterror-noise} whose void phase is defined by an inequality
+$f(x, y, z) > U$ where $f$ is a value noise function and $U$ is a threshold. We
+produce images of the noise rotated around $Z$ axis by $\phi$ radians by
+discretizing an inequation $f(p(x'), p(y'), p(z')) > U$ where
 \begin{equation*}
@@
 \end{equation*}
-Therefore we assume the noise to be periodic with the period equal to
-$2$ and the interface between phases is continuous. Discretizing for different
-values of $\phi \in [0, \pi/4]$ we obtain the first dataset which contains the
-best possible discretization of the rotated noise.
+Therefore we assume the noise to be periodic with the period equal to $2$ and
+the interface between phases is continuous. Discretizing this noise for
+different values of $\phi \in [0, \pi/4]$ with two different resolutions we
+obtain the first dataset which contains the best possible discretization of the
+rotated noise at those resolutions. For this study we have produced images with
+dimensionality $300 \times 300 \times 300$ and $600 \times 600 \times 600$
+voxels (i.e. the second resolution is twice as much as the first).
 
 The second dataset is constructed by discretizing the noise with $\phi = 0$ and
-then rotating the discretized image using nearest-neighbor interpolation.
+then rotating the discretized image using nearest-neighbor interpolation. This
+procedure is done for the same two dimensionalities as in the first dataset.
 
 We compute $S_3$ and $F_{sss}$ functions in periodic mode for the both datasets
-and calculate pointwisely a relative error introduced by the rotation as
+and calculate pointwisely a relative error introduced by rotation as
 \begin{equation}
@@
 where $F_1$ is a correlation function for a sample from the first dataset and
-$F_2$ is a correlation function for a sample from the second dataset. The we
-calculate the maximal relative error for each $\phi$ as the maximum of all
-pointwise errors for a given rotation angle.
+$F_2$ is a correlation function for a sample from the second dataset for the
+same combination of a rotation angle $\phi$ and dimensionality $D$. Then we
+calculate the maximal relative error as the maximum of all pointwise errors for
+a given pair $(\phi, D)$.
 
 Plots of maximal relative errors for functions $S_3$ and $F_{sss}$ are on
-\cref{fig:roterror-error}. For the surface-surface-surface function we omit
-values $F_{sss}(s_1, s_2)$ if either of its arguments is less than 10 voxels
-because this function is undefined for either $s_1$ or $s_2$ being equal to zero
-and our edge detection filter gives at least 7 voxel transition zone where the
-correlation function is affected by this indeterminacy. The maximal error for
-all $\phi$'s are 0.6\% for $S_3$ and 4.4\% for $F_{sss}$.
+\cref{fig:roterror-error}. When calculating the error of the
+surface-surface-surface function we omit values $F_{sss}(s_1, s_2)$ if either of
+its arguments is less than 10 voxels because this function is undefined for
+either $s_1$ or $s_2$ being equal to zero and our edge detection filter gives at
+least 7 voxel transition zone where the correlation function is affected by this
+indeterminacy. The maximal error for all $\phi$'s are 0.6\% for $S_3$ and 5.0\%
+for $F_{sss}$ for dimensionality $300 \times 300 \times 300$ and 0.3\% for $S_3$
+and 4.5\% for $F_{sss}$ for dimensionality $600 \times 600 \times 600$.
 

### 2024-04-24 data/error/calculate.jl

@@ -9,10 +9,12 @@ const fns = [D.surf3, D.s3]
 function foo(path)
     for fn in fns
         for s in 1:9
-            println(s)
-            data = joinpath(path, "data-$(s)-300.npy") |> npzread |> CuArray
-            cf = fn(data; periodic = true)[D.PlaneXY()]
-            npzwrite(joinpath(path, "data-$(s)-300-$(fn).npy"), cf)
+            for side in [300, 600]
+                println(side)
+                data = joinpath(path, "data-$(s)-$(side).npy") |> npzread |> CuArray
+                cf = fn(data; periodic = true)[D.PlaneXY()]
+                npzwrite(joinpath(path, "data-$(s)-$(side)-$(fn).npy"), cf)
+            end
         end
     end
 end

### 2024-04-24 data/error/plot.py

@@ -3,9 +3,9 @@
 import numpy as np
 import matplotlib.pyplot as plt
 
-def err(i, n, name):
-    datal = np.load("lisp/data-%i-300-%s.npy" % (i, name))
-    dataj = np.load("julia/data-%i-300-%s.npy" % (i, name))
+def err(i, n, side, name):
+    datal = np.load("lisp/data-%i-%i-%s.npy" % (i, side, name))
+    dataj = np.load("julia/data-%i-%i-%s.npy" % (i, side, name))
     err = np.abs(datal - dataj) / datal
     err = err[n:, n:]
     return np.max(err)
@@ -16,19 +16,24 @@ def toangle(i):
 xs = np.arange(1,10)
 xs = toangle(xs)
 
-errs3 = np.array(list(map(lambda i: err(i, 0, "s3"), range(1, 10))))
-errsss = np.array(list(map(lambda i: err(i, 10, "surf3"), range(1, 10))))
+errs3_300 = np.array(list(map(lambda i: err(i, 0, 300, "s3"), range(1, 10))))
+errsss_300 = np.array(list(map(lambda i: err(i, 10, 300, "surf3"), range(1, 10))))
+errs3_600 = np.array(list(map(lambda i: err(i, 0, 600, "s3"), range(1, 10))))
+errsss_600 = np.array(list(map(lambda i: err(i, 10, 600, "surf3"), range(1, 10))))
 
-plt.figure(figsize = (10, 8), dpi = 300)
-plt.rc('font', size = 25)
+#plt.figure(figsize = (10, 8), dpi = 300)
+#plt.rc('font', size = 25)
 ax1 = plt.gca()
 ax2 = ax1.twinx()
-p1, = ax1.plot(xs, errsss, 'b.-', label = r'$F_{sss}$')
-p2, = ax2.plot(xs, errs3, 'r.-', label = r'$S_3$')
+p1, = ax1.plot(xs, errsss_300, 'b.-', label = r'$F_{sss}, 300 \times 300 \times 300$')
+p2, = ax1.plot(xs, errsss_600, 'g.-', label = r'$F_{sss}, 600 \times 600 \times 600$')
+p3, = ax2.plot(xs, errs3_300, 'r.-', label = r'$S_3, 300 \times 300 \times 300$')
+p4, = ax2.plot(xs, errs3_600, 'm.-', label = r'$S_3, 600 \times 600 \times 600$')
[…]

### 2024-04-24 data/error/rotate.jl

@@ -3,7 +3,7 @@ import CorrelationFunctions.Utilities as U
 using NPZ
 using StaticArrays
 
-const sides = [300]
+const sides = [300, 600]
 
 function foo!()
     for side in sides

### 2024-04-24 paper.tex
Minor fixes

@@
 where $I_n^k$ is an indicator function for $k$-th cluster of $A_n$ and $K$
-is a total number of clusters. A cluster is a subset of $A_n$ so that any two
+is a total number of clusters. A cluster is a subset of $A_n$ such that any two
 points in this subset can be connected with a curve belonging to that subset.
@@
   F_{sss}^n(x_1, x_2) &= \langle M_n(x) M_n(x + x_1) M_n(x + x_2) \rangle \\
-  F_{ssv}^n(x_1, x_2) &= \langle M_n(x) M_{(void)}(x + x_1) I_{(void)}(x + x_2) \rangle \\
+  F_{ssv}^n(x_1, x_2) &= \langle M_n(x) M_n(x + x_1) I_{(void)}(x + x_2) \rangle \\
   F_{svv}^n(x_1, x_2) &= \langle M_n(x) I_{(void)}(x + x_1) I_{(void)}(x + x_2) \rangle
@@
 volume, surface and length, respectively (e.g., can be measured in $\mu m^{-3}$,
-$\mu m^{-2}$ and $\mu m^{-1}$ or other convenient dimensionless units depending
-on the problem to be solved).  These functions describe the interface of the
-subset $A_n$ and its spatial configuration with respect to $A_v$.
+$\mu m^{-2}$ and $\mu m^{-1}$ or other convenient units depending on the problem
+to be solved).  These functions describe the interface of the subset $A_n$ and
+its spatial configuration with respect to $A_{(void)}$.
 
@@
   \begin{array}{ll}
-    1 & \quad x = y \\
+    1 & \quad x = y \ne L_{(void)} \\
     0 & \quad \text{otherwise}.
@@
 \end{equation}
+where $L_{(void)}$ is a label of the void phase.
 
@@
   \hfill
-  \subfigure[A plot of $S_3(0, r)$ computed with our algorithm and theoretical
+  \subfigure[A plot of $S_3(0, r)$ computed with our algorithm and a theoretical
     formula.]{

### 2024-04-24 paper.tex
Replace ϕ with θ

@@
 $f(x, y, z) > U$ where $f$ is a value noise function and $U$ is a threshold. We
-produce images of the noise rotated around $Z$ axis by $\phi$ radians by
+produce images of the noise rotated around $Z$ axis by $\theta$ radians by
 discretizing an inequation $f(p(x'), p(y'), p(z')) > U$ where
@@
   \begin{aligned}
-    x' &= x \cos \phi + y \sin \phi \\
-    y' &= y \cos \phi - x \sin \phi \\
+    x' &= x \cos \theta + y \sin \theta \\
+    y' &= y \cos \theta - x \sin \theta \\
     z' &= z
@@
 the interface between phases is continuous. Discretizing this noise for
-different values of $\phi \in [0, \pi/4]$ with two different resolutions we
+different values of $\theta \in [0, \pi/4]$ with two different resolutions we
 obtain the first dataset which contains the best possible discretization of the
@@
 
-The second dataset is constructed by discretizing the noise with $\phi = 0$ and
+The second dataset is constructed by discretizing the noise with $\theta = 0$ and
 then rotating the discretized image using nearest-neighbor interpolation. This
@@
 $F_2$ is a correlation function for a sample from the second dataset for the
-same combination of a rotation angle $\phi$ and dimensionality $D$. Then we
+same combination of a rotation angle $\theta$ and dimensionality $D$. Then we
 calculate the maximal relative error as the maximum of all pointwise errors for
-a given pair $(\phi, D)$.
+a given pair $(\theta, D)$.
 
@@
 least 7 voxel transition zone where the correlation function is affected by this
-indeterminacy. The maximal error for all $\phi$'s are 0.6\% for $S_3$ and 5.0\%
+indeterminacy. The maximal error for all $\theta$'s are 0.6\% for $S_3$ and 5.0\%
 for $F_{sss}$ for dimensionality $300 \times 300 \times 300$ and 0.3\% for $S_3$

### 2024-04-24 data/error/plot.py

@@ -21,19 +21,18 @@ errsss_300 = np.array(list(map(lambda i: err(i, 10, 300, "surf3"), range(1, 10))
 errs3_600 = np.array(list(map(lambda i: err(i, 0, 600, "s3"), range(1, 10))))
 errsss_600 = np.array(list(map(lambda i: err(i, 10, 600, "surf3"), range(1, 10))))
 
-#plt.figure(figsize = (10, 8), dpi = 300)
-#plt.rc('font', size = 25)
+plt.figure(figsize = (10, 8), dpi = 300)
+plt.rc('font', size = 25)
 ax1 = plt.gca()
 ax2 = ax1.twinx()
 p1, = ax1.plot(xs, errsss_300, 'b.-', label = r'$F_{sss}, 300 \times 300 \times 300$')
 p2, = ax1.plot(xs, errsss_600, 'g.-', label = r'$F_{sss}, 600 \times 600 \times 600$')
 p3, = ax2.plot(xs, errs3_300, 'r.-', label = r'$S_3, 300 \times 300 \times 300$')
 p4, = ax2.plot(xs, errs3_600, 'm.-', label = r'$S_3, 600 \times 600 \times 600$')
-ax1.set_xlabel(r'$\phi$')
+ax1.set_xlabel(r'$\theta$')
 ax1.set_ylabel(r'$\max (\varepsilon)$, $F_{sss}$')
 ax2.set_ylabel(r'$\max (\varepsilon)$, $S_3$')
 ax1.ticklabel_format(axis = "y", scilimits = (0, 0), useMathText = True)
 ax2.ticklabel_format(axis = "y", scilimits = (0, 0), useMathText = True)
 ax1.legend(handles = [p1, p2, p3, p4])
-#plt.savefig('../../images/roterror-s3.png')
-plt.show()
+plt.savefig('../../images/roterror.png')

### 2024-04-24 paper.tex
Replace C_{0.5} with Q_{0.5}

@@
 to work correctly. A criterion for ``goodness'' of an image can be expressed
-with $C_{\alpha}$ parameter \cite{samarin2023robust}. Let $\alpha \in [0, 1]$
+with $Q_\alpha$ parameter \cite{samarin2023robust}. Let $\alpha \in [0, 1]$
 and $f(x)$ be (band-limited) input image ($x \in \mathbb{R}^2$ or
-$\mathbb{R}^3$). We define $C_\alpha$ as follows:
+$\mathbb{R}^3$). We define $Q_\alpha$ as follows:
 \begin{equation}
@@
     f_0(x) &= f(x) - \langle f(x) \rangle \\
-    C_\alpha &= \frac{\int_{-\alpha\omega}^{\alpha\omega} |\hat{f_0}(z)|^2
+    Q_\alpha &= \frac{\int_{-\alpha\omega}^{\alpha\omega} |\hat{f_0}(z)|^2
       dz}{\int_{-\omega}^{\omega} |\hat{f_0}(z)|^2 dz}
@@
 frequency which depends only on resolution of the image. If a criterion
-$C_{0.5} > 0.97$ holds then the image is suitable for application of
+$Q_{0.5} > 0.97$ holds then the image is suitable for application of
 aforementioned algorithms for calculation of surface functions, otherwise
@@
     Sample name & Image type & Dimensions (pixels/voxels) & Image resolution ($\mu m$)
-    & $C_{0.5}$ \\
+    & $Q_{0.5}$ \\
     \hline
@@
 samples. Note that we compute surface correlation functions only for those
-samples for which the criterion $C_{0.5} > 0.97$ holds (the two sandstones and
+samples for which the criterion $Q_{0.5} > 0.97$ holds (the two sandstones and
 the soil) \cite{samarin2023robust}. Images of the samples are presented on
@@
 verification results in \cref{sec:results}, it seems that it would be much
-faster to discretize the sphere packing with appropriate $C_{0.5} > 0.97$ and to
+faster to discretize the sphere packing with appropriate $Q_{0.5} > 0.97$ and to
 utilize our package to assess correlation functions within tens of minutes

### 2024-04-24 paper.tex
Replace C with Σ

@@
 To detect the direction of anisotropy we use an $N \times N$ (where $N$ is
-dimensionality of the sample) covariance matrix for coordinates of points in the
-phase of interest:
-\begin{equation}
-  C_{ij} = \sum_{x \in \left\{
+dimensionality of the sample) covariance matrix
+$\Sigma = \left\{ \sigma_{ij} \right\}$ for coordinates of points in the phase of
+interest:
+\begin{equation}
+  \sigma_{ij} = \sum_{x \in \left\{
     \begin{array}{l}
@@
 \end{equation}
-and decompose $C$ as $T \Lambda T^{-1}$ where $T$ is a unitary matrix and
+and decompose $\Sigma$ as $T \Lambda T^{-1}$ where $T$ is a unitary matrix and
 $\Lambda$ is diagonal. $T$ can always be made so that it defines a rotation (by

### 2024-04-25 paper.tex
Fix a typo
Add a citation

@@
 the correlation function \cref{fig:aniso}. In our implementation we use rotation
-with nearest-neighbor interpolcation which affects quality of computations as
+with nearest-neighbor interpolation which affects quality of computations as
 discussed in \cref{sec:rotqua}.
@@
 \cref{fig:roterror-noise} whose void phase is defined by an inequality
-$f(x, y, z) > U$ where $f$ is a value noise function and $U$ is a threshold. We
-produce images of the noise rotated around $Z$ axis by $\theta$ radians by
-discretizing an inequation $f(p(x'), p(y'), p(z')) > U$ where
+$f(x, y, z) > U$ where $f$ is a value noise function
+\cite[Section IV.B]{samarin2023robust} and $U$ is a threshold. We produce images
+of the noise rotated around $Z$ axis by $\theta$ radians by discretizing an
+inequation $f(p(x'), p(y'), p(z')) > U$ where
 \begin{equation*}

### 2024-04-27 paper.tex
revision some chages part1

@@
 are believed to possess larger information content and provide more information
-about studies structures. In this paper, we have developed algorithms and code
+about studied structures. In this paper, we have developed algorithms and code
 to compute $S_3, C_3, F_{sss}, F_{ssv}$ and $F_{svv}$ with a right-angle
@@
 patterns. Moreover, it allows to easily implement computations of directional
-3-point CFs. The execution times for the same number of sample are orders of
-magnitude lower than existing published counterparts. We showed that the volume
+3-point CFs. The execution times for the same number of samples are orders of
+magnitude lower than in existing published counterparts. We showed that the volume
 of data produced get unwieldy very easily, especially if computations are
@@
 part of open source package \code{CorrelationFunctions.jl} [Postnicov et al.,
-  2024, Comp.Phys.Commun(accepted)]. As described in this paper, 3-point CFs
+  2024, Comp.Phys.Commun., 299, 109134]. As described in this paper, 3-point CFs
 computations can be immediately applied in a great number of research
@@
     \cite{takada2003three,hopkins2013stars,shivashankar2015felix,saadatfar2017pore,
-      portillo2018developing,KarsaninaEJSS,PNM_Morse,khlyupin2023molecular},
+      portillo2018developing,cheng2022data,KarsaninaEJSS,PNM_Morse,khlyupin2023molecular},
     which may include temporal dynamics or surface evolution
@@
     between field-of-view and imaging resolution
-    \cite{SciRep1,Geoderma2018,chen2020super,karimpouli2022}.
+    \cite{SciRep1,Geoderma2018,chen2020super,yan2023multiscale,karimpouli2022,yan2024modeling}.
 \end{enumerate}
@@
 are more involved and, thus, require much more computational resources to
-assess. It has been shown that the amount of additional information content with
-each increase in number of points $n$ decreases \cite{yao1993high,Gommes2}. The
+assess. It has been shown that the amount of additional information content decreases with
+each increase in number of points $n$ \cite{yao1993high,Gommes2}. The
 trade-off between additional information and computational burden is still not

### 2024-04-27 paper.tex
revision some chages part1

@@
 image's resolution can be improved with the help of interpolation prior to
-computations \cite{samarin2023robust}.
+computations \cite{Samarin}.
 
@@
 \cref{fig:roterror-noise} whose void phase is defined by an inequality
-$f(x, y, z) > U$ where $f$ is a value noise function
-\cite[Section IV.B]{samarin2023robust} and $U$ is a threshold. We produce images
-of the noise rotated around $Z$ axis by $\theta$ radians by discretizing an
-inequation $f(p(x'), p(y'), p(z')) > U$ where
+$f(x, y, z) > U$ where $f$ is a value noise function and $U$ is a threshold. We
+produce images of the noise rotated around $Z$ axis by $\theta$ radians by
+discretizing an inequation $f(p(x'), p(y'), p(z')) > U$ where
 \begin{equation*}

### 2024-05-08 paper.tex
Something incomprehensible about rotations

--- 2024-04-27 paper.tex
@@
 
-Our implementation fixes $x_1$ and $x_2$ to be parallel to one of the axes $X$,
-$Y$ or $Z$ with restriction $x_1 \perp x_2$ (\cref{fig:pattern})
-\cite{dimitrakopoulos2010high}. Thus, the output has dimensions $D_1 \times D_2$
-where $D_1$ and $D_2$ are dimensions of the input array along selected
-axes. Note that shift operators with such $x_1$ and $x_2$ represent a 3-point
-function computed within a 3D domain, but along a predefined direction (see
-below).
-\begin{figure}[ht]
-  \centering
-  \includegraphics[width=0.5\linewidth]{images/pattern.png}
-  \caption[]{The pattern used for calculation of $S_3$ function in our
-    implementation.}
-  \label{fig:pattern}
-\end{figure}
-
 Algorithms for three-point surface functions are the same as for $S_3$,
@@
 
+\subsection{Open-source implementation}
+The described algorithms are implemented in our \code{CorrelationFunctions.jl}
+package written in Julia and have the same interface:
+\begin{verbatim}
+corrfn(input, phase, ps1, ps2)
+\end{verbatim}
+where \code{corrfn} stands for \code{s3} ($S_3$), \code{c3} ($C_3$),
+\code{surf3} ($F_{sss}$) etc., \code{input} is the input array, \code{phase} is
+a phase of interest and \code{ps1} and \code{ps2} are arrays of points in which
+correlation function is calculated. Firstly, \code{corrfn} does all necessary
+preparations for the input array (e.g. edge extraction or connected component
+labeling) and then calculates the correlation function for each pair of
+arguments from \code{ps1} and \code{ps2}.
+
+Our implementation provides a predefined right triangle pattern where arguments
+of a correlation function $x_1$ and $x_2$ are fixed to be parallel to one of the
+axes $X$, $Y$ or $Z$ with restriction $x_1 \perp x_2$ (\cref{fig:pattern})
+\cite{dimitrakopoulos2010high}. The output has dimensions $D_1 \times D_2$ where
+$D_1$ and $D_2$ are dimensions of the input array along selected axes. Note that
+shift operators with such $x_1$ and $x_2$ represent a 3-point function computed
+within a 3D domain, but along a predefined direction (see below).
+\begin{figure}[ht]
+  \centering
+  \includegraphics[width=0.5\linewidth]{images/pattern.png}
+  \caption[]{The pattern used for calculation of $S_3$ function in our
+    implementation.}
+  \label{fig:pattern}
+\end{figure}
+
+If it is desired, a user can use a custom pattern more appropriate to the
+situation.
+
 \subsection{Analysis of anisotropic media}
@@
 multiplication of one of the columns by $-1$ if needed, so that
-$\det T = 1$). Application of this rotation to the sample makes the direction of
-anisotropy parallel to one of the axes, so anisotropy can be better represented in
-the correlation function \cref{fig:aniso}. In our implementation we use rotation
-with nearest-neighbor interpolation which affects quality of computations as
-discussed in \cref{sec:rotqua}.
+$\det T = 1$). Application of this rotation to the sample (or its inverse to the
+pattern) makes the direction of anisotropy coaligned with the pattern, so
+anisotropy can be better represented in the correlation function. For the sake
+of visual clarity in this study we choose to rotate the image instead of the
+pattern \cref{fig:aniso}. This has such consequences as reduced accuracy of
+computed functions due to necessity to interpolate the image during
+rotation. Although we show in \cref{sec:rotqua} that even nearest-neighbor
+interpolation results only in insignificant loss of quality. Rotation of the
+pattern has same drawbacks related to interpolation of the sample which are most
+noticeable at small correlation lengths. The both methods (rotation of the
+sample or the pattern) produce nearly equivalent result if the sample is
+homogeneous and an average pore size is much less than the sample's size (see
+\cref{sec:rotrot})
 \begin{figure*}[!htp]
@@
 
+\section{Difference between rotating the input image or the sampling pattern}
+\label{sec:rotrot}
+Let's take the noise from \cref{sec:rotqua} with lesser sizes of pores and
+calculate $S_3$ function for it, preliminarily rotating the noise around Z-axis
+counter-clockwise using nearest-neighbor interpolation (the first case) or
+rotating the pattern around the same axis clock-wise (the second case). Then we
+compute a difference between the results point-wise using a formula
+\begin{equation}
+  \varepsilon = 2\frac{|S_3^{(1)} - S_3^{(2)}|}{S_3^{(1)} + S_3^{(2)}}
+  \label{eq:reldiff}
+\end{equation}
+The average of point-wise differences is at maximum for the angle of rotation
+$\theta = \frac{\pi}{4}$ and equals to 0.8\%. The maximal difference is about
+10\% for very small correlation length (about 2-3 pixels). These two methods of
+rotating give minimal difference if applied to a homogeneous medium with an
+average pore size much less than a size of the input (\cref{fig:rotdiff}).
+\begin{figure*}[tp]
+  \centering
+  \subfigure[A sample of value noise with small pores (compared to a size of the
+    sample, $300 \times 300 \times 300$)]{
+    \includegraphics[width=0.4\linewidth]{images/noise2.png}
+    \label{fig:rotdiff-noise}}
+  \hfill
+  \subfigure[Difference between two methods of rotation]{
+    \includegraphics[width=0.4\linewidth]{images/rotdiff.png}
+    \label{fig:rotdiff-error}}
+  \caption[]{A plot depicting difference between two rotation methods: rotation
+    of the sample and of the pattern. Dependency of an average point-wise
+    difference \cref{eq:reldiff} from a rotation angle is shown. The rotation is
+    performed around $Z$ axis counter-clockwise (sample) and clockwise (pattern).}
+  \label{fig:rotdiff}
+\end{figure*}
+
 \bibliography{paper}

### 2024-05-08 paper.tex
Superscript
Highlight a sentence which is hard to understand

@@
 
+When a phase of interest is clear from the context or irrelavant a superscript
+can be omitted from mathematical notation of correlation functions.
+
 \subsection{Computational algorithms}
@@
 \cite{dimitrakopoulos2010high}. The output has dimensions $D_1 \times D_2$ where
-$D_1$ and $D_2$ are dimensions of the input array along selected axes. Note that
-shift operators with such $x_1$ and $x_2$ represent a 3-point function computed
-within a 3D domain, but along a predefined direction (see below).
+$D_1$ and $D_2$ are dimensions of the input array along selected axes.
+\highlight{I CANNOT UNDESTAND THIS SENTENCE: Note that shift operators with such
+  $x_1$ and $x_2$ represent a 3-point function computed within a 3D domain, but
+  along a predefined direction (see below).}
 \begin{figure}[ht]

### 2024-05-08 paper.tex
Parens
Deal with rotations

@@
 of visual clarity in this study we choose to rotate the image instead of the
-pattern \cref{fig:aniso}. This has such consequences as reduced accuracy of
+pattern (\cref{fig:aniso}). This has such consequences as reduced accuracy of
 computed functions due to necessity to interpolate the image during
@@
 When a sample is known to be isotropic, the correlation function may be
-calculated multiple times, each time applying a random rotation of the sample,
-and then averaged across rotations to gather more statistics. This process is
-illustrated on \cref{fig:workflow}. This way we obtain similar results to
-sampling procedures used in \cite{berryman1988,SMITH1988176,malmir2018}.
+calculated multiple times, each time applying a random rotation to the sample or
+the pattern, and then averaged across rotations to gather more statistics. This
+process is illustrated on \cref{fig:workflow}. This way we obtain similar
+results to sampling procedures used in
+\cite{berryman1988,SMITH1988176,malmir2018}.
 
@@
 correlation functions averaged in all directions (by randomly rotating the
-sample), along predefined number of directions (e.g., orthogonal and diagonal by
-rotation in these directions) or along the direction of major anisotropy (that
-can be determined using \code{$detect\_anisotropy$} function).  Full correlation
-map for 3-point functions is impractical due its huge size and is not
-implemented.
+sample or the pattern), along predefined number of directions (e.g., orthogonal
+and diagonal by rotation in these directions) or along the direction of major
+anisotropy (that can be determined using \code{$detect\_anisotropy$} function).
+Full correlation map for 3-point functions is impractical due its huge size and
+is not implemented.
 
@@
 between catheti of the sampling pattern is fixed to be $\theta = \frac{\pi}{2}$,
-but can be mitigated by rotation of the pattern as a whole by an equivalent
-operation of rotation of a sample. These rotations can be random as in the
-Malmir et al. algorithm, or it can be a single rotation to align catheti of the
-sampling triangle with the direction of anisotropy (\cref{fig:aniso}). The
-latter allows computing directional 3-point correlation functions for
-anisotropic structures similar to 2-point counterparts
-\cite{10.1063/1.4867611,EPL1}.
+but it can be mitigated by choosing a random pattern or rotating the
+pattern. The rotations can be random as in the Malmir et al. algorithm, or it
+can be a single rotation to align catheti of the sampling triangle with the
+direction of anisotropy (\cref{fig:aniso}). The latter allows computing
+directional 3-point correlation functions for anisotropic structures similar to
+2-point counterparts \cite{10.1063/1.4867611,EPL1}.
 

### 2024-05-08 paper.tex
Remove erroneous information about speedup

@@
 GPU). For $n=3$ we have developed code in Julia language to compute $S_3, C_3,
-F_{sss}, F_{ssv}$ and $F_{svv}$ with a right-angle triangle pattern. This
-pattern is much easier to vectorize and parallelize compared to previously used
-random triangle or spider-web sampling patterns. Moreover, it allows to easily
-implement computations of directional 3-point CFs. The execution times for the
-same number of sample are orders of magnitude lower than existing published
-counterparts. We showed that the volume of data produced get unwieldy very
-easily, especially if computations are performed in frequency domain. For these
-reasons until information content of different sets of correlation functions
-with different "n-pointness" is not known, it is seemingly no much reason to
-increase the number of points. Nonetheless, developed algorithms and code are
-universal enough to be easily extendable to any $n$ (with increasing
-computational and RAM burden). All results are available as part of open source
-package \code{CorrelationFunctions.jl}, developed by our group and freely
-available to the public with numerous Jupiter notebooks showing examples of
-applications to assess 3-point correlation functions for 2D and 3D images.
+F_{sss}, F_{ssv}$ and $F_{svv}$ in an arbitrary set of points. We also provide a
+function which generates a right-angle triangle pattern. Computations are easily
+vectorized and utilize the power of modern CPU and GPU architectures. The
+execution times for the same number of sample are orders of magnitude lower than
+existing published counterparts. We showed that the volume of data produced get
+unwieldy very easily, especially if computations are performed in frequency
+domain. For these reasons until information content of different sets of
+correlation functions with different "n-pointness" is not known, it is seemingly
+no much reason to increase the number of points. Nonetheless, developed
+algorithms and code are universal enough to be easily extendable to any $n$
+(with increasing computational and RAM burden). All results are available as
+part of open source package \code{CorrelationFunctions.jl}, developed by our
+group and freely available to the public with numerous Jupiter notebooks showing
+examples of applications to assess 3-point correlation functions for 2D and 3D
+images.
 

### 2024-05-08 paper.tex
until the content is NOT known -> until the content is known

@@
 domain. For these reasons until information content of different sets of
-correlation functions with different "n-pointness" is not known, it is seemingly
-no much reason to increase the number of points. Nonetheless, developed
-algorithms and code are universal enough to be easily extendable to any $n$
-(with increasing computational and RAM burden). All results are available as
-part of open source package \code{CorrelationFunctions.jl}, developed by our
-group and freely available to the public with numerous Jupiter notebooks showing
-examples of applications to assess 3-point correlation functions for 2D and 3D
-images.
+correlation functions with different "n-pointness" is known, it is seemingly no
+much reason to increase the number of points. Nonetheless, developed algorithms
+and code are universal enough to be easily extendable to any $n$ (with
+increasing computational and RAM burden). All results are available as part of
+open source package \code{CorrelationFunctions.jl}, developed by our group and
+freely available to the public with numerous Jupiter notebooks showing examples
+of applications to assess 3-point correlation functions for 2D and 3D images.
 

### 2024-08-29 paper.tex
web-like -> weblike, spider-web -> spiderweb

@@
 triangle pattern. This pattern is much easier to vectorize and parallelize
-compared to previously used random triangle or spider-web sampling
+compared to previously used random triangle or spiderweb sampling
 patterns. Moreover, it allows to easily implement computations of directional
@@
 correlation function at the point $(r_1, r_2, \theta)$. The second algorithm
-takes a precalculated triangle $(r_1, r_2, \theta)$ from a web-like pattern and
+takes a precalculated triangle $(r_1, r_2, \theta)$ from a weblike pattern and
 places it in the medium without rotation, only applying a random

### 2024-08-29 paper.tex
last changes before revision

--- 2024-05-08 paper.tex
@@
 
-\author{Vasily~Postnicov\textsuperscript{1}}
-\author{Marina~V.~Karsanina\textsuperscript{1}}
+\author{Vasily~Postnicov\textsuperscript{1,3}}
+\author{Marina~V.~Karsanina\textsuperscript{1,2}}
 \author{Aleksey~Khlyupin\textsuperscript{1,2}}
-\author{Kirill~M.~Gerke\textsuperscript{1}}
+\author{Kirill~M.~Gerke\textsuperscript{1,2}}
 \email{kg@ifz.ru}
 
-\affiliation{\textsuperscript{1}Schmidt Institute of Physics of the Earth of
+\affiliation{\textsuperscript{1}Moscow Institute of Physics and Technology,
+  Dolgoprudny, 141701, Russia}
+\affiliation{\textsuperscript{2}Schmidt Institute of Physics of the Earth of
   Russian Academy of Sciences, Moscow, 107031, Russia}
-\affiliation{\textsuperscript{2}Moscow Institute of Physics and Technology,
-  Dolgoprudny, 141701, Russia}
+\affiliation{\textsuperscript{3}Dokuchaev Soil Science Institute, Moscow, 119017, Russia}
 
@@
 about studied structures. In this paper, we have developed algorithms and code
-to compute $S_3, C_3, F_{sss}, F_{ssv}$ and $F_{svv}$ with a right-angle
-triangle pattern. This pattern is much easier to vectorize and parallelize
-compared to previously used random triangle or spider-web sampling
-patterns. Moreover, it allows to easily implement computations of directional
-3-point CFs. The execution times for the same number of samples are orders of
+to compute $S_3, C_3, F_{sss}, F_{ssv}$ and $F_{svv}$ with a right-angle and arbitrary
+triangle pattern. The former was believed to be faster to compute, but with the help of precomputed
+regular positions we achieved the same speed for arbitrary pattern. In this work we also 
+implement and demonstrate computations of directional 3-point CFs -- for this
+purpose right-triangular pattern seems to be superior due to explicit orientation and high coverage.
+Moreover, we assess the errors in CFs' evaluation due to image or pattern rotations and show that they 
+have minor effect on accuracy of computations.
+The execution times of our algorithms for the same number of samples are orders of
 magnitude lower than in existing published counterparts. We showed that the volume
@@
   \item Morphological representativity
-    \cite{capek2009,rozenbaum2014,gerke2019tensor} and spatial stationarity
-    analysis \cite{REVpaper,LavrukhinPRE};
+    \cite{capek2009,rozenbaum2014,gerke2019tensor,zubov2024search} and spatial stationarity
+    analysis \cite{REVpaper,LavrukhinPRE,zubov2024search};
   \item Stochastic reconstructions from limited amount of input data
@@
 \cite{Torquato_book}, persistence diagrams
-\cite{shivashankar2015felix,saadatfar2017pore,obayashi2018persistence}. The
+\cite{shivashankar2015felix,saadatfar2017pore,obayashi2018persistence,zubov2024search}. The
 evolution of such metrics was mainly induced by the ease of measurement and
@@
   tahmasebiPRL,Euras2012,EPL2,karsaninaPRL,jiao2007,SciRep1,Havelka,Geoderma2018}
-is based on so-called correlation functions (CFs). These functions define a
+is based on so-called correlation functions (CFs). Majority of these functions, with 
+surface functions being a notable exception \cite{samarin2023robust}, define a
 probability that some events are occurring withing the structure (with some
@@
   \item Correlation functions can be scaled \cite{karsaninaPRL} or manipulated,
-    for example, to add functions into a single one \cite{moctezuma2002};
+    for example, to add functions into a single structure \cite{moctezuma2002};
   \item As opposed to scalar metrics such as porosity, surface area or Minkowski
@@
     bounds \cite{hashin1963variational}. Other expressions based on integration
-    of higher order $S_n$ are known and were found to be close to direct
+    of higher order $S_n$ are known and were found to be closer to direct
     simulations
@@
 
-\subsection{Open-source implementation}
-The described algorithms are implemented in our \code{CorrelationFunctions.jl}
-package written in Julia and have the same interface:
+\subsection{Triangular sampling pattern}
+There are three major known sampling pattern implementations reported in the literature (\cref{fig:pattern}):
+\begin{enumerate}
+  \item Arbitrary pattern (or random) triangle is thrown into the structure (e.g., \cite{malmir2018});
+  \item Web-like predefined triangular pattern (e.g., \cite{SMITH1988176});
+  \item Right-triangular sampling pattern (e.g., \cite{dimitrakopoulos2010high}).
+\end{enumerate}
+The second case of the web-like pattern was useful at times of low computational resources and seems to be the least flexible in terms of structure coverage.
+Right-traingle as a pattern was popular due ease of implementation and potential speed gains due to vectorization.
+However, we have organized the algorithms of \code{CorrelationFunctions.jl} to be able to utilize any patterns.
+This was achieved by organizing computational functions not around a shifting pattern, but rather around precomputed points representing
+triangle's vertices -- thus making our approach under the hood using the ideas behind the web-like pattern method.
+
+This is implemented in our code by using the same interface for all computation functions to assess CFs:
 \begin{verbatim}
@@
 where \code{corrfn} stands for \code{s3} ($S_3$), \code{c3} ($C_3$),
-\code{surf3} ($F_{sss}$) etc., \code{input} is the input array, \code{phase} is
+\code{surf3} ($F_{sss}$) etc., \code{input} is the input array describing the structure, \code{phase} is
 a phase of interest and \code{ps1} and \code{ps2} are arrays of points in which
@@
 
-Our implementation provides a predefined right triangle pattern where arguments
+To compare different approaches in this work we performed calculations with right-triangular\cite{dimitrakopoulos2010high,malmir2018},
+equilateral triangle and isosceles triangle with varying angle \cite{SMITH1988176,malmir2018} patterns -- both with averaging
+over the whole structure, or computed in directions (see next two subsections below). In the first case the pattern where arguments
 of a correlation function $x_1$ and $x_2$ are fixed to be parallel to one of the
-axes $X$, $Y$ or $Z$ with restriction $x_1 \perp x_2$ (\cref{fig:pattern})
-\cite{dimitrakopoulos2010high}. The output has dimensions $D_1 \times D_2$ where
-$D_1$ and $D_2$ are dimensions of the input array along selected axes.
-\highlight{I CANNOT UNDESTAND THIS SENTENCE: Note that shift operators with such
-  $x_1$ and $x_2$ represent a 3-point function computed within a 3D domain, but
-  along a predefined direction (see below).}
-\begin{figure}[ht]
-  \centering
-  \includegraphics[width=0.5\linewidth]{images/pattern.png}
-  \caption[]{The pattern used for calculation of $S_3$ function in our
-    implementation.}
+axes $X$, $Y$ or $Z$ with restriction $x_1 \perp x_2$ (\cref{fig:pattern}, right scheme).
+Except for equilateral triangle, the output  has dimensions $D_1 \times D_2$ where $D_1$ and $D_2$ are dimensions of the input array along selected axes.
+For equilateral pattern there is a single curve (i.e.,
+similar to $S_2$ graphical representation).
+
+\begin{figure*}[ht]
+  \centering
+  \includegraphics[width=0.8\linewidth]{images/web-like.png}
+  \caption[]{Schematic representation of patterns for 3-point correlation functions evaluation:
+  arbitrary or random triangle, web-like, and right-triangular patterns. Note that real patterns are
+  more complex and are made simple for visualization, i.e., for right-triangular pattern we sample
+  all possible variations between points. Equilateral or isosceles triangles can be considered
+  as arbitrary patterns and can be either fixed in space, or rotated randomly.}
   \label{fig:pattern}
-\end{figure}
-
-If it is desired, a user can use a custom pattern more appropriate to the
-situation.
+\end{figure*}
 
@@
 When an analyzed sample is anisotropic, i.e., it is stretched or oriented along
-some specific direction, it may be beneficial to align one of the cathetus of
+some specific direction, it may be beneficial to align one of the sides (cathetus for the right-triangular pattern) of
 sampling triangle \cref{fig:pattern} with that direction. In this case the
@@
 of visual clarity in this study we choose to rotate the image instead of the
-pattern (\cref{fig:aniso}). This has such consequences as reduced accuracy of
+pattern (\cref{fig:aniso}). Any rotation can potentially reduce accuracy of
 computed functions due to necessity to interpolate the image during
-rotation. Although we show in \cref{sec:rotqua} that even nearest-neighbor
-interpolation results only in insignificant loss of quality. Rotation of the
-pattern has same drawbacks related to interpolation of the sample which are most
-noticeable at small correlation lengths. The both methods (rotation of the
-sample or the pattern) produce nearly equivalent result if the sample is
-homogeneous and an average pore size is much less than the sample's size (see
-\cref{sec:rotrot})
-\begin{figure*}[!htp]
-  \centering
-  \begin{tabular}{ccc}
-    \includegraphics[width=0.3\linewidth, frame]{images/aniso.png} &
-    \includegraphics[width=0.3\linewidth, frame]{images/aniso-rot.png} & \\
-    \includegraphics[width=0.3\linewidth]{images/aniso-s3.png} &
-    \includegraphics[width=0.3\linewidth]{images/aniso-rot-s3.png} &
-    \includegraphics[width=0.3\linewidth]{images/aniso-avg-s3.png} \\
-  \end{tabular}
-  \caption{Behaviour of our algorithm for calculation of the $S_3$ function
-    when dealing with highly anisotropic media. The pattern \cref{fig:pattern}
+rotation, and this important issue is explored later.
+\begin{figure*}[ht]
+  \centering
+  \includegraphics[width=0.8\linewidth]{images/fig_rot.png}
+  \caption{Examples of directional analysis of images with the help of $S_3$ function
+    when dealing with highly anisotropic media. The right-triangular pattern (\cref{fig:pattern}, right side)
     which we use in our algorithm is most sensitive to anisotropy which is
@@
     From top down, left to right: an original image of an anisotropic pore; a
-    rotated image of the pore, so it is elongated along the axis; $S_3$ function
+    rotated image of the pore, so it is positioned along the major axis; $S_3$ function
     for the original pore; $S_3$ function for the rotated pore with a vector
     $(0.92, -0.4)$ being a direction of elongation of the pore; $S_3$ function
-    averaged across rotations similar to the algorithm described in
+    averaged across rotations similar to previously known algorithms
     \cite{berryman1988,SMITH1988176,malmir2018}.}
@@
 anisotropy (that can be determined using \code{$detect\_anisotropy$} function).
-Full correlation map for 3-point functions is impractical due its huge size and
+Full correlation map for 3-point functions is impractical due its huge size and, thus,
 is not implemented.
@@
     \includegraphics[width=0.4\linewidth]{images/dumbbell-sss-julia.png}}
-  \caption[]{A comparison of $F_{sss}$ function calculated using our approach
+  \caption[]{A comparison of $F_{sss}$ function calculated using our algorithm
     with its precise values.}
@@
 
+\subsection{Comparison of sampling patterns}
+\label{sec:compare_patterns}
+To compare different sampling and averaging patterns we performed computations of $S_3$ on Sandstone 3D sample.
+They were performed in three different manners: 1) isosceles triangle with a right-triangle
+between the equal side -- this sampling resembles both our right-triangle pattern and pattern
+of Malmir et al. \cite{malmir2018}, computations were made within XY planes within the image and, thus,
+represent directional CF; 2) equilateral triangle with side $r$ directionally analyzed within XY planes;
+3) equilateral triangle with side $r$ averaged over 20 random rotations -- reminiscence of web-like and random patterns.
+
+The results of the comparison are shown in \cref{fig:comparison_patterns}. For isotropic samples curves for
+directional and ensemble averaged, as well as for right-angle isosceles triangle, basically collapse to each other
+with minimal differences.
+\begin{figure*}[ht]
+  \centering
+  \includegraphics[width=0.8\linewidth]{images/fig_compar.png}
+  \caption[]{A comparison of computations of $S_3$ correlation function for the Sandstone sample
+  using different patterns with and without random rotations. Left: evaluated with isosceles triangle 
+  pattern with the side $r$ and the angle between edges $\phi$; sampling triangles are aligned with the plane XY.
+  Middle: evaluated with equilateral triangle pattern with the side $r$; sampling triangles are aligned with the plane XY.
+  Right: evaluated with equilateral triangle pattern with the side $r$. The result is averaged over 20 
+  random rotations of the sampling triangle. Lower image: comparison of $S_3$ functions calculated with 
+  right triangle pattern with length of the both catheti $r$ and equilateral triangle pattern 
+  (both averaged over rotations and aligned with the plane XY).}
+  \label{fig:comparison_patterns}
+\end{figure*}
+
+A Jupiter notebook presenting all these cases is available online \cite{Repo_example} and is a good example of
+applications of our package, especially in terms of establishing \code{ps1} and \code{ps2}
+arrays for arbitrary triangle patterns (isosceles and equilateral cases in our example),
+and for directional and ensemble averaged calculations.
+
 \subsection{Applications to material images}
@@
 
-Wall times are shown in \cref{fig:timings}. It can be seen that the time of
+Wall times are shown in \cref{fig:timings}. They do not depend on the type of sampling pattern used. It can be seen that the time of
 execution is a power function of voxels number. GPU gives a
@@
 
-We have made execuation time comparisons of our algorithm with existing
+We have made execution time comparisons of our algorithm with existing
 algorithms.  However, it is also beneficial to compare some algorithmic details
-against existing digital approaches -- proposed by Malmir~et~al
+against existing digital approaches -- proposed by Malmir~et.~al.
 \cite{malmir2018} and another one by Smith and Torquato \cite{SMITH1988176}. The
@@
 translation. This way the algorithm preserves orientation of triangles stored in
-the pattern. The main advantage of our approach based on right triangle is in
-its parallelizability and ease of implementation. A drawback is that an angle
-between catheti of the sampling pattern is fixed to be $\theta = \frac{\pi}{2}$,
-but it can be mitigated by choosing a random pattern or rotating the
-pattern. The rotations can be random as in the Malmir et al. algorithm, or it
-can be a single rotation to align catheti of the sampling triangle with the
+the pattern. The main advantage of our approach that can operate on arbitrary patterns is in
+its parallelizability and ease of implementation. The rotations necessary
+for arbitrary placement of the pattern within the image can be random as in the Malmir et al. algorithm, or it
+can be a single rotation to align the sampling triangle with the
 direction of anisotropy (\cref{fig:aniso}). The latter allows computing
@@
 
+The question if image rotation affects the quality of computations remains open.
+To answer this question we performed a study on value noise images.
+In \cref{sec:rotqua} we demonstrate that even nearest-neighbor
+interpolation results only in insignificant loss of quality. Rotation of the
+pattern has same drawbacks related to interpolation of the sample which are most
+noticeable at small correlation lengths. The both methods (rotation of the
+sample or the pattern) produce nearly equivalent result if the sample is
+homogeneous and an average pore size is much less than the sample's size (see
+\cref{sec:rotrot}).
+
+Another interesting question is which sampling pattern is more powerful?
+Our results shown in \cref{fig:comparison_patterns} clear illustrate that
+for isotropic structure all sampling techniques provide quite similar results.
+The differences, of course, will be significant for isotropic cases and
+directional 3-point CFs calculations. Again, the clear winner here is not obvious.
+Right-triangular pattern allows to systematically sample the structure with
+predefined direction. On the other hand, equilateral triangle allows to
+minimize the volume of computed functions and represent them as single curve,
+similar to 2-point functions. Random pattern could be useful for rigorous bounds.
+So, the better approach can depend on the problem at hand. Nonetheless,
+the direct comparison of patterns can be performed only on the basis of
+information content -- something we discuss in the next paragraph.
+
 We mentioned that classic set of correlation functions describes both the
@@
 reconstructions is very limited due to computational burden of cluster
-relabeling during annealing \cite{PLoS_ONE}. Still, effective information
+relabeling during annealing \cite{karsanina2015}. Still, effective information
 content assessment techniques will provide a possibility to account for such
@@
 F_{sss}, F_{ssv}$ and $F_{svv}$ in an arbitrary set of points. We also provide a
-function which generates a right-angle triangle pattern. Computations are easily
+function which generates a right-angle triangle pattern which can be useful for
+directional CFs evaluation. Computations are easily
 vectorized and utilize the power of modern CPU and GPU architectures. The
@@
 
+\section{Acknowledgements}
+This research was supported by the Russian Science Foundation grant 23-74-00061.
+
+Collaborative effort of the authors within the FaT iMP (Flow and Transport in Media with Pores) research group
+and used some of its software. We thank our colleague Konstantin Romanenko for suggestions and administrative work.
+
 \appendix
@@
     -\sum\limits_{\substack{l \\ l \ne 0}} E_l & \quad k = 0 \\
-    1 / \rho(k, 0) & \quad \text{otherwise}
+    1 / \rho(k, 0) & \quad \text{otherwise.}
   \end{array}
@@
 so is to use nearest-neighbor interpolation when sampling subvoxel data during
-rotation. This results only in minimal precision loss in computation of
+rotation. As we show below, this results only in minimal precision loss in computation of
 correlation functions.
@@
 of the noise rotated around $Z$ axis by $\theta$ radians by discretizing an
-inequation $f(p(x'), p(y'), p(z')) > U$ where
+inequation $f(p(x'), p(y'), p(z')) > U$ where:
 \begin{equation*}
@@
     \right. \\
-    x ' &= x \mod 2
+    x ' &= x \mod 2.
   \end{aligned}
@@
 dimensionality $300 \times 300 \times 300$ and $600 \times 600 \times 600$
-voxels (i.e. the second resolution is twice as much as the first).
+voxels (i.e., the second resolution is twice as much as the first).
 
@@
 
-\section{Difference between rotating the input image or the sampling pattern}
+\section{Difference between rotation of the input image or the sampling pattern}
 \label{sec:rotrot}
@@
   \centering
-  \subfigure[A sample of value noise with small pores (compared to a size of the
-    sample, $300 \times 300 \times 300$)]{
+  \subfigure[A sample of value noise with small pores]{
     \includegraphics[width=0.4\linewidth]{images/noise2.png}

### 2024-08-29 paper.tex
web-like -> weblike + fill-region

@@
 about studied structures. In this paper, we have developed algorithms and code
-to compute $S_3, C_3, F_{sss}, F_{ssv}$ and $F_{svv}$ with a right-angle and arbitrary
-triangle pattern. The former was believed to be faster to compute, but with the help of precomputed
-regular positions we achieved the same speed for arbitrary pattern. In this work we also 
-implement and demonstrate computations of directional 3-point CFs -- for this
-purpose right-triangular pattern seems to be superior due to explicit orientation and high coverage.
-Moreover, we assess the errors in CFs' evaluation due to image or pattern rotations and show that they 
-have minor effect on accuracy of computations.
-The execution times of our algorithms for the same number of samples are orders of
-magnitude lower than in existing published counterparts. We showed that the volume
-of data produced get unwieldy very easily, especially if computations are
-performed in frequency domain. For these reasons until information content of
-different sets of correlation functions with different "n-pointness" is not
-known, advantages of CFs with $n>3$ are not clear. Nonetheless, developed
-algorithms and code are universal enough to be easily extendable to any $n$
-(with increasing computational and RAM burden). All results are available as
-part of open source package \code{CorrelationFunctions.jl} [Postnicov et al.,
-  2024, Comp.Phys.Commun., 299, 109134]. As described in this paper, 3-point CFs
+to compute $S_3, C_3, F_{sss}, F_{ssv}$ and $F_{svv}$ with a right-angle and
+arbitrary triangle pattern. The former was believed to be faster to compute, but
+with the help of precomputed regular positions we achieved the same speed for
+arbitrary pattern. In this work we also implement and demonstrate computations
+of directional 3-point CFs -- for this purpose right-triangular pattern seems to
+be superior due to explicit orientation and high coverage.  Moreover, we assess
+the errors in CFs' evaluation due to image or pattern rotations and show that
+they have minor effect on accuracy of computations.  The execution times of our
+algorithms for the same number of samples are orders of magnitude lower than in
+existing published counterparts. We showed that the volume of data produced get
+unwieldy very easily, especially if computations are performed in frequency
+domain. For these reasons until information content of different sets of
+correlation functions with different "n-pointness" is not known, advantages of
+CFs with $n>3$ are not clear. Nonetheless, developed algorithms and code are
+universal enough to be easily extendable to any $n$ (with increasing
+computational and RAM burden). All results are available as part of open source
+package \code{CorrelationFunctions.jl} [Postnicov et al., 2024,
+  Comp.Phys.Commun., 299, 109134]. As described in this paper, 3-point CFs
 computations can be immediately applied in a great number of research
@@
 are more involved and, thus, require much more computational resources to
-assess. It has been shown that the amount of additional information content decreases with
-each increase in number of points $n$ \cite{yao1993high,Gommes2}. The
-trade-off between additional information and computational burden is still not
-clear. Nonetheless, the computation of 3-point statistics is known to be
-advantageous at least in the number of applications as related to cosmology,
-astrophysics and turbulence patterns analysis as they can probe non-Gaussian
-signatures in the distribution of matter and energy, which are not captured by their
-2-point counterparts
+assess. It has been shown that the amount of additional information content
+decreases with each increase in number of points $n$
+\cite{yao1993high,Gommes2}. The trade-off between additional information and
+computational burden is still not clear. Nonetheless, the computation of 3-point
+statistics is known to be advantageous at least in the number of applications as
+related to cosmology, astrophysics and turbulence patterns analysis as they can
+probe non-Gaussian signatures in the distribution of matter and energy, which
+are not captured by their 2-point counterparts
 \cite{TakadaJain,hopkins2013stars,gorbunova2016precessing,yoo2022non}.
@@
 \subsection{Triangular sampling pattern}
-There are three major known sampling pattern implementations reported in the literature (\cref{fig:pattern}):
+There are three major known sampling pattern implementations reported in the
+literature (\cref{fig:pattern}):
 \begin{enumerate}
-  \item Arbitrary pattern (or random) triangle is thrown into the structure (e.g., \cite{malmir2018});
-  \item Web-like predefined triangular pattern (e.g., \cite{SMITH1988176});
-  \item Right-triangular sampling pattern (e.g., \cite{dimitrakopoulos2010high}).
+  \item Arbitrary pattern (or random) triangle is thrown into the structure
+    (e.g., \cite{malmir2018});
+  \item Weblike predefined triangular pattern (e.g., \cite{SMITH1988176});
+  \item Right-triangular sampling pattern (e.g.,
+    \cite{dimitrakopoulos2010high}).
 \end{enumerate}
-The second case of the web-like pattern was useful at times of low computational resources and seems to be the least flexible in terms of structure coverage.
-Right-traingle as a pattern was popular due ease of implementation and potential speed gains due to vectorization.
-However, we have organized the algorithms of \code{CorrelationFunctions.jl} to be able to utilize any patterns.
-This was achieved by organizing computational functions not around a shifting pattern, but rather around precomputed points representing
-triangle's vertices -- thus making our approach under the hood using the ideas behind the web-like pattern method.
-
-This is implemented in our code by using the same interface for all computation functions to assess CFs:
+The second case of the weblike pattern was useful at times of low computational
+resources and seems to be the least flexible in terms of structure
+coverage. Right-traingle as a pattern was popular due ease of implementation and
+potential speed gains due to vectorization.  However, we have organized the
+algorithms of \code{CorrelationFunctions.jl} to be able to utilize any patterns.
+This was achieved by organizing computational functions not around a shifting
+pattern, but rather around precomputed points representing triangle's vertices
+-- thus making our approach under the hood using the ideas behind the weblike
+pattern method.
+
+This is implemented in our code by using the same interface for all computation
+functions to assess CFs:
 \begin{verbatim}
@@
 where \code{corrfn} stands for \code{s3} ($S_3$), \code{c3} ($C_3$),
-\code{surf3} ($F_{sss}$) etc., \code{input} is the input array describing the structure, \code{phase} is
-a phase of interest and \code{ps1} and \code{ps2} are arrays of points in which
-correlation function is calculated. Firstly, \code{corrfn} does all necessary
-preparations for the input array (e.g. edge extraction or connected component
-labeling) and then calculates the correlation function for each pair of
-arguments from \code{ps1} and \code{ps2}.
-
-To compare different approaches in this work we performed calculations with right-triangular\cite{dimitrakopoulos2010high,malmir2018},
-equilateral triangle and isosceles triangle with varying angle \cite{SMITH1988176,malmir2018} patterns -- both with averaging
-over the whole structure, or computed in directions (see next two subsections below). In the first case the pattern where arguments
-of a correlation function $x_1$ and $x_2$ are fixed to be parallel to one of the
-axes $X$, $Y$ or $Z$ with restriction $x_1 \perp x_2$ (\cref{fig:pattern}, right scheme).
-Except for equilateral triangle, the output  has dimensions $D_1 \times D_2$ where $D_1$ and $D_2$ are dimensions of the input array along selected axes.
-For equilateral pattern there is a single curve (i.e.,
-similar to $S_2$ graphical representation).
+\code{surf3} ($F_{sss}$) etc., \code{input} is the input array describing the
+structure, \code{phase} is a phase of interest and \code{ps1} and \code{ps2} are
+arrays of points in which correlation function is calculated. Firstly,
+\code{corrfn} does all necessary preparations for the input array (e.g. edge
+extraction or connected component labeling) and then calculates the correlation
+function for each pair of arguments from \code{ps1} and \code{ps2}.
+
+To compare different approaches in this work we performed calculations with
+right-triangular\cite{dimitrakopoulos2010high,malmir2018}, equilateral triangle
+and isosceles triangle with varying angle \cite{SMITH1988176,malmir2018}
+patterns -- both with averaging over the whole structure, or computed in
+directions (see next two subsections below). In the first case the pattern where
+arguments of a correlation function $x_1$ and $x_2$ are fixed to be parallel to
+one of the axes $X$, $Y$ or $Z$ with restriction $x_1 \perp x_2$
+(\cref{fig:pattern}, right scheme). Except for equilateral triangle, the output
+has dimensions $D_1 \times D_2$ where $D_1$ and $D_2$ are dimensions of the
+input array along selected axes. For equilateral pattern there is a single curve
+(i.e., similar to $S_2$ graphical representation).
 
@@
   \includegraphics[width=0.8\linewidth]{images/web-like.png}
-  \caption[]{Schematic representation of patterns for 3-point correlation functions evaluation:
-  arbitrary or random triangle, web-like, and right-triangular patterns. Note that real patterns are
-  more complex and are made simple for visualization, i.e., for right-triangular pattern we sample
-  all possible variations between points. Equilateral or isosceles triangles can be considered
-  as arbitrary patterns and can be either fixed in space, or rotated randomly.}
+  \caption[]{Schematic representation of patterns for 3-point correlation
+    functions evaluation: arbitrary or random triangle, weblike, and
+    right-triangular patterns. Note that real patterns are more complex and are
+    made simple for visualization, i.e., for right-triangular pattern we sample
+    all possible variations between points. Equilateral or isosceles triangles
+    can be considered as arbitrary patterns and can be either fixed in space, or
+    rotated randomly.}
   \label{fig:pattern}
@@
 When an analyzed sample is anisotropic, i.e., it is stretched or oriented along
-some specific direction, it may be beneficial to align one of the sides (cathetus for the right-triangular pattern) of
-sampling triangle \cref{fig:pattern} with that direction. In this case the
-anisotropy present in the sample will be properly captured by computed 3-point
-correlation function.
+some specific direction, it may be beneficial to align one of the sides
+(cathetus for the right-triangular pattern) of sampling triangle
+\cref{fig:pattern} with that direction. In this case the anisotropy present in
+the sample will be properly captured by computed 3-point correlation function.
 
@@
   \includegraphics[width=0.8\linewidth]{images/fig_rot.png}
-  \caption{Examples of directional analysis of images with the help of $S_3$ function
-    when dealing with highly anisotropic media. The right-triangular pattern (\cref{fig:pattern}, right side)
-    which we use in our algorithm is most sensitive to anisotropy which is
-    directed along one of the axes. \\
-    From top down, left to right: an original image of an anisotropic pore; a
-    rotated image of the pore, so it is positioned along the major axis; $S_3$ function
-    for the original pore; $S_3$ function for the rotated pore with a vector
-    $(0.92, -0.4)$ being a direction of elongation of the pore; $S_3$ function
-    averaged across rotations similar to previously known algorithms
-    \cite{berryman1988,SMITH1988176,malmir2018}.}
+  \caption{Examples of directional analysis of images with the help of $S_3$
+    function when dealing with highly anisotropic media. The right-triangular
+    pattern (\cref{fig:pattern}, right side) which we use in our algorithm is
+    most sensitive to anisotropy which is directed along one of the
+    axes. \\ From top down, left to right: an original image of an anisotropic
+    pore; a rotated image of the pore, so it is positioned along the major axis;
+    $S_3$ function for the original pore; $S_3$ function for the rotated pore
+    with a vector $(0.92, -0.4)$ being a direction of elongation of the pore;
+    $S_3$ function averaged across rotations similar to previously known
+    algorithms \cite{berryman1988,SMITH1988176,malmir2018}.}
   \label{fig:aniso}
@@
 anisotropy (that can be determined using \code{$detect\_anisotropy$} function).
-Full correlation map for 3-point functions is impractical due its huge size and, thus,
-is not implemented.
+Full correlation map for 3-point functions is impractical due its huge size and,
+thus, is not implemented.
 
@@
 \label{sec:compare_patterns}
-To compare different sampling and averaging patterns we performed computations of $S_3$ on Sandstone 3D sample.
-They were performed in three different manners: 1) isosceles triangle with a right-triangle
-between the equal side -- this sampling resembles both our right-triangle pattern and pattern
-of Malmir et al. \cite{malmir2018}, computations were made within XY planes within the image and, thus,
-represent directional CF; 2) equilateral triangle with side $r$ directionally analyzed within XY planes;
-3) equilateral triangle with side $r$ averaged over 20 random rotations -- reminiscence of web-like and random patterns.
-
-The results of the comparison are shown in \cref{fig:comparison_patterns}. For isotropic samples curves for
-directional and ensemble averaged, as well as for right-angle isosceles triangle, basically collapse to each other
-with minimal differences.
+To compare different sampling and averaging patterns we performed computations
+of $S_3$ on Sandstone 3D sample.  They were performed in three different
+manners: 1) isosceles triangle with a right-triangle between the equal side --
+this sampling resembles both our right-triangle pattern and pattern of Malmir et
+al. \cite{malmir2018}, computations were made within XY planes within the image
+and, thus, represent directional CF; 2) equilateral triangle with side $r$
+directionally analyzed within XY planes; 3) equilateral triangle with side $r$
+averaged over 20 random rotations -- reminiscence of weblike and random
+patterns.
+
+The results of the comparison are shown in \cref{fig:comparison_patterns}. For
+isotropic samples curves for directional and ensemble averaged, as well as for
+right-angle isosceles triangle, basically collapse to each other with minimal
+differences.
 \begin{figure*}[ht]
-  \centering
-  \includegraphics[width=0.8\linewidth]{images/fig_compar.png}
-  \caption[]{A comparison of computations of $S_3$ correlation function for the Sandstone sample
-  using different patterns with and without random rotations. Left: evaluated with isosceles triangle 
-  pattern with the side $r$ and the angle between edges $\phi$; sampling triangles are aligned with the plane XY.
-  Middle: evaluated with equilateral triangle pattern with the side $r$; sampling triangles are aligned with the plane XY.
-  Right: evaluated with equilateral triangle pattern with the side $r$. The result is averaged over 20 
-  random rotations of the sampling triangle. Lower image: comparison of $S_3$ functions calculated with 
-  right triangle pattern with length of the both catheti $r$ and equilateral triangle pattern 
-  (both averaged over rotations and aligned with the plane XY).}
+  \centering \includegraphics[width=0.8\linewidth]{images/fig_compar.png}
+  \caption[]{A comparison of computations of $S_3$ correlation function for the
+    Sandstone sample using different patterns with and without random
+    rotations. Left: evaluated with isosceles triangle pattern with the side $r$
+    and the angle between edges $\phi$; sampling triangles are aligned with the
+    plane XY.  Middle: evaluated with equilateral triangle pattern with the side
+    $r$; sampling triangles are aligned with the plane XY.  Right: evaluated
+    with equilateral triangle pattern with the side $r$. The result is averaged
+    over 20 random rotations of the sampling triangle. Lower image: comparison
+    of $S_3$ functions calculated with right triangle pattern with length of the
+    both catheti $r$ and equilateral triangle pattern (both averaged over
+    rotations and aligned with the plane XY).}
   \label{fig:comparison_patterns}
@@
 
-A Jupiter notebook presenting all these cases is available online \cite{Repo_example} and is a good example of
-applications of our package, especially in terms of establishing \code{ps1} and \code{ps2}
-arrays for arbitrary triangle patterns (isosceles and equilateral cases in our example),
+A Jupiter notebook presenting all these cases is available online
+\cite{Repo_example} and is a good example of applications of our package,
+especially in terms of establishing \code{ps1} and \code{ps2} arrays for
+arbitrary triangle patterns (isosceles and equilateral cases in our example),
 and for directional and ensemble averaged calculations.
@@
 \subsection{Applications to material images}
-
 \begin{table*}[!htp]
@@
 
-Wall times are shown in \cref{fig:timings}. They do not depend on the type of sampling pattern used. It can be seen that the time of
-execution is a power function of voxels number. GPU gives a
-10x-100x performance boost depending on the correlation function. Note that
-random pixel/voxel patterns are a hard test for some functions, especially for
-$C_3$, as it produces a huge number of separate clusters. Thus, for real samples
-execution times can be even smaller compared to those reported on \cref{fig:timings}.
+Wall times are shown in \cref{fig:timings}. They do not depend on the type of
+sampling pattern used. It can be seen that the time of execution is a power
+function of voxels number. GPU gives a 10x-100x performance boost depending on
+the correlation function. Note that random pixel/voxel patterns are a hard test
+for some functions, especially for $C_3$, as it produces a huge number of
+separate clusters. Thus, for real samples execution times can be even smaller
+compared to those reported on \cref{fig:timings}.
 
@@
 its parallelizability and ease of implementation. The rotations necessary
-for arbitrary placement of the pattern within the image can be random as in the Malmir et al. algorithm, or it
-can be a single rotation to align the sampling triangle with the
-direction of anisotropy (\cref{fig:aniso}). The latter allows computing
-directional 3-point correlation functions for anisotropic structures similar to
-2-point counterparts \cite{10.1063/1.4867611,EPL1}.
+for arbitrary placement of the pattern within the image can be random as in the
+Malmir et al. algorithm, or it can be a single rotation to align the sampling
+triangle with the direction of anisotropy (\cref{fig:aniso}). The latter allows
+computing directional 3-point correlation functions for anisotropic structures
+similar to 2-point counterparts \cite{10.1063/1.4867611,EPL1}.
 
@@
 
-Collaborative effort of the authors within the FaT iMP (Flow and Transport in Media with Pores) research group
-and used some of its software. We thank our colleague Konstantin Romanenko for suggestions and administrative work.
+Collaborative effort of the authors within the FaT iMP (Flow and Transport in
+Media with Pores) research group and used some of its software. We thank our
+colleague Konstantin Romanenko for suggestions and administrative work.
 
@@
 so is to use nearest-neighbor interpolation when sampling subvoxel data during
-rotation. As we show below, this results only in minimal precision loss in computation of
-correlation functions.
+rotation. As we show below, this results only in minimal precision loss in
+computation of correlation functions.
 

### 2024-08-30 paper.tex
Remove non-existent images

@@
 rotation, and this important issue is explored later.
-\begin{figure*}[ht]
-  \centering
-  \includegraphics[width=0.8\linewidth]{images/fig_rot.png}
-  \caption{Examples of directional analysis of images with the help of $S_3$
-    function when dealing with highly anisotropic media. The right-triangular
-    pattern (\cref{fig:pattern}, right side) which we use in our algorithm is
-    most sensitive to anisotropy which is directed along one of the
-    axes. \\ From top down, left to right: an original image of an anisotropic
-    pore; a rotated image of the pore, so it is positioned along the major axis;
-    $S_3$ function for the original pore; $S_3$ function for the rotated pore
-    with a vector $(0.92, -0.4)$ being a direction of elongation of the pore;
-    $S_3$ function averaged across rotations similar to previously known
-    algorithms \cite{berryman1988,SMITH1988176,malmir2018}.}
-  \label{fig:aniso}
-\end{figure*}
+%\begin{figure*}[ht]
+%  \centering
+%  \includegraphics[width=0.8\linewidth]{images/fig_rot.png}
+%  \caption{Examples of directional analysis of images with the help of $S_3$
+%    function when dealing with highly anisotropic media. The right-triangular
+%    pattern (\cref{fig:pattern}, right side) which we use in our algorithm is
+%    most sensitive to anisotropy which is directed along one of the
+%    axes. \\ From top down, left to right: an original image of an anisotropic
+%    pore; a rotated image of the pore, so it is positioned along the major axis;
+%    $S_3$ function for the original pore; $S_3$ function for the rotated pore
+%    with a vector $(0.92, -0.4)$ being a direction of elongation of the pore;
+%    $S_3$ function averaged across rotations similar to previously known
+%    algorithms \cite{berryman1988,SMITH1988176,malmir2018}.}
+%  \label{fig:aniso}
+%\end{figure*}
 
@@
 differences.
-\begin{figure*}[ht]
-  \centering \includegraphics[width=0.8\linewidth]{images/fig_compar.png}
-  \caption[]{A comparison of computations of $S_3$ correlation function for the
-    Sandstone sample using different patterns with and without random
-    rotations. Left: evaluated with isosceles triangle pattern with the side $r$
-    and the angle between edges $\phi$; sampling triangles are aligned with the
-    plane XY.  Middle: evaluated with equilateral triangle pattern with the side
-    $r$; sampling triangles are aligned with the plane XY.  Right: evaluated
-    with equilateral triangle pattern with the side $r$. The result is averaged
-    over 20 random rotations of the sampling triangle. Lower image: comparison
-    of $S_3$ functions calculated with right triangle pattern with length of the
-    both catheti $r$ and equilateral triangle pattern (both averaged over
-    rotations and aligned with the plane XY).}
-  \label{fig:comparison_patterns}
-\end{figure*}
+%\begin{figure*}[ht]
+%  \centering \includegraphics[width=0.8\linewidth]{images/fig_compar.png}
+%  \caption[]{A comparison of computations of $S_3$ correlation function for the
+%    Sandstone sample using different patterns with and without random
+%    rotations. Left: evaluated with isosceles triangle pattern with the side $r$
+%    and the angle between edges $\phi$; sampling triangles are aligned with the
+%    plane XY.  Middle: evaluated with equilateral triangle pattern with the side
+%    $r$; sampling triangles are aligned with the plane XY.  Right: evaluated
+%    with equilateral triangle pattern with the side $r$. The result is averaged
+%    over 20 random rotations of the sampling triangle. Lower image: comparison
+%    of $S_3$ functions calculated with right triangle pattern with length of the
+%    both catheti $r$ and equilateral triangle pattern (both averaged over
+%    rotations and aligned with the plane XY).}
+%  \label{fig:comparison_patterns}
+%\end{figure*}
 

### 2024-08-30 data/error/plot.py
Fix one image

@@ -25,14 +25,14 @@ plt.figure(figsize = (10, 8), dpi = 300)
 plt.rc('font', size = 25)
 ax1 = plt.gca()
 ax2 = ax1.twinx()
-p1, = ax1.plot(xs, errsss_300, 'b.-', label = r'$F_{sss}, 300 \times 300 \times 300$', linewidth = 3, markersize = 10)
-p2, = ax1.plot(xs, errsss_600, 'g.-', label = r'$F_{sss}, 600 \times 600 \times 600$', linewidth = 3, markersize = 10)
-p3, = ax2.plot(xs, errs3_300, 'r.-', label = r'$S_3, 300 \times 300 \times 300$', linewidth = 3, markersize = 10)
-p4, = ax2.plot(xs, errs3_600, 'm.-', label = r'$S_3, 600 \times 600 \times 600$', linewidth = 3, markersize = 10)
+p1, = ax1.plot(xs, errsss_300, 'bo-', label = r'$F_{sss}, 300^3$', linewidth = 3, markersize = 10)
+p2, = ax1.plot(xs, errsss_600, 'g*-', label = r'$F_{sss}, 600^3$', linewidth = 3, markersize = 10)
+p3, = ax2.plot(xs, errs3_300, 'r^-', label = r'$S_3, 300^3$', linewidth = 3, markersize = 10)
+p4, = ax2.plot(xs, errs3_600, 'ms-', label = r'$S_3, 600^3$', linewidth = 3, markersize = 10)
 ax1.set_xlabel(r'$\theta$')
 ax1.set_ylabel(r'$\max (\varepsilon)$, $F_{sss}$')
 ax2.set_ylabel(r'$\max (\varepsilon)$, $S_3$')
 ax1.ticklabel_format(axis = "y", scilimits = (0, 0), useMathText = True)
 ax2.ticklabel_format(axis = "y", scilimits = (0, 0), useMathText = True)
-ax1.legend(handles = [p1, p2, p3, p4])
+ax1.legend(handles = [p1, p2, p3, p4], loc='best', bbox_to_anchor=(0.5, 0.03, 0.4, 0.4))
 plt.savefig('roterror.png')

### 2024-08-30 timings/timings.py
Fix two images

@@ -5,18 +5,18 @@ import matplotlib.pyplot as plt
 
 legend = ['$S_3$', '$C_3$', '$F_{sss}$', '$F_{ssv}$', '$F_{svv}$']
 names = map(lambda name: name + '.npy', ['s3', 'c3', 'surf3', 'surf2void', 'surfvoid2'])
-colors = ['b', 'r', 'g', 'k', 'm']
+colors = ['bo', 'rv', 'gP', 'k*', 'ms']
 
 plt.figure(figsize = (10, 9), dpi = 300)
-plt.rc('font', size = 25)
+plt.rc('font', size = 24)
 
 for (name, color) in zip(names, colors):
     data = np.load('gpu/' + name)
-    plt.plot(data[:,0]**3, data[:,1], color + '.-', linewidth = 3)
+    plt.plot(data[:,0]**3, data[:,1], color + '-', linewidth = 3, markersize = 10)
 
 plt.legend(legend)
 plt.yscale('log')
 plt.xscale('log')
 plt.xlabel('Number of voxels')
-plt.ylabel('Time of execution, s')
+plt.ylabel('Time of execution [s]')
 plt.savefig('timings-gpu.png')

### 2024-08-30 data/plot-surface.py
Fix 2 images

@@ -12,11 +12,12 @@ def sv(x, R):
 ssc = np.load('ball-ss.npy')
 svc = np.load('ball-sv.npy')
 
-xs = np.linspace(0, 0.5, ssc.size)
+xs1 = np.linspace(0, 0.5, svc.size)
+xs2 = np.linspace(0, 0.5, 1000)
 plt.figure(figsize = (10, 9), dpi = 300)
 plt.rc('font', size = 25)
-plt.plot(xs, ssc, linewidth = 3)
-plt.plot(xs, ss(xs, 0.2), linewidth = 3)
+plt.plot(xs1, ssc, color = '#1f77b4', linewidth = 3)
+plt.plot(xs2, ss(xs2, 0.2), color = '#ff7f0e', linestyle = '-.', linewidth = 3)
 plt.ylim([0, 20])
 plt.xlabel(r'$r$')
 plt.ylabel(r'$F_{ssv}(r, 0.5)$')
@@ -25,11 +26,12 @@ plt.ticklabel_format(axis = "y", scilimits = (0, 0), useMathText = True)
 plt.ticklabel_format(axis = "x", scilimits = (0, 0), useMathText = True)
 plt.savefig('../images/ball-ssv.png')
 
-xs = np.linspace(0, 0.5, svc.size)
+xs1 = np.linspace(0, 0.5, svc.size)
+xs2 = np.linspace(0, 0.5, 1000)
 plt.figure(figsize = (10, 9), dpi = 300)
 plt.rc('font', size = 25)
-plt.plot(xs, svc, linewidth = 3)
-plt.plot(xs, sv(xs, 0.2), linewidth = 3)
+plt.plot(xs1, svc, color = '#1f77b4', linewidth = 3)
+plt.plot(xs2, sv(xs2, 0.2), color = '#ff7f0e', linestyle = '-.', linewidth = 3)
 plt.xlabel(r'$r$')
 plt.ylabel(r'$F_{svv}(r, 0.5)$')
 plt.legend(['Calculation', 'Theory'])

### 2024-08-30 data/plot-s2.py
Fix 2 images

@@ -8,7 +8,8 @@ def s2_th(x, λ, R):
     return np.exp(-ρ * np.where(x < 2*R, 1 + 3/4*x/R - 1/16*(x/R)**3, 2))
 
 s2 = np.load('test-s2.npy')
-xs = np.linspace(0, 0.5, s2.size)
+xs1 = np.linspace(0, 0.5, s2.size)
+xs2 = np.linspace(0, 0.5, 1000)
 
 #plt.figure(figsize = (10, 8), dpi = 300)
 #plt.rc('font', size = 25)
@@ -33,8 +34,8 @@ xs = np.linspace(0, 0.5, s2.size)
 
 plt.figure(figsize = (10, 9), dpi = 300)
 plt.rc('font', size = 25)
-plt.plot(xs, s2, linewidth = 3)
-plt.plot(xs, s2_th(xs, 5000, 0.02), linewidth = 3)
+plt.plot(xs1, s2, color = '#1f77b4', linewidth = 3)
+plt.plot(xs2, s2_th(xs2, 5000, 0.02), color = '#ff7f0e', linestyle = '-.', linewidth = 3)
 plt.ticklabel_format(axis = "y", scilimits = (0, 0), useMathText = True)
 plt.ticklabel_format(axis = "x", scilimits = (0, 0), useMathText = True)
 plt.xlim([0.025, 0.055])

### 2024-09-02 paper.tex
Fix 3 images
Fix 2 images
Fix formatting

--- 2024-08-29 paper.tex
@@
 domain. For these reasons until information content of different sets of
-correlation functions with different "n-pointness" is not known, advantages of
+correlation functions with different ``n-pointness'' is not known, advantages of
 CFs with $n>3$ are not clear. Nonetheless, developed algorithms and code are
@@
 has to possess following key properties: (1) high information content, (2) ease
-of assess, (3) high compression ratio (i.e., descriptor is much "smaller" than
+of assess, (3) high compression ratio (i.e., descriptor is much ``smaller'' than
 the structure itself).
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{images/3point.png}
+  \subfigure[2-point CF]{
+    \includegraphics[width=0.45\linewidth]{images/2p.png}}
+  \hfill
+  \subfigure[3-point CF]{
+    \includegraphics[width=0.45\linewidth]{images/3p.png}}
   \caption[]{A schematic representation of a binary porous media (pores are
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{images/web-like.png}
+  \subfigure[Arbitrary]{
+    \includegraphics[width=0.3\linewidth]{images/arbitrary.png}}
+  \hfill
+  \subfigure[Weblike]{
+    \includegraphics[width=0.3\linewidth]{images/web.png}}
+  \hfill
+  \subfigure[Right-triangular]{
+    \includegraphics[width=0.3\linewidth]{images/right.png}}
   \caption[]{Schematic representation of patterns for 3-point correlation
@@
 domain. For these reasons until information content of different sets of
-correlation functions with different "n-pointness" is known, it is seemingly no
+correlation functions with different ``n-pointness'' is known, it is seemingly no
 much reason to increase the number of points. Nonetheless, developed algorithms

### 2024-09-02 data/heatmap.py
Fix 4 images

@@ -2,13 +2,23 @@
 
 import numpy as np
 import matplotlib.pyplot as plt
+from matplotlib import ticker
+import matplotlib as mpl
 
-data = np.load('shale-s3.npy')
+data = np.load('shale-avg.npy')
+
+def fuck(x, pos):
+    if pos%4 == 0:
+        f = ticker.LogFormatterSciNotation(10, False)
+        return f(x)
+    else:
+        return ''
 
 plt.figure(figsize = (8, 8), dpi = 300)
 plt.rc('font', size = 20)
 plt.imshow(data, extent = (0, 160/2*2.25, 160/2*2.25, 0), norm = 'log')
-plt.colorbar()
-plt.xlabel(r'$r_1 \cdot (1, 1, 0), \mu m$')
-plt.ylabel(r'$r_2 \cdot (-1, 1, 0), \mu m$')
-plt.savefig('../images/shale-s3.png', bbox_inches = 'tight')
+cb = plt.colorbar()
+cb.minorformatter = ticker.FuncFormatter(fuck)
+plt.xlabel(r'$r_1\ [\mu m]$')
+plt.ylabel(r'$r_2\ [\mu m]$')
+plt.savefig('../images/shale-avg.png', bbox_inches = 'tight')

### 2024-09-03 paper.tex
Fix isosceles
Fix another image
Fix formula
Replace \times

@@
 correlation map, however, requires a lot of memory and is rarely
-needed. Imagine, that the input array $A$ is of dimensions $500 \times 500$.
-Then, considering that single precision floating point numbers are used,
+needed. Imagine, that the input array $A$ is of dimensions $500^2$. Then,
+considering that single precision floating point numbers are used,
 $4 \cdot 2 \cdot 500^4 / 1000^3 = 500$ GB are needed to store Fourier image of
-the map. Moreover, Fourier image of the whole map has to be computed even if only one
-element of the map in spatial domain is required. The aforementioned limitations
-render this approach impractical.
+the map. Moreover, Fourier image of the whole map has to be computed even if
+only one element of the map in spatial domain is required. The aforementioned
+limitations render this approach impractical.
 
@@
   \begin{array}{ll}
-    1 & \quad x = y \ne L_{(void)} \\
+    1 & \quad x = y \ne B \\
     0 & \quad \text{otherwise}.
@@
 \end{equation}
-where $L_{(void)}$ is a label of the void phase.
+where $B$ is a background label (i.e. a label for all elements which are not in
+the phase $n$).
 
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{images/fig_rot.png}
+  \subfigure[Original image]{
+    \includegraphics[width=0.4\linewidth,frame]{images/aniso.png}}
+  \hfill
+  \subfigure[Rotated image]{
+    \includegraphics[width=0.4\linewidth,frame]{images/aniso-rot.png}}
+  \vskip\baselineskip
+  \includegraphics[width=0.3\linewidth]{images/aniso-s3.png}
+  \hfill
+  \includegraphics[width=0.3\linewidth]{images/aniso-rot-s3.png}
+  \hfill
+  \includegraphics[width=0.3\linewidth]{images/aniso-avg-s3.png}
   \caption{Examples of directional analysis of images with the help of $S_3$
@@
 \begin{figure*}[ht]
-  \centering \includegraphics[width=0.8\linewidth]{images/fig_compar.png}
+  \centering
+  \subfigure[Isosceles with right angle]{
+    \includegraphics[width=0.4\linewidth]{images/isosceles.png}}
+  \hfill
+  \subfigure[Equilateral]{
+    \includegraphics[width=0.4\linewidth]{images/equilateral.png}}
+  \vskip\baselineskip
+  \subfigure[With random rotations]{
+    \includegraphics[width=0.4\linewidth]{images/equilateral-avg.png}}
+  \hfill
+  \subfigure[Comparison plot]{
+    \includegraphics[width=0.4\linewidth]{images/alltogether.png}}
   \caption[]{A comparison of computations of $S_3$ correlation function for the
@@
     \hline
-    Sandstone & XCT &  $500 \times 500 \times 500$ & 2.25 & 0.9703 \\
-    Soil & Reconstruction & $500 \times 500 \times 500$ & 0.72 & 0.9431 \\
-    Shale & Reconstruction & $160 \times 160 \times 160$ & 2.25 & 0.8912 \\
+    Sandstone & XCT &  $500^3$ & 2.25 & 0.9703 \\
+    Soil & Reconstruction & $500^3$ & 0.72 & 0.9431 \\
+    Shale & Reconstruction & $160^3$ & 2.25 & 0.8912 \\
     Sandstone & SEM &  $1280 \times 869$ & 0.10 & 0.9613 \\
@@
 rotated noise at those resolutions. For this study we have produced images with
-dimensionality $300 \times 300 \times 300$ and $600 \times 600 \times 600$
-voxels (i.e., the second resolution is twice as much as the first).
+dimensionality $300^3$ and $600^3$ voxels (i.e., the second resolution is twice
+as much as the first).
 
@@
 indeterminacy. The maximal error for all $\theta$'s are 0.6\% for $S_3$ and 5.0\%
-for $F_{sss}$ for dimensionality $300 \times 300 \times 300$ and 0.3\% for $S_3$
-and 4.5\% for $F_{sss}$ for dimensionality $600 \times 600 \times 600$.
+for $F_{sss}$ for dimensionality $300^3$ and 0.3\% for $S_3$ and 4.5\% for
+$F_{sss}$ for dimensionality $600^3$.
 

### 2024-09-03 paper.tex
clear -> clearly

@@
 Another interesting question is which sampling pattern is more powerful?
-Our results shown in \cref{fig:comparison_patterns} clear illustrate that
+Our results shown in \cref{fig:comparison_patterns} clearly illustrate that
 for isotropic structure all sampling techniques provide quite similar results.

### 2024-09-03 paper.tex
Fix figure caption

--- 2024-09-03 paper.tex
@@
 \subsection{Comparison of sampling patterns}
-\label{sec:compare_patterns}
+\label{sec:compare-patterns}
 To compare different sampling and averaging patterns we performed computations
@@
 
-The results of the comparison are shown in \cref{fig:comparison_patterns}. For
+The results of the comparison are shown in \cref{fig:comparison-patterns}. For
 isotropic samples curves for directional and ensemble averaged, as well as for
@@
   \subfigure[Isosceles with right angle]{
-    \includegraphics[width=0.4\linewidth]{images/isosceles.png}}
+    \includegraphics[width=0.4\linewidth]{images/isosceles.png}
+    \label{fig:cp-isosceles}}
   \hfill
   \subfigure[Equilateral]{
-    \includegraphics[width=0.4\linewidth]{images/equilateral.png}}
+    \includegraphics[width=0.4\linewidth]{images/equilateral.png}
+    \label{fig:cp-equilateral}}
   \vskip\baselineskip
   \subfigure[With random rotations]{
-    \includegraphics[width=0.4\linewidth]{images/equilateral-avg.png}}
+    \includegraphics[width=0.4\linewidth]{images/equilateral-avg.png}
+    \label{fig:cp-equilateral-avg}}
   \hfill
   \subfigure[Comparison plot]{
-    \includegraphics[width=0.4\linewidth]{images/alltogether.png}}
+    \includegraphics[width=0.4\linewidth]{images/alltogether.png}
+    \label{fig:cp-comp}}
   \caption[]{A comparison of computations of $S_3$ correlation function for the
     Sandstone sample using different patterns with and without random
-    rotations. Left: evaluated with isosceles triangle pattern with the side $r$
-    and the angle between edges $\phi$; sampling triangles are aligned with the
-    plane XY.  Middle: evaluated with equilateral triangle pattern with the side
-    $r$; sampling triangles are aligned with the plane XY.  Right: evaluated
-    with equilateral triangle pattern with the side $r$. The result is averaged
-    over 20 random rotations of the sampling triangle. Lower image: comparison
-    of $S_3$ functions calculated with right triangle pattern with length of the
-    both catheti $r$ and equilateral triangle pattern (both averaged over
-    rotations and aligned with the plane XY).}
-  \label{fig:comparison_patterns}
+    rotations. Fig.~\ref{fig:cp-isosceles}: evaluated with isosceles triangle
+    pattern with the side $r$ and the angle between edges $\phi$; sampling
+    triangles are aligned with the plane XY. Fig.~\ref{fig:cp-equilateral}:
+    evaluated with equilateral triangle pattern with the side $r$; sampling
+    triangles are aligned with the plane XY. Fig.~\ref{fig:cp-equilateral-avg}:
+    evaluated with equilateral triangle pattern with the side $r$. The result is
+    averaged over 20 random rotations of the sampling
+    triangle. Fig.~\ref{fig:cp-comp}: comparison of $S_3$ functions calculated
+    with right triangle pattern with length of the both catheti $r$ and
+    equilateral triangle pattern (both averaged over rotations and aligned with
+    the plane XY).}
+  \label{fig:comparison-patterns}
 \end{figure*}
@@
 Another interesting question is which sampling pattern is more powerful?
-Our results shown in \cref{fig:comparison_patterns} clear illustrate that
+Our results shown in \cref{fig:comparison-patterns} clearly illustrate that
 for isotropic structure all sampling techniques provide quite similar results.
